\documentclass{article}
\usepackage[utf8]{inputenc}
%Packages Used------------------------------------------
% the following is to get qoppa and Qoppa
\DeclareFontFamily{T1}{cbgreek}{}
\DeclareFontShape{T1}{cbgreek}{m}{n}{<-6>  grmn0500 <6-7> grmn0600 <7-8> grmn0700 <8-9> grmn0800 <9-10> grmn0900 <10-12> grmn1000 <12-17> grmn1200 <17-> grmn1728}{}
\DeclareSymbolFont{quadratics}{T1}{cbgreek}{m}{n}
\DeclareMathSymbol{\qoppa}{\mathord}{quadratics}{19}
\DeclareMathSymbol{\Qoppa}{\mathord}{quadratics}{21}

\usepackage{amsmath, amssymb, amsthm}
\usepackage{longtable}
%\usepackage{amsfonts}
%\usepackage{mathtools}
%\usepackage{wasysym}
%\usepackage{MnSymbol}
%\usepackage{thmtools}
\usepackage{stmaryrd} % wanted to use this for \varoast
\usepackage[letterpaper,margin=1in]{geometry}   
%\usepackage{slashed}
%\usepackage[english]{babel}				
%\usepackage[pdfencoding=auto, psdextra, draft=false]{hyperref}
\usepackage{bookmark}
\usepackage{url}		
\usepackage{lmodern}			
\usepackage[T1]{fontenc}
%\usepackage{xspace}		
%\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{soul,color}
\usepackage{tikz-cd}
\usepackage[maxbibnames=99,style=alphabetic]{biblatex}
\usepackage{csquotes}
\usepackage{chngcntr}
\usepackage[bbgreekl]{mathbbol}
\counterwithin{equation}{section}
\addbibresource{biblio.bib}
\usepackage{todonotes}

%hyperlink setup
\definecolor{darkred}{RGB}{128,0,0}
\definecolor{darkgreen}{RGB}{0,128,0}
\definecolor{darkblue}{RGB}{0,0,128}

\hypersetup{linktocpage,
	pdfborder = {0 0 0},
	colorlinks,
	citecolor=darkgreen,
	filecolor=darkred,
	linkcolor=darkblue,
	urlcolor=cyan!50!black!90}

%Greek and Latin black board bold-----------------------
\DeclareSymbolFontAlphabet{\mathbb}{AMSb}
\DeclareSymbolFontAlphabet{\mathbbl}{bbold}

%shortcut commands-------------------------------------------
\DeclareMathOperator{\Br}{Br} % Brauer functor
\DeclareMathOperator{\Brp}{Br^p} % Poincare Brauer functor
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\CAlg}{CAlg} % Commutative Algebra objects
\DeclareMathOperator{\Alg}{Alg}
\DeclareMathOperator{\CAlgp}{CAlg^p} % Poincare ring spectra
\DeclareMathOperator{\Cat}{Cat} % small categories
\DeclareMathOperator{\CAT}{C\normalfont\textsc{at}_\infty} % (not necessarily small) Categories
\DeclareMathOperator{\Catex}{\Cat_\infty^{ex}} % small stable categories with exact functors
\DeclareMathOperator{\Cath}{Cat^h_\infty} % Hermitian Categories
\DeclareMathOperator{\Catp}{Cat^p_\infty} % Poincare Categories
\DeclareMathOperator{\Catpidem}{Cat^p_{\infty, idem}} % idempotent complete Poincare Categories
\DeclareMathOperator{\Einfty}{\mathbf{E}_\infty} % E-infinity 
\DeclareMathOperator{\ex}{ex} % exact 
\DeclareMathOperator{\Fun}{Fun} % Functors
\DeclareMathOperator{\gp}{gp} % grouplike
\DeclareMathOperator{\id}{id} % identity
\DeclareMathOperator{\idem}{idem} % idempotent
\DeclareMathOperator{\Mod}{Mod} % Modules
\DeclareMathOperator{\LMod}{LMod} % Left modules
\DeclareMathOperator{\BiMod}{BiMod} % Bimodules
\DeclareMathOperator{\Modh}{{}^{\sigma}Mod} % Hermitian modules
%\DeclareMathOperator{\op}{op} % opposite functor
\DeclareMathOperator{\Pic}{Pic} % Picard functor
\DeclareMathOperator{\Picp}{Pic^p} % Poincare Picard functor
\DeclareMathOperator{\Pn}{Pn} % Poincare space functor
\DeclareMathOperator{\Spectra}{Sp} % Spectra
\DeclareMathOperator{\Spaces}{\mathcal{S}} % Spaces
\DeclareMathOperator{\sSet}{sSet}
\DeclareMathOperator{\Mon}{Mon} % monoids
\DeclareMathOperator*{\fiberproduct}{\times}

\newcommand{\pf}{{\bf Proof. \ }}
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\rho}{\varrho}
\renewcommand{\phi}{\varphi}
\newcommand{\NN}{\ensuremath{\mathbb{N}}\xspace}
\newcommand{\ZZ}{\ensuremath{\mathbb{Z}}\xspace}
\newcommand{\QQ}{\ensuremath{\mathbb{Q}}\xspace}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\ensuremath{\mathbb{C}}\xspace}
\newcommand{\FF}{\ensuremath{\mathbb{F}}\xspace}
\newcommand{\EE}{\mathbb{E}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\TT}{\ensuremath{\mathbb{T}}\xspace}
\newcommand{\RP}{\ensuremath{\mathbb{RP}}\xspace}
\newcommand{\DD}{\ensuremath{\mathbbl{\Delta}}\xspace}
\newcommand{\tc}{\ensuremath{\mathrm{TC}}}
\newcommand{\thh}{\ensuremath{\mathrm{THH}}}
\newcommand{\tp}{\ensuremath{\mathrm{TP}}}
\newcommand{\tr}{\ensuremath{\mathrm{TR}}}
\newcommand{\pnpic}{\ensuremath{\mathrm{PnPic}}}
\newcommand{\pnbr}{\ensuremath{\mathrm{PnBr}}}
\newcommand{\pic}{\ensuremath{\mathrm{Pic}}}
\newcommand{\br}{\ensuremath{\mathrm{Br}}}
\DeclareMathOperator*{\colim}{\ensuremath{\operatorname{colim}}}
\newcommand{\aps}{\mathrm{APS}}
\newcommand{\psch}{\mathrm{PSch}}
\newcommand{\perf}{\mathrm{Perf}}
\newcommand{\perfpn}{\mathrm{Perf}^{\mathrm{Pn}}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\sphere}{\mathbb{S}^0}
\newcommand{\Assoc}{\mathrm{Assoc}}
\newcommand{\Associnv}{\mathrm{Assoc}_\sigma}
\newcommand{\BMinv}{\mathrm{BM}_\sigma} % for `hermitian' bimodules; made a macro so we can change this later easily. 
\newcommand{\Fin}{\mathrm{Fin}} % finite sets 
\newcommand{\epoly}{\mathrm{epoly}}
\newcommand{\ev}{\mathrm{ev}}
\newcommand{\morphism}[3]{\mathop{\rotatebox{270}{$\xrightarrow{\rotatebox{90}{$\scriptstyle#2$}}$}}\limits^{#1}_{#3}}
\newcommand{\Ar}{\mathrm{Ar}}


%Theorem Environments ----------------------------------------------------------------
\newtheorem{theorem}[equation]{Theorem}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem{corollary}[equation]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[equation]{Definition}
\newtheorem{construction}[equation]{Construction}
\newtheorem{remark}[equation]{Remark}
\newtheorem{remarks}[equation]{Remarks}
\newtheorem{observation}[equation]{Observation}
\newtheorem{notation}[equation]{Notation}
\newtheorem{example}[equation]{Example}
\newtheorem{question}[equation]{Question}
\newtheorem{recollection}[equation]{Recollection}
\newtheorem{variant}[equation]{Variant}

\newcommand{\Viktor}[1]{\todo{V: #1}}
\newcommand{\Noah}[1]{\todo[color=red]{N: #1}}
\newcommand{\Lucy}[1]{\todo[color=cyan!30]{\footnotesize L: #1}}
\newcommand{\Lucyil}[1]{\todo[inline,color=cyan!30]{\footnotesize L: #1}}

\title{Et cetera}
\author{Viktor Burghardt, Noah Riggenbach, Lucy Yang}
\date{}
\addbibresource{biblio.bib}

\begin{document}

\maketitle
\begin{abstract}
   Dumping ground for other stuff: Notes, one-off observations, stuff that we can collectively use when preparing talks, etc. \Lucy{I make no promises re: organization but I will do my best to keep it reasonably readable} 
\end{abstract}
\tableofcontents

\section{Talk prep}

\section{References}
\begin{itemize}
    \item \href{https://ems.press/journals/dm/articles/8965687}{Involutions of Azumaya algebras} by First and Williams (2020 \emph{Documenta})
    \item \href{https://arxiv.org/abs/2405.15260}{Counterexamples in involutions of Azumaya algebras} by First and Williams; much more readable than the 2020 Documenta paper 
    \item \href{https://arxiv.org/abs/1510.06133}{Azumaya algebras without involution} by Auel, First, and Williams: the introduction of this provides a very helpful historical overview of the connection between involutions on Azumaya algebras and 2-torsion/kernel of coRes
\end{itemize}
\section{Questions and directions}
\begin{question}
    [Literature]
\begin{itemize}
    \item In \cite{MR1162189} Parimala--Srinivas assume that 2 is invertible in the ring of functions. 
    Has anyone been able to extend their results to the 2 not necessarily invertible case in the meantime? 
\end{itemize}
\end{question}
\begin{question}
    [Morita theory for $ \Catp $]
    Let $ R $ be a Poincaré ring. 
    Suppose given two $ R $-algebras (suitably interpreted so their module categories are canonically endowed with $ R $-linear Poincaré structures--perhaps $ \mathbb{E}_\sigma $) $ A $, $ B $. 
    Can we characterize
    \begin{equation*}
        \hom_{\Catp_R}\left(\left(\Mod_A^\omega,\Qoppa_A\right),\left(\Mod_B^\omega,\Qoppa_B\right)\right)
     \end{equation*} 
     in terms of something bimodule-like? 
\end{question}
\begin{question}
    On page 2 of the \emph{Counterexamples} paper, First and Williams write that `` existence of an extraordinary involution means classification of Azumaya algebras with involution...\emph{cannot} be reduced to questions about projective modules and hermitian forms on them.'' 

    What if we replaced projective modules by perfect complexes? 
\end{question}
\begin{question}
    First--Williams show (see discussion in \S4 of the \emph{Counterexamples} paper) that coarse type classify many (most?) Azumaya algebras up to (étale-local) \emph{isomorphism}. 

    What is a suitable derived version of ``coarse type''?
\end{question}

\begin{question}
    [asked by Andrew Nov 2, 2024] 
    C. Schlichtkrull shows in \href{https://arxiv.org/pdf/math/0405079}{this paper} that a map $ BGL_1(R) \to K(R) \to THH(R) \to R $ in terms of the Hopf map $ \eta $. 

    Is there a ``Poincaré'' version of this result? 
\end{question}

\begin{question}
    Are there some general conditions for a ring with involution $ R $ so that the inclusion $ R^{C_2} \to R $ is `nice'?

    There's some stuff in section 4 \href{https://www.math.nagoya-u.ac.jp/~hasimoto/paper/knop2.pdf}{here}, idk. 
    Also see M. Hochster and J. L. Roberts, Rings of invariants of reductive groups acting on regular rings are Cohen–Macaulay. 
\end{question}
\begin{question}
    \href{https://arxiv.org/pdf/1607.06392}{Derived category of non-generic cubic 4-fold} has an application/use of pushforwards of Azumaya algebras along double covers. 
    Kuznetsov has also written about this, see `Derived categories of quadric fibrations and intersections of quadrics' \href{https://homepage.mi-ras.ru/~akuznet/publications/DerivedCategoriesOfQuadricFibrationsAndIntersectionsOfQuadrics.pdf}{here}.
\end{question}

\paragraph{Applications to Hodge theory?} 
\begin{itemize}
    \item \href{https://arxiv.org/abs/1501.05294}{A Deligne pairing for Hermitian Azumaya modules}
    \item \href{https://www.math.ucla.edu/~totaro/papers/public_html/structure.pdf}{Burt Totaro's paper} on Hodge structures of type $ (n,0,\ldots, 0, n) $
    \item There's some stuff about endomorphisms of Hodge structures \href{https://webusers.imj-prg.fr/~claire.voisin/Articlesweb/verbanianotes.pdf}{here}
\end{itemize}

\section{Thoughts \& observations}
\begin{question}
   When $ R $ has the Tate Poincaré structure and $ (\Mod_A^\omega, M_A, N_A, N_A \to M_A^{tC_2}) $ is invertible, then by invertibility have an equivalence $ \hom_R(A, R)\simeq N_A\otimes_R N_{A^\op} $ of $ A \otimes_R A^\op $-modules. 
   Restricting the left-hand side along the unit map $ R \to A $ gives a map $ N_A \otimes_R N_{A^\op} \to \hom_R(R,R) \simeq R $. 
   Is this a perfect ($R$-linear) pairing? 

   I \emph{think} using that $ R^{\varphi C_2} \simeq R $ and combining the linear and bilinear part conditions, we get something like
   \begin{equation*}
       M_A \otimes_R M_{A^\op} \simeq (N_A \otimes_R N_{A^\op})^{\otimes_R 2} \qquad \text{ as $A \otimes_R A^\op$-bimodules. }
   \end{equation*}
   Is this useful?
\end{question}

\paragraph{Brauer-Severi schemes} 
We know there is a correspondence between Azumaya algebras $ A $ over $ X $ and Brauer-Severi schemes. 
What does a Poincaré structure on $ \Mod_A^\omega $ mean `geometrically' for $ D^b_{\mathrm{coh}} $ of the corresponding Brauer-Severi scheme? 
(Lucy: I didn't get very far here, but just typing up what I had)
\begin{itemize}
    \item $ \Mod_A^\omega $ corresponds to $ \alpha $-twisted sheaves on $ X $ (see Proposition 3.2.2.1 of Max Lieblich's thesis)
    \item The bounded derived category of $ \alpha $-twisted sheaves on $ X $ includes as one `piece' of a semiorthogonal decomposition on $ D^b_{\mathrm{coh}} $ of the corresponding Brauer-Severi scheme (see Theorem 5.1 \href{https://arxiv.org/abs/math/0511497}{here})
\end{itemize}

\section{Desperate Flailing}

This section is a cronical of my thoughts about $\mathbb{G}_m^\Qoppa$.
\paragraph{Goal} The goal is to build a Poincar{\'e} ring $\mathbb{G}_{m}^\Qoppa:=(\mathrm{Mod}_R, \Qoppa_R)$  such that $B\mathbb{G}_m^\Qoppa(\underline{S}) = \Picp(\underline{S})$ for any Poincar{\'e} ring $\underline{S}$.
\begin{lemma}
Let $\underline{S}$ be a Poincar{\'e} ring. Then $\pi_0(\mathrm{Aut}_{\mathrm{Pn}(\mathrm{Mod}_S)}(S,u))=\{s\in \pi_0(S)^\times | s=1 \textrm{ in }\pi_0(S^{C_2})\}$.
\end{lemma}
\begin{proof}
Since the functor $\mathrm{Pn}(\mathrm{Mod}_S)\to \mathrm{Mod}_S$ is conservative it follows that an element of $\pi_0(\mathrm{Aut}_{\mathrm{Pn}(\mathrm{Mod}_S)}(S,u))$ must have underlying map an element of $\pi_0\mathrm{Aut}(S)=\pi_0(S)^\times$. Then in order for $s\in \pi_0(S)^\times$ to induce a map $(S,u)\to (S,u)$, the induced map $s^*:S^{C_2}\to S^{C_2}$ must satisfy $s^*(u)=u$. The pullback is given by multiplication by $s$, so this requirement translates into $s$ being the unit, as desired.
\end{proof}

The problem I thought existed maybe doesn't. Here is a candidate construction:

\begin{construction}
Define $R$ to be the $\mathbb{E}_\infty$ ring given by $\mathbb{S}\{x^{\pm 1}, y^{\pm 1}\}\otimes_{\mathbb{S}\{z\}}\mathbb{S}$ where the map $\mathbb{S}\{z\}\to \mathbb{S}\{x^{\pm 1}, y^{\pm 1}\}$ is induced by the map $z\mapsto xy$, and the map $\mathbb{S}\{z\}\to \mathbb{S}$ is induced by $z\mapsto 1$. We can give $R$ an $\mathbb{E}_\infty$ ring structure in $\mathrm{Sp}^{BC_2}$ by taking the trivial action on $\mathbb{S}\{z\}$ and $\mathbb{S}$, and taking the action induced by $x\mapsto y$ and $y\mapsto x$ on $\mathbb{S}\{x^{\pm 1}, y^{\pm 1}\}$. Thus in $\mathrm{CAlg}(\mathrm{Sp}^{BC_2})$ the ring $R$ corepresents the functor $S\mapsto \{s\in \pi_0(S)^\times| s\sigma(s)=1\}$.

Now take $\underline{R}$ to be the Poincar{\'e} ring with underlying Borel $C_2$ structure as described in the previous paragraph and geometric fixed points $R^{\phi C_2}=\mathbb{S}$ and the map $R^{\phi C_2}\to R^{tC_2}$ given by the unit map. Endowing $R^{\phi C_2}$ with the $R$-module structre given by $x,y\mapsto 1$, it remains to show that the unit map $R^{\phi C_2}\to R^{tC_2}$ factors the Tate valued Frobenius $R\to R^{tC_2}$ in order to promote $\underline{R}$ to a Poincar{\'e} ring. By construction of $R$ it is then enough to show that on $\pi_0$ the Tate valued Frobenius sends $x,y\mapsto 1$ in $\pi_0(R^{tC_2})$. This map sends both $x$ and $y$ to $xy\in \pi_0(R^{tC_2})$. These areequal to $1$ in $\pi_0(R^{tC_2})$ since the functor $(-)^{tC_2}$ is lax-monoidal so $R^{tC_2}$ is a modules over $\mathbb{S}\{x^{\pm 1}, y^{\pm 1}\}^{tC_2}\otimes_{\mathbb{S}\{z\}^{tC_2}}\mathbb{S}^{tC_2}$ which has the image of $xy$ equal to $1$. 
\end{construction}

Now consider another Poincar{\'e} ring $\underline{S}$. We then have that maps $\pi_0(\mathrm{Maps}(\underline{R},\underline{S}))$ is the data of a unit $s\in \pi_0(S)^\times$, a path $s\sigma(s)\to 1$ in $\Omega^\infty S$, and paths $x,y\to 1$ in $\Omega^\infty S^{\phi C_2}$.  This then agrees with $\mathbb{G}_m^\Qoppa$ by the following lemma.

\begin{lemma}
Let $S\in \mathrm{CAlg}(\mathrm{Sp}^{BC_2})$ and $s\in \pi_0(S)^\times$. Then $s\sigma(s)=1$ in $\pi_0(S)$ if and only if $(s\otimes s)^*$ acts by $1$ on $\pi_0(S^{hC_2})=\pi_0(\mathrm{Hom}_{S\otimes S}(S\otimes S, S)^{hC_2})$.
\end{lemma}
\begin{proof}
The 'only if' direction follows from the fact that the map $S^{hC_2}\to S$ is an $S$-bimodule map. Now suppose that $s\sigma(s)=1$ in  $S$. Then before taking homotopy fixed points the induced map $s^*=id$ because $S$ is $\mathbb{E}_\infty$.\footnote{Or just $\mathbb{E}_2$.} 
\end{proof}

\section{Modules with genuine involution} 
\begin{remark}
    [Lucy] I'm just going to put drafts of stuff pertaining to hermitian modules\Lucy{or whatever we want to keep calling these} here. 
    Eventually when it gets to be more complete, I will hopefully move this entire section over to the main file. 
\end{remark}
\paragraph{Meta-commentary} There are (at least) three things we want to do: 
\begin{enumerate}[label=(\alph*)]
    \item Define a category of `bimodules with involution over algebras with anti-involution' equipped with a forgetful functor $ \Theta \colon \mathrm{BMod}_{\mathrm{inv}}(-) \to \EE_1\Alg(-)^{hC_2} $. 
    \item Show that $ \Theta $ is a coCartesian fibration. 
    For this, it suffices to show that it is a \emph{Cartesian} fibration and that it satisfies the hypotheses of \cite[Corollary 5.2.2.5]{HTT}
    \begin{itemize}
        \item I used to think that we could obtain this by `bootstrapping' a result from Higher Algebra, plus some facts about assembly. 
        This doesn't seem to be working, so I'm just going to try to do this directly (imitating certain aspects of Chapter 4 of higher algebra.) 
    \end{itemize}
    \item Define a relative tensor product for hermitian bimodules 
    \item Show that the formula for the cocartesian pushforward along a map $ A \to B $ in $ \EE_1\Alg(-)^{hC_2} $ is something like $ - \otimes_{A \otimes A^\op} \left(B \otimes B^\op \right) \otimes_{B\otimes B^\op} B $. 
    \begin{itemize}
        \item In Higher Algebra, the formula for the cocartesian pushforward is proven in \cite[\S4.6]{LurHA}; in particular, this is in the section on duality. 
        In particular, see Proposition 4.6.2.17 and the paragraph immediately preceding this.  
        \item I don't know how to do this yet--while (a) and (b) are not useful if I can't show (c), I can't suss out the feasibility of (c) without (a) and (b) already in place. 
    \end{itemize} 
    \item Towards an adjunction between $ \EE_\sigma $-algebras and categories with additional structure.  
    \begin{itemize}
        \item Involutive version of statement that, for a monoidal $ \infty $-category $ \mathcal{C} $ and an $ \EE_1 $-algebra $ A $, $ \mathrm{LMod}_A(\mathcal{C}) $ is right-tensored over $ \mathcal{C} $? 
        \item Involutive version of endomorphism categories? \cite[\S4.7.1]{LurHA}
    \end{itemize}
\end{enumerate} 
I think that the equivalence of part (b) of the definition of an Azumaya algebra with genuine involution follows from the property of being Azumaya; see Lemma 1(b) (and p.216 for the `type 2' case) of \cite{MR1162189}. 
\begin{lemma}
    Let $ R $ be an $ \EE_\infty $-ring with an involution $ \sigma \colon R \xrightarrow{\sim} R$ and suppose $ A $ is an $ \EE_1 $-$ R $-algebra with an anti-involution $ \lambda \colon A \xrightarrow{\sim} \sigma^* A^\op $. 
    Suppose $ A $ is further Azumaya in the sense of \Lucy{reference}. 
    Then the bilinear pairing 
    \begin{equation*}
    \begin{split}
        A \otimes_R \sigma^* A \xrightarrow{\id \otimes \sigma^*\lambda} A \otimes_R A^\op \simeq \mathrm{End}_R(A) \xrightarrow{\mathrm{tr}} R     
    \end{split}    
    \end{equation*}
    is perfect, i.e. its adjoint $ A \to (\sigma^* A)^\vee $ is an equivalence. 
\end{lemma}
\begin{question}
    Does the map in part (e) of the definition of an Azumaya algebra with genuine involution follow from property of being Azumaya? 
\end{question}

\subsection{Step (a)}
\begin{definition}\label{defn:colored_operad_monoid_with_involution}
\Lucy{This is just an imitation of \cite[Definition 4.1.1.1]{LurHA}, modified in accordance with ideas from \S5.4.2. }
    Define a colored operad $ \Associnv $ as follows:
    \begin{enumerate}[label=(\roman*)]
        \item The colored operad has a single object, which we denote by $ \mathfrak{a} $. 
        \item For every finite set $ I $, the set of operations $ \mathrm{Mul}_{\Associnv}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq \mathcal{L}I \times \{\pm 1\}^I $, where $ \mathcal{L}I $ is the set of linear orderings on $ I $ and an element of $ \{\pm 1\}^I $ is a function $ I \to \{\pm 1 \} $. 
        \item Suppose given a map of finite sets $ \alpha \colon I \to J $, together with operations $ (\preceq_j, f_j \colon I_j \to \{\pm 1\}) \in \mathrm{Mul}_{\Associnv}\left(\left\{\mathfrak{a}_i\right\}_{\alpha(i)=j}, \mathfrak{a}\right) $ and $ (\preceq_J, g \colon J \to \{\pm 1\}) \in \mathrm{Mul}_{\Associnv}\left(\left\{\mathfrak{a}_j\right\}_{j\in J}, \mathfrak{a}\right) $. 
        Define a linear ordering on the set $ I $ as follows: $ i \leq i' $ if $ \alpha(i) \preceq_J \alpha(i') $ or $ \alpha(i) = \alpha(i')= j $ and $ i \preceq_j i' $ and $ g(j)= +1 $ or $ \alpha(i) = \alpha(i')= j $ and $ i \succeq_j i' $ and $ g(j)= -1 $. 
        Finally, define a function 
        \begin{align*}
            I &\to \{\pm 1\} \\
            i &\mapsto f_{\alpha(i)} (i) \cdot  g(\alpha(i))\,,
        \end{align*}  
        where the multiplication on $ \{\pm 1\} $ is the usual one. 
    \end{enumerate} 
\end{definition}
\begin{remark}\label{rmk:assoc_opd_to_assoc_inv_opd}
    There is a map of colored operads $ \iota \colon \mathrm{Assoc} \to \Associnv $ which is the identity on objects and on operations $ \mathrm{Mul}_{\mathrm{Assoc}}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\Associnv}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ is $ \mathrm{id}_{\mathcal{L}I} \times \{ c_1\} $ where $ c_1 $ is the constant function on $ I $ with value $ 1 $. 

    There is another map of colored operads $ \iota^{\mathrm{rev}} \colon \mathrm{Assoc} \to \Associnv $ which is the identity on objects and on operations $ \mathrm{Mul}_{\mathrm{Assoc}}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\Associnv}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ sends a linear ordering $ \ell $ to $ (\ell^{\mathrm{rev}}, c_{-1})$ where $ c_{-1} $ is the constant function on $ I $ with value $ 1 $. 
\end{remark}
\begin{definition}\label{defn:infty_operad_monoid_with_involution}
    Let $ \Associnv^\otimes $ denote the associated $ \infty $-operad (via Construction 2.1.1.7 and Example 2.1.1.21 of \cite{LurHA}). 
\end{definition} 
\begin{remark}
    Unwinding definitions
    \begin{itemize}
        \item Objects $ \Associnv^\otimes $ are finite pointed sets $ \langle n \rangle \in \mathrm{Fin}_* $ 
        \item Morphisms $ \langle m \rangle \to \langle n \rangle $ consist of 
        \begin{itemize}
            \item $ \alpha \colon \langle m \rangle \to \langle n \rangle $ a map of finite pointed sets
            \item for each $ i \in \langle n \rangle^\circ $, a linear ordering $ \preceq_i $ on the inverse image $ \alpha^{-1}(\{i\}) $ 
            \item a map of sets $ s \colon  \alpha^{-1}\left(\langle m \rangle^\circ\right) \to \{\pm 1\} $
        \end{itemize}
        \item For each pair of morphisms
        \begin{equation*}
             \left(\beta \colon \langle \ell \rangle \to \langle m \rangle, \preceq_j, s\right) \qquad \left(\alpha \colon \langle m \rangle \to \langle n \rangle, \preceq_i, t\right) \,,
        \end{equation*}
        the composite is the triple $ \left(\alpha \circ \beta, \preceq_j'', u \right) $ where $ \preceq_j'' $ is the ordering on $ (\alpha \circ \beta)^{-1}(\{i\}) $ so that if $ a,b \in \langle \ell \rangle $ so that $ \alpha (\beta(a)) = \alpha(\beta(b)) $, then $ a \preceq_j'' b $ if $ \beta(a) \preceq_i \beta(b) $ or $ \beta(a) =_i \beta(b) = i $ and $ a \preceq_i b $ if $ s(i) = 1 $ or $ a \succeq_i b $ if $ s(i) = -1 $. 
        Finally $ u (l) = s(l) \cdot t(\beta(l))  $. 
        \Lucy{Note that when $ s, t$ are identically one, the resulting order $ \preceq_j''$ agrees with the lexicographic order defined in \cite[Remark 4.1.1.4]{LurHA}.}  
    \end{itemize}
\end{remark}
\begin{remark}\label{rmk:assoc_infty_opd_to_assoc_inv_infty_opd}
    The maps $ \iota, \iota^{\mathrm{rev}} $ of Remark \ref{rmk:assoc_opd_to_assoc_inv_opd} induce maps of $ \infty $-operads $ \mathrm{Assoc}^\otimes \to \Associnv^\otimes $. 
    There is a canonical identification $ \iota^{\mathrm{rev}} = \sigma \circ \iota $, where $ \sigma $ is the automorphism of the associative operad considered in \cite[Remark 4.1.1.7]{LurHA}. 

    Note that each object $ \langle n \rangle \in \Associnv^\otimes $ has a distinguished automorphism $ \mathrm{rev}_{\langle n \rangle} $ of order two given by the identity map on $ \langle n \rangle $ and the constant map $ c_{-1} \colon \langle n \rangle^\circ \to \{\pm 1\} $ at $ -1 $. 
    There is a canonical natural equivalence $ \iota \overset{\sim}{\implies} \iota^{\mathrm{rev}} $ whose component at $ \langle n \rangle $ is $ \mathrm{rev}_{\langle n \rangle} $. 
\end{remark}
\begin{definition}\label{defn:naive_involutive_algebras}
    Let $ \mathcal{C}^\otimes  $ be a $ \infty $-operad equipped with the data of a fibration\Lucy{do we need weaker than cocartesian fibration?} $ p \colon \mathcal{C}^\otimes \to \Associnv^\otimes $. 
    Let $ \Alg^\sigma (\mathcal{C}) $ denote the $ \infty $-category $ \Alg_{/\Associnv}(\mathcal{C}) $ of $ \infty $-operad sections of $ p $. 
    We will refer to $ \Alg^\sigma(\mathcal{C}) $ as the $ \infty $-category of \emph{involutive algebra objects of $ \mathcal{C}$}. 

    An \emph{involutive monoidal $ \infty $-category} is the data of a cocartesian fibration $ \mathcal{C}^\otimes \to \Associnv^\otimes $. 
\end{definition}
\begin{remark}\label{rmk:assoc_inv_mon_cat_as_mon_cat_with_autoequiv}
    Suppose given a cocartesian fibration $ f \colon \mathcal{D}^\otimes \to \Associnv^\otimes $ of $ \infty $-operads. 
    Write $ \mathcal{C}^\otimes := \mathcal{D}^\otimes \times_{\Associnv^\otimes, \iota} \mathrm{Assoc}^\otimes $; $ \mathcal{C}^\otimes $ is a monoidal $ \infty $-category in the sense of \cite[Definition 4.1.1.10]{LurHA}. 
    Furthermore, $ \mathcal{C}^\otimes_{\mathrm{rev}}:= \mathcal{D}^\otimes \times_{\Associnv^\otimes, \iota^{\mathrm{rev}}} \mathrm{Assoc}^\otimes $ is a monoidal $ \infty $-category. 
    By Remark \ref{rmk:assoc_infty_opd_to_assoc_inv_infty_opd}, this notation is consistent with that of \cite[Remark 4.1.1.7]{LurHA}. 
    In particular, a $ \Associnv $-monoidal $ \infty $-category $ \mathcal{D}^\otimes $ determines a monoidal $ \infty $-category $ \mathcal{C}^\otimes $ equipped with a monoidal equivalence $ \sigma_{\mathcal{C}} \colon \mathcal{C}^\otimes \xrightarrow{\sim} \mathcal{C}^\otimes_{\mathrm{rev}} $. 
    Pullback along the involution of $ \mathrm{Assoc}^\otimes $ determines another monoidal equivalence $ \sigma_{\mathcal{C}}^{\mathrm{rev}} \colon \mathcal{C}^\otimes_{\mathrm{rev}} \xrightarrow{\sim} \mathcal{C}^\otimes $, and our assumptions imply that $ \sigma_{\mathcal{C}}^{\mathrm{rev}} \circ \sigma_{\mathcal{C}} $ is equivalent to the identity on $ \mathcal{C}^\otimes $. 

    Now suppose that $ A $ is an involutive algebra object of $ \mathcal{D} $. 
    With the same notation as before, pullback along $ \iota $ (resp. $ \iota^{\mathrm{rev}} $) determines associative algebra objects $ u(A) $, $ u^{\mathrm{rev}}(A) $ of $ \mathcal{C} $ and $ \mathcal{C}_{\mathrm{rev}} $, respectively. 
    Note that $ \sigma_{\mathcal{C}}(u(A)) $ is an algebra object of $ \mathcal{C}_{\mathrm{rev}} $, which we may regard as an algebra object of $ \mathcal{C} $ by precomposing with the autoequivalence $ \sigma \colon \mathrm{Assoc}^\otimes \xrightarrow{\sim} \mathrm{Assoc}^\otimes $. 
    It follows from Remark \ref{rmk:assoc_infty_opd_to_assoc_inv_infty_opd} that $ A $ determines an equivalence $ \sigma_A \colon u(A) \xrightarrow{\sim} \sigma_{\mathcal{C}}(u(A))^{\mathrm{rev}} $ of algebra objects in $ \mathcal{C} $. 

    Now suppose furthermore that $ \mathcal{D}^\otimes $ is of the form $ \mathcal{E}^\otimes \times_{\mathrm{Fin}_*} \Associnv^\otimes $ for some symmetric monoidal $ \infty $-category $ \mathcal{E} $. 
    Then the associated involution $ \sigma_{\mathcal{C}} $ is the identity, and for any involutive algebra object $ A $ of $ \mathcal{D} $, $ \sigma_A $ is an equivalence $ u(A) \simeq u(A)^{\mathrm{rev}} $ satisfying $ \sigma_A^{\mathrm{rev}} \circ \sigma_A \simeq \mathrm{id}_A $. 
\end{remark}
\begin{remark}\label{rmk:naive_inv_alg_as_assoc_alg}
    Suppose given a cocartesian fibration $ f \colon \mathcal{D}^\otimes \to \Associnv^\otimes $ of $ \infty $-operads, and write $ \mathcal{C} $ for its underlying monoidal $ \infty $-category with equivalence $ \sigma_{\mathcal{C}} $ as in Remark \ref{rmk:assoc_inv_mon_cat_as_mon_cat_with_autoequiv}. 
    The functors of Remark \ref{rmk:assoc_infty_opd_to_assoc_inv_infty_opd} induce a functor 
    \begin{equation*}
        \Alg^\sigma(\mathcal{D}) \to \Alg(\mathcal{C}) \times \Alg(\mathcal{C}_{\mathrm{rev}}) \,;
    \end{equation*}
    moreover, the aforementioned functor factors through the fixed points of the $ C _2 $-action on the right-hand side given by $ \Alg(\mathcal{C}) \times \Alg(\mathcal{C}_{\mathrm{rev}}) \xrightarrow{\mathrm{swap}} \Alg(\mathcal{C}_{\mathrm{rev}}) \times \Alg(\mathcal{C}) \xrightarrow{\sigma_{\mathcal{C}} \times \sigma_{\mathcal{C}}} \Alg(\mathcal{C}) \times \Alg(\mathcal{C}_{\mathrm{rev}}) $. 
\end{remark}
\begin{definition}
    Define a category $ \Delta_\sigma $ 
    \begin{itemize}
        \item objects are pairs $ ([n], s \colon \{1, \ldots, n\} \to \{\pm 1\}) $ \Lucy{maybe better to write $ s $ as a function defined on the set of \emph{morphisms} $ i < i+1 $ in $[n]$.}
        \item a morphism from $ ([n], s \colon \{1, \ldots, n\} \to \{\pm 1\}) $ to $ ([m], t \colon \{0, 1, \ldots, m\} \to \{\pm 1\}) $ is an order-preserving map $ [n] \to [m] $ in $ \Delta $. 
    \end{itemize}
\end{definition}
\begin{construction}\label{cons:involutive_cut}
    Define a functor $ \mathrm{Cut} \colon \Delta_\sigma^\op \to \Associnv^\otimes $: 
    \begin{itemize}
        \item For each $ ([n],s) $, we have $ \mathrm{Cut}([n],s) = \langle n \rangle $. 
        \item Given a morphism $ \alpha\colon ([n],s) \to ([m], t) $, the associated morphism $ \mathrm{Cut} ([n],s) \to \mathrm{Cut}([m], t) $ consists of
        \begin{itemize}
            \item On underlying finite pointed sets $ \langle m\rangle \to \langle n \rangle $, $ \mathrm{Cut} $ agrees with that appearing in \cite[Construction 4.1.2.9]{LurHA}
            \item Identifying the cut $ \{k \mid k< j\} \sqcup \{k \mid k \geq j \} $ with the morphism $ j-1 < j $, we may regard $ s \colon \langle n\rangle^\circ \to \{\pm 1\} $ and likewise $ t \colon \langle m\rangle^\circ \to \{\pm 1\} $. 
            Define $ u\colon \mathrm{Cut}(\alpha)^{-1}\left(\langle n\rangle^\circ\right) \to \{\pm 1\} $ to be the unique function so that $ u(j)t(j) = s(\mathrm{Cut}(\alpha)(j)) $. 
            % This means that $ \alpha^{-1}(\{k \mid k< j\}) $ and $ \alpha^{-1}(\{k \mid k \geq j\}) $ 
        \end{itemize}
    \end{itemize}
\end{construction}
\begin{lemma}\label{lemma:involutive_cut_is_approximation}
    The functor $ \mathrm{Cut} \colon \Delta^\op_\sigma \to \Associnv^\otimes $ exhibits $ \Delta^\op_\sigma $ as an approximation to the $ \infty $-operad $ \Associnv^\otimes $. 
    \Lucyil{I think the proof of this lemma is not too different from the proof of Proposition 4.1.2.11 of \cite{LurHA}; the point here is just to unravel the definitions of locally coCartesian and Cartesian; the morphisms in $ \Delta^\op_\sigma $ are a little more complicated than $ \Delta^\op $, but not by much. } 
\end{lemma}
\begin{notation}\label{ntn:E_sigma_monoidal_cat_variant}
    Let $ \mathcal{C}^\otimes \to \Associnv^\otimes $ exhibit $ \mathcal{C} $ as $ \EE_\sigma $-monoidal. 
    Let $ \mathcal{C}^\varoast $ denote the fiber product $ \mathcal{C}^\otimes \times_{\Associnv^\otimes} \Delta^\op_{\sigma} $. 
\end{notation}
\begin{definition}\label{defn:inert_map_in_involutive_simplicial_cat}
    Say that a morphism $ ([n], s) \to ([m], t) $ is \emph{inert} if the induced map $ \mathrm{Cut}([m],t) \to \mathrm{Cut}([n],s) $ is an inert morphism in $ \Associnv^\otimes $. 
\end{definition}
\begin{definition}
    A \emph{$ \RR^\sigma $-planar operad} is an $ \infty $-category $ \mathcal{O}^\varoast $ equipped with a functor $ q \colon \mathcal{O}^\varoast \to \Delta^\op_\sigma $ so that 
    \begin{enumerate}
        \item For every object $ X \in \mathcal{O}^\varoast $ and every inert morphism $ \alpha\colon ([n],s) \to q(X) $ in $ \Delta_\sigma $, there is a $ q $-cocartesian morphism $ \overline{\alpha} \colon X \to Y $ satisfying $ q (\overline{\alpha}) = \alpha $
        \item Let $ X $ be an object satisfying $ q (X) = ([n],s) $, and choose $ q $-cocartesian morphisms $ \overline{\alpha}_i \colon X \to X_i $ corresponding to the morphism $ ([i-1< i], s_i) \to ([n], s) $ which is the inclusion on underlying sets and satisfies $ s_i(i) = s(i) $. 
        Then the morphisms $ \overline{\alpha}_i $ exhibit $ X $ as the $ q $-product of the $ X_i $. 
        \item For each $ n \geq 0 $, the construction $ C \mapsto \{C_i \}_{1 \leq i \leq n} $ induces an equivalence of $ \infty $-categories 
        \begin{equation*}
            \mathcal{O}^\varoast \times_{\Delta^\op_\sigma} \{([n], s)\} \xrightarrow{\sim} \left(\mathcal{O}^\varoast \times_{\Delta^\op_\sigma} \{([1], s|_{\{i\}})\}\right)^{\times n}
        \end{equation*}
    \end{enumerate}
    We say that a morphism $ \alpha $ in $ \RR^\sigma $-planar operad is \emph{inert} if it is $ q $-cocartesian and $ q (\alpha) $ is inert in $ \Delta^\op_\sigma $ in the sense of Definition \ref{defn:inert_map_in_involutive_simplicial_cat}. 
\end{definition}
\begin{definition}\label{defn:inv_planar_alg}
    Let $ q \colon \mathcal{O}^\varoast \to \Delta^\op_\sigma $ be a $ \RR^\sigma $-planar operad. 
    An $ \AA^\sigma_\infty $-algebra object of $ \mathcal{O}^{\varoast} $ is a section of $ q $ which carries inert morphisms to inert morphisms. 
    Write $ \Alg_{\AA^\sigma_\infty}(\mathcal{O}) $ for the full subcategory of $ \Fun_{\Delta^\op_{\sigma}}\left(\Delta^\op_\sigma, \mathcal{O}^\varoast\right) $ on $ \AA^\sigma_\infty $-algebra objects.  
\end{definition}
\begin{proposition}
    Let $ \mathcal{O}^\otimes \to \Associnv^\otimes $ be a fibration of $ \infty $-operads. 
    Then precomposition with the functor $ \mathrm{Cut} $ of Construction \ref{cons:involutive_cut} induces an equivalence of $ \infty $-categories
    \begin{equation*}
        \Alg_{\Associnv}(\mathcal{O}) \xrightarrow{\sim} \Alg_{\AA_\infty^\sigma}\left(\mathcal{O}\right)\,.
    \end{equation*}
\end{proposition}
\begin{proof}
    Combine Lemma \ref{lemma:involutive_cut_is_approximation} with \cite[Theorem 2.3.3.23]{LurHA}. 
\end{proof}
\begin{definition}\label{defn:inv_leftmod_operad}
    Define a colored operad $ \mathbf{LM}_\mathrm{inv} $
    \begin{enumerate}[label=(\roman*)]
        \item The set of objects of $ \mathbf{LM}_\mathrm{inv} $ has two elements, which we denote by $ \mathfrak{a}, \mathfrak{m} $. 
        \item Let $ \{X_i\}_{i \in I} $ be a finite collection of objects of $ \mathbf{LM}_{\mathrm{inv}} $ and let $ Y $ be another object of $ \mathbf{LM}_{\mathrm{inv}} $. 
        If $ Y = \mathfrak{a} $, then $ \mathrm{Mul}_{\mathbf{LM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is the set of pairs consisting of a linear ordering on $ I $ and a function $ I \to \{\pm 1\} $ if $ X_i = \mathfrak{a} $ for all $ i $, and empty otherwise. 
        If $ Y = \mathfrak{m} $, then $ \mathrm{Mul}_{\mathbf{LM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is a subset of the set of pairs $ (\lambda, c) $ consisting of a linear ordering $ \lambda = \{i_1 < i_2 < \cdots < i_n\} $ on $ I $ and a function $ c\colon I \to \{\pm 1 \} $ satisfying either 
        \begin{itemize}
            \item  $ X_{i_n} = \mathfrak{m} $ and $ c(i_n) = 1 $ and $ X_{j} = \mathfrak{a} $ otherwise
            \item  $ X_{i_1} = \mathfrak{m} $ and $ c(i_n) = -1 $ and $ X_{j} = \mathfrak{a} $ otherwise
            % \item if there is exactly one index $ i_k $ so that $ X_{i_k} = \mathfrak{m} $ and $ X_j = \mathfrak{a} $ for all $ j \neq i_k $, and $ \mathrm{Mul}_{\mathbf{LM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is empty otherwise. 
        \end{itemize}
        \item The composition law on $ \mathbf{LM}_{\mathrm{inv}} $ is determined by the composition of linear orderings, with reversal of linear orderings according to Definition \ref{defn:colored_operad_monoid_with_involution} 
    \end{enumerate}
\end{definition} 
\begin{remark}
    There is a colored operad $ \mathbf{RM}_{\mathrm{inv}} $ defined exactly in the same way as $ \mathbf{LM}_{\mathrm{inv}} $ in Definition \ref{defn:inv_leftmod_operad}. 
    In the interest of precision: $ \mathbf{RM}_{\mathrm{inv}} $ has the same objects $ \mathfrak{a}, \mathfrak{m} $. 
    Let $ \{X_i\}_{i \in I} $ be a finite collection of objects of $ \mathbf{RM}_{\mathrm{inv}} $ and let $ Y $ be another object of $ \mathbf{RM}_{\mathrm{inv}} $. 
    If $ Y = \mathfrak{m} $, then $ \mathrm{Mul}_{\mathbf{RM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is a subset of the set of pairs $ (\lambda, c) $ consisting of a linear ordering $ \lambda = \{i_1 < i_2 < \cdots < i_n\} $ on $ I $ and a function $ c\colon I \to \{\pm 1 \} $ satisfying either 
    \begin{itemize}
        \item  $ X_{i_n} = \mathfrak{m} $ and $ c(i_n) = -1 $ and $ X_{j} = \mathfrak{a} $ otherwise
        \item  $ X_{i_1} = \mathfrak{m} $ and $ c(i_n) = 1 $ and $ X_{j} = \mathfrak{a} $ otherwise
        % \item if there is exactly one index $ i_k $ so that $ X_{i_k} = \mathfrak{m} $ and $ X_j = \mathfrak{a} $ for all $ j \neq i_k $, and $ \mathrm{Mul}_{\mathbf{LM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is empty otherwise. 
    \end{itemize}
\end{remark}
\begin{remark} % compare Remark 4.2.1.2
    Restricting to the objects which are both called $ \mathfrak{a} $, we see that both $ \mathbf{LM}_\mathrm{inv} $ and $ \mathbf{RM}_{\mathrm{inv}} $ have a sub-colored operad which is canonically identified with $ \mathbf{Assoc}_\mathrm{inv} $ of Definition \ref{defn:colored_operad_monoid_with_involution}. 
\end{remark}
\begin{remark}\label{rmk:lmod_opd_to_inv_lmod_opd}
    There is a map of colored operads $ \iota \colon \mathrm{LM} \to \mathrm{LM}_{\sigma} $ which sends $ \mathfrak{m} $ to $ \mathfrak{m} $ and sends $ \mathfrak{a} $ to $ \mathfrak{a} $. 
    On $ \mathrm{Mul}_{\mathrm{LM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\mathrm{LM}_\sigma}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $  is $ \mathrm{id}_{\mathcal{L}I} \times \{ c_1\} $, this map agrees with $ \iota $ of Remark \ref{rmk:assoc_opd_to_assoc_inv_opd}. 
    On $ \mathrm{Mul}_{\mathrm{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I} \sqcup\{\mathfrak{m}\}, \mathfrak{m}\right) \subseteq  \mathcal{L}(I\sqcup \{j\}) \to \mathrm{Mul}_{\mathrm{BM}_\sigma}\left(\left\{\mathfrak{a}_i\right\}_{i \in I} \sqcup \{\mathfrak{m}\}, \mathfrak{m}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ is the restriction of the map $ \mathrm{id}_{\mathcal{L}(I\sqcup \{j\})} \times \{ c_1\} $ where $ c_1 $ is the constant function on $ I \sqcup \{j\} $ with value $ 1 $. 

    There is a map of colored operads $ \iota^{\mathrm{rev}} \colon \mathrm{RM} \to \mathrm{LM}_{\sigma} $ which sends $ \mathfrak{m} $ to $ \mathfrak{m} $ and sends $ \mathfrak{a} $ to $ \mathfrak{a} $. 
    On $ \mathrm{Mul}_{\mathrm{RM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\mathrm{LM}_\sigma}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $  is $ \mathrm{rev}_{\mathcal{L}I} \times \{ c_{1}\} $, this map agrees with $ \iota^{\mathrm{rev}} $ of Remark \ref{rmk:assoc_opd_to_assoc_inv_opd}. 
    On $ \mathrm{Mul}_{\mathrm{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I} \sqcup\{\mathfrak{m}\}, \mathfrak{m}\right) \subseteq  \mathcal{L}(I\sqcup \{j\}) \to \mathrm{Mul}_{\mathrm{BM}_\sigma}\left(\left\{\mathfrak{a}_i\right\}_{i \in I} \sqcup \{\mathfrak{m}\}, \mathfrak{m}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ is the restriction of the map $ \mathrm{rev}_{\mathcal{L}(I\sqcup \{j\})} \times \{ c_1\} $ where $ c_1 $ is the constant function on $ I \sqcup \{j\} $ with value $ 1 $. 
\end{remark}
\begin{definition}\label{defn:inv_bimod_operad}
    Define colored operads $ \mathbf{BM}_\mathrm{inv} $ and $ \mathbf{BM}_\sigma $
    \begin{enumerate}[label=(\roman*)]
        \item The set of objects of $ \mathbf{BM}_\mathrm{inv} $ has three elements, which we denote by $ \mathfrak{a}_\ell, \mathfrak{a}_r, \mathfrak{m} $. 
        $ \mathbf{BM}_\sigma $ has the same objects
        \item Let $ \{X_i\}_{i \in I} $ be a finite collection of objects of $ \mathbf{BM}_{\mathrm{inv}} $ and let $ Y $ be another object of $ \mathbf{BM}_{\mathrm{inv}} $. 
        If $ Y = \mathfrak{a}_\ell $ (resp. $ Y = \mathfrak{a}_r $), then $ \mathrm{Mul}_{\mathbf{BM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is the set of pairs consisting of a linear ordering on $ I $ and a function $ I \to \{\pm 1\} $ if $ X_i = \mathfrak{a}_\ell $ (resp. $ X_i = \mathfrak{a}_r $) for all $ i $, and empty otherwise. 
        If $ Y = \mathfrak{m} $, then $ \mathrm{Mul}_{\mathbf{BM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is the subset of pairs $ (\lambda, c) $ consisting of a linear ordering $ \lambda = \{i_1 < i_2 < \cdots < i_n\} $ on $ I $ and a function $ c \colon I \to \{\pm 1 \} $ satisfying: if  there is exactly one index $ i_k $ so that $ X_{i_k} = \mathfrak{m} $, either
        \begin{itemize}
            \item $ c(i_k) = 1 $, $ X_{j} = \mathfrak{a}_\ell $ for $ j < i_k $ and $ X_j = \mathfrak{a}_{r} $ for $ j > i_k $; or
            \item $ c(i_k) = - 1 $, $ X_{j} = \mathfrak{a}_\ell $ for $ j > i_k $ and $ X_j = \mathfrak{a}_{r} $ for $ j < i_k $ 
        \end{itemize}
        % if there is exactly one index $ i_k $ so that $ X_{i_k} = \mathfrak{m} $ and $ X_j = \mathfrak{a} $ for all $ j \neq i_k $, and $ \mathrm{Mul}_{\mathbf{BM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ is empty otherwise. 
        $ \mathrm{Mul}_{\mathbf{BM}_\sigma} \left(\{X_i\}_{i \in I}, Y\right) $ is the subset of pairs $ (\lambda, c) $ consisting of a linear ordering $ \lambda = \{i_1 < i_2 < \cdots < i_n\} $ on $ I $ and a function $ c \colon I \to \{\pm 1 \} $ satisfying: if  there is exactly one index $ i_k $ so that $ X_{i_k} = \mathfrak{m} $, $ c(i_k) = 1 $, $ X_{j} = \mathfrak{a}_\ell $ for $ j < i_k $ and $ X_j = \mathfrak{a}_{r} $ for $ j > i_k $. 
        \item The composition law on $ \mathbf{BM}_{\mathrm{inv}} $ is determined by the composition of linear orderings, with reversal of linear orderings according to Definition \ref{defn:colored_operad_monoid_with_involution}. 
        The composition law on $ \mathbf{BM}_{\sigma} $ is determined by the composition of linear orderings 
    \end{enumerate}
\end{definition} 
\begin{remark}\label{rmk:bimod_opd_involution}
    The colored operad $ \mathbf{BM}_{\mathrm{inv}} $ has a canonical involution $ \sigma $ which fixes $ \mathfrak{m} $, exchanges $ \mathfrak{a}_\ell $ and $ \mathfrak{a}_r $, and sends a morphism $ (\lambda, c) $ to $ (\lambda^{\mathrm{rev}}, I \xrightarrow{c} \{\pm 1\} \xrightarrow{\cdot (-1)} \{\pm 1 \}) $. 
\end{remark}
\begin{remark}\label{rmk:bimod_opd_to_inv_bimod_opd}
    There is a map of colored operads $ \iota \colon \mathbf{BM} \to \mathbf{BM}_{\mathrm{inv}} $ which sends $ \mathfrak{m} $ to $ \mathfrak{m} $ and sends $ \mathfrak{a}_{-} $ to $ \mathfrak{a}_\ell $ and $ \mathfrak{a}_+ $ to $ \mathfrak{a}_r $. 
    On $ \mathrm{Mul}_{\mathbf{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I}, \mathfrak{a}_{\pm}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\mathbf{BM}_\mathrm{inv}}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $  is $ \mathrm{id}_{\mathcal{L}I} \times \{ c_1\} $, this map agrees with $ \iota $ of Remark \ref{rmk:assoc_opd_to_assoc_inv_opd}. 
    On $ \mathrm{Mul}_{\mathbf{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I} \sqcup\{\mathfrak{m}\}, \mathfrak{m}\right) \subseteq  \mathcal{L}(I\sqcup \{j\}) \to \mathrm{Mul}_{\mathbf{BM}_{\mathrm{inv}}}\left(\left\{\mathfrak{a}_i\right\}_{i \in I} \sqcup \{\mathfrak{m}\}, \mathfrak{m}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ is the restriction of the map $ \mathrm{id}_{\mathcal{L}(I\sqcup \{j\})} \times \{ c_1\} $ where $ c_1 $ is the constant function on $ I \sqcup \{j\} $ with value $ 1 $. 

    There is \emph{also} a map of colored operads $ \iota^{\mathrm{rev}} \colon \mathbf{BM} \to \mathbf{BM}_{\mathrm{inv}} $ which sends $ \mathfrak{m} $ to $ \mathfrak{m} $ and  and sends $ \mathfrak{a}_{-} $ to $ \mathfrak{a}_r $ and $ \mathfrak{a}_+ $ to $ \mathfrak{a}_\ell $. 
    On $ \mathrm{Mul}_{\mathbf{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I}, \mathfrak{a}_{\pm}\right) \simeq  \mathcal{L}I \to \mathrm{Mul}_{\mathbf{BM}_{\mathrm{inv}}}\left(\left\{\mathfrak{a}_i\right\}_{i \in I}, \mathfrak{a}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $  is $ \mathrm{id}_{\mathcal{L}I} \times \{ c_1\} $, this map agrees with $ \iota^{\mathrm{rev}} $ of Remark \ref{rmk:assoc_opd_to_assoc_inv_opd}. 
    On $ \mathrm{Mul}_{\mathbf{BM}}\left(\left\{(\mathfrak{a}_{\pm})_i\right\}_{i \in I} \sqcup\{\mathfrak{m}\}, \mathfrak{m}\right) \subseteq  \mathcal{L}(I\sqcup \{j\}) \to \mathrm{Mul}_{\mathbf{BM}_\sigma}\left(\left\{\mathfrak{a}_i\right\}_{i \in I} \sqcup \{\mathfrak{m}\}, \mathfrak{m}\right) \simeq  \mathcal{L}I \times \{\pm 1\}^I $ is the restriction of the map $ \mathrm{rev}_{\mathcal{L}(I\sqcup \{j\})} \times \{ c_{-1}\} $ where $ c_{-1} $ is the constant function on $ I \sqcup \{j\} $ with value $ -1 $. 
\end{remark}
\begin{definition}\label{defn:inv_leftrightbimod_infty_operad}
    Let $ \mathcal{LM}_\mathrm{inv}^\otimes $, $ \mathcal{RM}_\mathrm{inv}^\otimes $, $ \mathcal{BM}_\mathrm{inv}^\otimes $, and $ \mathcal{BM}_\sigma^\otimes $ denote the $ \infty $-operads associated to the colored operads of Definitions \ref{defn:inv_leftmod_operad} and \ref{defn:inv_bimod_operad} (via Construction 2.1.1.7 and Example 2.1.1.21 of \cite{LurHA}).
\end{definition}
\begin{remark}
    We can describe the category $ \mathcal{LM}_\mathrm{inv}^\otimes $ as follows: 
    \begin{enumerate}[label=(\arabic*)]
        \item An object of $ \mathcal{LM}_\mathrm{inv}^\otimes $ is a pair $ (\langle n\rangle,S) $ where $ S $ is a subset of $ \langle n \rangle^\circ $. 
        \item Morphisms $ (\langle m \rangle, T) \to (\langle n \rangle,S) $ consist of a map $ (\alpha \colon \langle m \rangle \to \langle n \rangle, \lambda \colon \langle m \rangle^\circ \to \{\pm 1\}) $ in $ \Associnv^\otimes $ satisfying: 
        \begin{itemize}
            \item The map $ \alpha $ takes $ T \cup \{*\} $ to $ S \cup \{*\} $
            \item For each $ s \in S $, then $ \alpha^{-1}(\{s\}) $ contains exactly one element $ t_s $ of $ T $, and it is maximal (resp. minimal) with respect to the linear ordering on $ \alpha^{-1}(\{s\}) $ if $ \lambda (t_s) = 1 $ (resp. $ \lambda(t_s) = -1 $). 
        \end{itemize}
    \end{enumerate}
\end{remark}
\begin{remark}
    We can describe the category $ \mathcal{BM}_\mathrm{inv}^\otimes $ as follows: 
    \begin{enumerate}[label=(\arabic*)]
        \item An object of $ \mathcal{BM}_\mathrm{inv}^\otimes $ is a triple $ (\langle n\rangle,c_+, c_{-}) $ where $ c_{\pm} $ are functions $ \langle n \rangle^\circ \to \{0,1\} $ and $ c_{-}(i) \leq c_{+}(i) $ for all $ i \in \langle n \rangle^\circ $. 
        \item Morphisms $ (\langle m \rangle, c_+, c_{-}) \to (\langle n \rangle, c_{+}', c_{-}') $ consist of a map $ (\alpha \colon \langle m \rangle \to \langle n \rangle, \lambda \colon \langle m \rangle^\circ \to \{\pm 1\}) $ in $ \Associnv^\otimes $ satisfying: if $ j \in \langle n \rangle^\circ $ and $ \alpha^{-1}(j) = \{i_1 < i_2 < \cdots < i_\ell\} $,
        \begin{itemize}
             \item If $ c_{-} (j) = c_+(j) $, then 
                \begin{equation*}
                    c'_{-}(j) = c_{-}(i_1) \leq c_{+}(i_1) = c_{-}(i_2) \leq c_{+}(i_2) \cdots \cdots c_{-}(i_{m-1}) \leq c_{+}(i_m) = c'_{+}(j)
                \end{equation*}
            \item If $ c_{-} (j) < c_+(j) $, then there exists a unique $ k $ so that $ c_{-}(i_k) < c_{+}(i_k) $ and 
                \begin{equation*}
                \begin{split}
                    \lambda(i_k) \cdot c'_{-}(j) = \lambda(i_k) \cdot c_{-}(i_1) \leq \lambda(i_k) \cdot c_{+}(i_1) = \lambda(i_k) \cdot c_{-}(i_2) \leq \lambda(i_k) \cdot c_{+}(i_2)  \cdots \\ \lambda(i_k) \cdot c_{-}(i_{m-1}) \leq \lambda(i_k) \cdot c_{+}(i_m) = \lambda(i_k) \cdot c'_{+}(j)           
                \end{split}
                \end{equation*}
         \end{itemize} 
        % \begin{itemize}
        %     \item The map $ \alpha $ takes $ T \cup \{*\} $ to $ S \cup \{*\} $
        %     \item For each $ s \in S $, then $ \alpha^{-1}(\{s\}) $ contains exactly one element of $ t $. 
        % \end{itemize}
    \end{enumerate}
\end{remark}
\begin{remark}\label{rmk:inv_bimod_opd_to_inv_alg_opd} %compare Remark 4.2.1.5 in Higher algebra
    Each morphism $ \phi \in \mathrm{Mul}_{\mathbf{BM}_\mathrm{inv}} \left(\{X_i\}_{i \in I}, Y\right) $ determines a linear ordering $\ell $ on the set $ I $ and a function $ s \colon I \to \{\pm 1\} $. 
    Passing from $ \phi $ to the pair $ (\ell, s) $ determines a map of colored operads $ j \colon \mathbf{BM}_\mathrm{inv} \to \mathbf{Assoc}_\mathrm{inv} $. 
    The map $ j $ induces a morphism of $ \infty $-operads $  \mathcal{BM}_{\mathrm{inv}}^\otimes \to \Associnv^\otimes $ which we will also denote by $ j $. 
\end{remark} 
\begin{remark}\label{rmk:lmod_infty_opd_to_inv_lmod_infty_opd}
    The maps $ \iota, \iota^{\mathrm{rev}} $ of Remark \ref{rmk:lmod_opd_to_inv_lmod_opd} induce maps of $ \infty $-operads $ \iota \colon \mathcal{LM}^\otimes \to \mathcal{LM}^\otimes_{\mathrm{inv}} $ and $ \iota^{\mathrm{rev}} \colon \mathcal{RM}^\otimes \to \mathcal{LM}^\otimes_{\mathrm{inv}} $. 
\end{remark}
\begin{remark}\label{rmk:bimod_infty_opd_to_inv_bimod_infty_opd}
    The maps $ \iota, \iota^{\mathrm{rev}} $ of Remark \ref{rmk:bimod_opd_to_inv_bimod_opd} induce maps of $ \infty $-operads $ \iota, \iota^{\mathrm{rev}} \colon \mathcal{BM}^\otimes \to \BMinv^\otimes $. 
    There are canonical identifications $ \iota \circ \mathrm{rev} \simeq \sigma \circ \iota^{\mathrm{rev}} $ where $ \sigma $ is the involution on $ \BMinv^\otimes $ induced by Remark \ref{rmk:bimod_opd_involution} and $ \mathrm{rev} $ is the involution on $ \mathcal{BM}^\otimes $ of \cite[Construction 4.6.3.1]{LurHA}. 
\end{remark}
\begin{remark}\label{rmk:rmod_lmod_opd_to_inv_bimod_opd}
    There are canonical maps of $ \infty $-operads $ \mathcal{LM}^\otimes_{\mathrm{inv}} \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ and $ \mathcal{RM}^\otimes_{\mathrm{inv}} \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ sending $ \mathfrak{a} $ to $ \mathfrak{a}_\ell $, resp. $ \mathfrak{a}_r $ and making the diagram 
    \begin{equation*}
    \begin{tikzcd}[row sep=tiny]
        \mathrm{Assoc}^\otimes \ar[dd,"\sigma"] \ar[r] & \mathcal{LM}^\otimes_{\mathrm{inv}} \ar[dd,"{\mathrm{rev}}"] \ar[rd] & \\
        & & \mathcal{BM}^\otimes_{\mathrm{inv}}  \\ 
        \mathrm{Assoc}^\otimes  \ar[r] & \mathcal{RM}^\otimes_{\mathrm{inv}} \ar[ru] & 
    \end{tikzcd}   
    \end{equation*}
    commute, where $ \mathrm{rev} $ is (an involutive version of) the reversal involution of \cite[Remark 4.6.3.2]{LurHA}. 
\end{remark}
\begin{definition}\label{defn:leftrightbimodules_with_involution}
    Let $ \mathcal{C}^\otimes \to \Associnv^\otimes $ and $ \mathcal{D}^\otimes \to \Associnv^\otimes $ be fibrations of $ \infty $-operads and let $ \mathcal{M} $ be an $ \infty $-category. 
    Suppose given a fibration of $ \infty $-operads $ q \colon \mathcal{O}^\otimes \to \mathcal{LM}^\otimes_{\mathrm{inv}} $ together with equivalences $ \mathcal{O}^\otimes_{\mathfrak{a}} \simeq \mathcal{C}^\otimes $ and $ \mathcal{O}^\otimes_{\mathfrak{m}} \simeq \mathcal{M} $. 
    Let $ L\Modh\left(\mathcal{M}\right) $ denote the $ \infty $-category $ \Alg_{/\mathcal{LM}_{\mathrm{inv}}}\left(\mathcal{O}\right) $. 
    We will refer to $ L\Modh\left(\mathcal{M}\right) $ as the \emph{$\infty$-category of left hermitian module objects of $ \mathcal{M}$}. 

    Suppose given a fibration of $ \infty $-operads $ q \colon \mathcal{O}^\otimes \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ together with equivalences $ \mathcal{O}^\otimes_{\mathfrak{a}_\ell} \simeq \mathcal{C}^\otimes $, $ \mathcal{O}^\otimes_{\mathfrak{a}_R} \simeq \mathcal{D}^\otimes $ and $ \mathcal{O}^\otimes_{\mathfrak{m}} \simeq \mathcal{M} $. \Lucy{Lurie gives this a name (Definition 4.2.1.12 \emph{weakly enriched})--not sure what to call this. something \emph{bi-enriched}?}
    Let $ \Modh\left(\mathcal{M}\right) $ denote the $ \infty $-category $ \Alg_{/\mathcal{BM}_{\mathrm{inv}}}\left(\mathcal{O}\right) $. 
    We will refer to $ \Modh\left(\mathcal{M}\right) $ as the \emph{$\infty$-category of hermitian bimodule objects of $ \mathcal{M}$}. 
    Composition with the inclusions $ \Associnv^\otimes \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ induces a categorical fibration
    \begin{equation*}
        \Modh\left(\mathcal{M}\right) = \Alg_{/\mathcal{BM}_{\mathrm{inv}}}\left(\mathcal{O}\right) \to \Alg_{\Associnv}(\mathcal{C}) \times \Alg_{\Associnv}(\mathcal{D}) \,.
    \end{equation*}
    If $ A $ is an $ \Associnv $-algebra object of $ \mathcal{C} $, we let $ \Modh_A\left(\mathcal{M}\right) $ denote the fiber $ \Modh\left(\mathcal{M}\right) \times_{\Alg_{\Associnv}(\mathcal{C})} \{A\} $. 
    We will refer to $ \Modh_A\left(\mathcal{M}\right) $ as the \emph{$\infty$-category of hermitian $A$-bimodule objects of $ \mathcal{M} $}. 
\end{definition}
\begin{definition}
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ be a fibration of $ \infty $-operads. 
    We say that $ q $ exhibits $ \mathcal{O}_{\mathfrak{m}} $ as \emph{$ \EE_\sigma $-bitensored over $ \mathcal{O}_{\mathfrak{a}_\ell} $ and $ \mathcal{O}_{\mathfrak{a}_r} $} if $ q $ is a cocartesian fibration. 
\end{definition}
\begin{remark}\label{rmk:bitensored_cat_informal_description} % Compare Remark 4.2.1.21 in higher algebra
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ be a cocartesian fibration of $ \infty $-operads. 
    Then $ q $ is classified by a map $ \chi \colon \mathcal{BM}^\otimes_{\mathrm{inv}} \to \mathrm{Cat}_\infty $. 
    By Remark \ref{rmk:bimod_infty_opd_to_inv_bimod_infty_opd}, we can think of $ q $ as giving two $ \EE_\sigma $ algebras $ \mathcal{C} $, $ \mathcal{D} $ in $ \mathrm{Cat}_\infty $ with an $ \infty $-category $ \mathcal{M} $ equipped with both the structure of a $ \mathcal{C} $-$ \mathcal{D} $-bimodule (equivalently, the structure of a left $ \mathcal{C} \times \mathcal{D}_{\mathrm{rev}} $-module) and of a $ \mathcal{D} $-$ \mathcal{C} $-bimodule, and an autoequivalence $ \sigma_{\mathcal{M}} \colon \mathcal{M} \simeq \mathcal{M} $ of order two which is linear with respect to the autoequivalence $ \mathcal{C} \times \mathcal{D}_{\mathrm{rev}} \xrightarrow{\mathrm{flip}} \mathcal{D}_{\mathrm{rev}} \times \mathcal{C} \xrightarrow{\sigma_{\mathcal{D}}^{-1} \times \sigma_{\mathcal{C}}}  \mathcal{D} \times \mathcal{C}_{\mathrm{rev}} $. 
\end{remark}
\begin{remark} 
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{LM}^\otimes_{\mathrm{inv}} $ be a cocartesian fibration of $ \infty $-operads. 
    Consider a left hermitian module object $ F \colon \mathcal{LM}^\otimes_{\mathrm{inv}} \to \mathcal{O}^\otimes $. 
    By Remark \ref{rmk:rmod_lmod_opd_to_inv_bimod_opd}, $ F $ determines an associative algebra $ A $ of $ \mathcal{C} $ with an equivalence of algebras $ \sigma_A \colon A \simeq \sigma_{\mathcal{C}} (A)^{\mathrm{rev}} $, an object $ M \in \mathcal{M} $ so that $ M $ (resp. $ \sigma_{\mathcal{M}}(M) $) is equipped with the structure of a left $ A $-module (resp. right $ \sigma_{\mathcal{C}}(A) $-module). %and the structure of a right $ \sigma_{\mathcal{C}} (A) $-module on $ \sigma_{\mathcal{M}}(M) $. \Lucy{Want this to be a bimodule structure} 
    % By \cite[\S4.6.3]{LurHA}, equivalently $ M $ and $ \sigma_{\mathcal{M}}(M) $ both have the structure of a left $ A \otimes \sigma_{\mathcal{C}}(A)^{\mathrm{rev}} $-module.  
    Furthermore, we have an equivalence $ \sigma_{M} \colon M \simeq \sigma_{\mathcal{M}} (M) $ which is linear with respect to the equivalence $ A \xrightarrow{\sigma_A} \sigma_{\mathcal{C}}(A)^{\mathrm{rev}} $. 
    \Lucyil{is this related to ``modules with involution'' from \cite[\S3.1]{CDHHLMNNSI}?}
\end{remark}
\begin{remark}\label{rmk:inv_bimod_informal_description}
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{BM}^\otimes_{\mathrm{inv}} $ be a cocartesian fibration of $ \infty $-operads. 
    Consider a hermitian module object $ F \colon \mathcal{BM}^\otimes_{\mathrm{inv}} \to \mathcal{O}^\otimes $ and keep the notation of Remark \ref{rmk:bitensored_cat_informal_description}. 
    By Remark \ref{rmk:rmod_lmod_opd_to_inv_bimod_opd}, $ F $ determines an associative algebra $ A $ of $ \mathcal{C} $ with an equivalence of algebras $ \sigma_A \colon A \simeq \sigma_{\mathcal{C}} (A)^{\mathrm{rev}} $ and an associative algebra $ B $ of $ \mathcal{D} $ with an equivalence of algebras $ \sigma_B \colon B \simeq \sigma_{\mathcal{D}} (B)^{\mathrm{rev}} $, an object $ M \in \mathcal{M} $ so that $ M $ (resp. $ \sigma_{\mathcal{M}}(M) $) is equipped with the structure of a $ A $-$ B $-bimodule (resp. $ \sigma_{\mathcal{D}}(B) $-$ \sigma_{\mathcal{C}}(A) $-bimodule). %and the structure of a right $ \sigma_{\mathcal{C}} (A) $-module on $ \sigma_{\mathcal{M}}(M) $. \Lucy{Want this to be a bimodule structure} 
    % By \cite[\S4.6.3]{LurHA}, equivalently $ M $ and $ \sigma_{\mathcal{M}}(M) $ both have the structure of a left $ A \otimes \sigma_{\mathcal{C}}(A)^{\mathrm{rev}} $-module.  
    Furthermore, we have an equivalence $ \sigma_{M} \colon M \simeq \sigma_{\mathcal{M}} (M) $ which is linear with respect to the equivalence $ A \otimes B  \xrightarrow{\mathrm{flip}} B \otimes A \xrightarrow{\sigma_B^{-1} \otimes \sigma_A} \sigma_{\mathcal{D}}(B)^{\mathrm{rev}} \otimes \sigma_{\mathcal{C}}(A)^{\mathrm{rev}} $. 
    \Lucyil{when $ \mathcal{C} = \mathcal{D} $ and $ \sigma_{\mathcal{M}} $ and $ \sigma_{\mathcal{C}} $ are both the identity and $ A = B $, I think this recovers the ``module with involution'' from \cite[\S3.1]{CDHHLMNNSI}.}
\end{remark}
\begin{remark}\label{rmk:inv_alg_as_bimodule_over_itself}
    Let $ q \colon \mathcal{O}^\otimes \to \Associnv $ be a cocartesian fibration of $ \infty $-operads exhibiting $ \mathcal{C} $ as a monoidal $ \infty $-category with an involution $ \sigma_{\mathcal{C}} $. 
    Let us write $ \mathcal{C}^{\otimes}_{\pm} \to \mathcal{BM}^{\otimes} $ for the pullback of $ q $ the functors of Remark \ref{rmk:bimod_opd_to_inv_bimod_opd} and \ref{rmk:inv_bimod_opd_to_inv_alg_opd}. 
    Restriction along the functors of Remark \ref{rmk:bimod_opd_to_inv_bimod_opd} and \ref{rmk:inv_bimod_opd_to_inv_alg_opd} defines functors $ \Alg^\sigma(\mathcal{D}) \to \Modh(\mathcal{D}) \to \mathrm{BMod}(\mathcal{C}_{\pm}^\otimes) $ which is equivariant with respect to the action of $ \sigma_{\mathcal{C}} $ on the target. \Lucy{explain the action on $ \mathcal{C}_\pm $ or delete the last half of the sentence.}
    Moreover, there is a commutative diagram
    \begin{equation*}
    \begin{tikzcd}[column sep=large]
        \Alg^\sigma(\mathcal{D}) \ar[r] \ar[d,"{\Delta_\tau}"] & \Modh(\mathcal{D}) \ar[r] \ar[ld] & \mathrm{BMod}\left(\mathcal{C}^\otimes_{\pm}\right) \ar[d] \\
           \Alg^\sigma(\mathcal{D}) \times \Alg^\sigma(\mathcal{D}) \ar[r,"{(A,B) \mapsto A}"'] & \Alg^\sigma(\mathcal{D}) \ar[r] & \Alg(\mathcal{C}) \times \Alg(\mathcal{C}_{\mathrm{rev}})  
    \end{tikzcd}
    \end{equation*}
    where the right vertical arrow is the categorical fibration of \cite[Definition 4.3.1.12]{LurHA}, the central diagonal arrow is the categorical fibration of Definition \ref{defn:leftrightbimodules_with_involution}, and the left vertical arrow $ \Delta_\tau $ is the identity on one component and precomposition with the involution of Remark \ref{rmk:bimod_opd_involution}. 
    The total composite from the upper left to the lower right agrees with the forgetful functor of Remark \ref{rmk:naive_inv_alg_as_assoc_alg}. 
    If $ A \colon \Associnv \to \mathcal{O}^\otimes $ is an involutive algebra object (Definition \ref{defn:naive_involutive_algebras}), informally the functor sends $ A $ to $ A $, regarded as an $ A $-$ \sigma_{\mathcal{C}}(A) $-bimodule in the notation of Remark \ref{rmk:inv_bimod_informal_description} (compare \cite[Remark 4.2.1.17]{LurHA}). 
\end{remark}
\begin{construction}\label{cons:involutive_cut_module_operad}
    Define a functor $ \mathrm{MCut} \colon \Delta_\sigma^\op \to \mathcal{RM}^\otimes_{\mathrm{inv}} $: \Lucy{maybe this overloaded notation is not good. I'm running out of ideas.}
    \begin{itemize}
        \item For each $ ([n],s) $, we have $ \mathrm{MCut}([n],s) = \langle n + 1 \rangle \simeq \mathrm{RCut}_0([n]) $ where $ \mathrm{RCut} $ is from \cite[Construction 4.8.4.4]{LurHA}. 
        \item Given a morphism $ \alpha\colon ([n],s) \to ([m], t) $, the associated morphism $ \mathrm{MCut}([m], t) \to \mathrm{MCut} ([n],s) $ consists of
        \begin{itemize}
            \item On underlying finite pointed sets $ \langle m+1\rangle \to \langle n+1 \rangle $, $ \mathrm{MCut} $ agrees with (the reverse of) that appearing in \cite[Construction 4.2.2.6]{LurHA}
            \item Identifying the cut $ \{k \mid k< j\} \sqcup \{k \mid k \geq j \} $ with the morphism $ j-1 < j $, we may regard $ s \colon \langle n+1\rangle^\circ \to \{\pm 1\} $ and likewise $ t \colon \langle m+1\rangle^\circ \to \{\pm 1\} $. \Lucy{check later}
            Define $ u\colon \mathrm{MCut}(\alpha)^{-1}\left(\langle n+1\rangle^\circ\right) \to \{\pm 1\} $ to be the unique function so that $ u(j)t(j) = s(\mathrm{MCut}(\alpha)(j)) $. 
            % This means that $ \alpha^{-1}(\{k \mid k< j\}) $ and $ \alpha^{-1}(\{k \mid k \geq j\}) $ 
        \end{itemize}
    \end{itemize}
\end{construction}
\begin{remark}\label{rmk:nat_transformation_of_cut_functors} % compare remark 4.2.2.8
    We can identify $ \Associnv^\otimes $ with the full subcategory of $ \mathcal{RM}^\otimes_{\mathrm{inv}} $ spanned by objects of the form $ (\langle n\rangle, \langle n\rangle^\circ) $. 
    We can regard Construction \ref{cons:involutive_cut} as defining a functor $ \Delta^\op_\sigma \to \mathcal{RM}^\otimes_{\mathrm{inv}} $. 
    For each $ ([n], s) \in \Delta^\op_\sigma $, there is a map of sets $ \theta \colon \mathrm{MCut} ([n], s) \to \mathrm{Cut}([n], s) $ defined as in \cite[Remark 4.2.2.8]{LurHA}. 
    Concretely, on underlying pointed sets, $ \theta $ takes the form \Lucy{check that the signs $s$ work out!}
    \begin{equation*}
    \begin{split}
        \theta \colon \langle n+1 \rangle &\to \langle n \rangle \\
                            k &\mapsto \begin{cases}
                                k-1 & \text{ if }k>0 \\
                                * & \text{ if }k = 0, * \,.
                            \end{cases}
    \end{split}    
    \end{equation*} 
    This construction determines a morphism $ \gamma $ in the $ \infty $-category $ \Fun\left(\Delta^\op_\sigma, \mathcal{RM}^\otimes_{\mathrm{inv}}\right) $, or equivalently a map $ \gamma \colon \Delta^\op_\sigma \times \Delta^1 \to \mathcal{RM}^\otimes_{\mathrm{inv}} $. 
\end{remark}
\begin{lemma}\label{lemma:involutive_cut_is_approx_on_module_operad}
    The morphism $ \gamma \colon \Delta^\op_\sigma \times \Delta^1 \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ defined in Remark \ref{rmk:nat_transformation_of_cut_functors} exhibits $\Delta^\op_\sigma \times \Delta^1 $ as an approximation to the $ \infty $-operad $ \mathcal{RM}^\otimes_{\mathrm{inv}} $. 
\end{lemma}
\begin{definition}\label{defn:involutive_planar_module}
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ be a fibration of $ \infty $-operads, so $ q $ exhibits $ \mathcal{M}:= \mathcal{O}^\otimes_{\mathfrak{m}} $ as weakly bi-enriched over $ \mathcal{O}^\otimes_{\mathfrak{a}} $. 
    Let $ \gamma $ be as in Remark \ref{rmk:nat_transformation_of_cut_functors}. 
    Let $ R\Modh^{\AA^\sigma_\infty}(\mathcal{M}) $ denote the full subcategory of $ \Fun_{\mathcal{RM}^\otimes_{\mathrm{inv}}}\left(\Delta^\op_\sigma \times \Delta^1,\mathcal{O}^\otimes\right) $ spanned by those maps $ f \colon \Delta^\op_\sigma \times \Delta^1 \to \mathcal{O}^\otimes $ satisfying 
    \begin{enumerate}
        \item The restriction of $ f $ to $ \Delta^\op_\sigma \times \{1\} $ belongs to $ \Alg_{\AA^\sigma_\infty}(\mathcal{O}) $ of Definition \ref{defn:inv_planar_alg}
        \item If $ \alpha \colon ([m], s)\to ([n], t) $ so that $ \alpha(0) = 0 $, then the induced map $ f ([m], s, 0)\to f([n], t, 0) $ is an inert map in $ \mathcal{O}^\otimes $
        \item for each object $ ([n], s) $ in $ \Delta^\op_\sigma $, the induced map $ f ([n], s, 0) \to f([n], s, 1) $ is an inert map in $ \mathcal{O}^\otimes $
    \end{enumerate}
\end{definition}
\begin{example}
    \Lucy{see Example 4.2.1.17 of higher algebra} 
    Let $ \mathcal{C}^\otimes \to \mathcal{RM}^\otimes $ be a fibration of $ \infty $-operads. 
    Restriction along the map\Lucy{fibration?} of $ \infty $-operads $ \mathcal{RM}^\otimes_{\mathrm{inv}} \to \Associnv^\otimes $ induced by Remark \ref{rmk:inv_bimod_opd_to_inv_alg_opd} induces a map $ \EE_\sigma\Alg\left(\mathcal{C}\right) \to R\Modh\left(\mathcal{C}\right) $ which is a section of the projection map $ R\Modh\left(\mathcal{C}\right) \to \EE_\sigma\Alg\left(\mathcal{C}\right) $. 
\end{example}
\begin{notation}\label{ntn:E_sigma_tensored_cat_variant} % basically lifted straight from Higher algebra 4.2.2.17
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ be a fibration of $ \infty $-operads, so $ q $ exhibits $ \mathcal{M}:= \mathcal{O}^\otimes_{\mathfrak{m}} $ as weakly bi-enriched over $ \mathcal{O}^\otimes_{\mathfrak{a}} $. 
    Define a new simplicial set $ \overline{\mathcal{M}}^\varoast $ by the following universal property
    \begin{equation*}
        \hom_{\sSet_{/\Delta^{\op}_\sigma}} \left(K, \overline{\mathcal{M}}^\varoast \right) \simeq \hom_{\sSet_{/\mathcal{RM}^\otimes_{\mathrm{inv}}}}\left(K \times \Delta^1 , \mathcal{O}^\otimes\right) \,.
    \end{equation*}
    Here we regard $ K \times \Delta^1 $ as a simplicial set over $ \mathcal{RM}^\otimes_{\mathrm{inv}} $ via the composite $ K \times \Delta^1 \to \Delta^\op_{\sigma} \times \Delta^1 \xrightarrow{\gamma} \mathcal{RM}^\otimes_{\mathrm{inv}} $ where $ \gamma $ is from Remark \ref{rmk:nat_transformation_of_cut_functors}. 

    Unwinding definitions, we see that a vertex in $ \overline{\mathcal{M}}^\varoast $ lying over an object $ ([n], s \colon \{1, \ldots, n\} \to \{\pm 1\}) \in \Delta^\op_{\sigma} $ corresponds to a morphism $ \alpha $ in $ \mathcal{O}^\otimes $ whose image in $ \mathcal{RM}^\otimes_{\mathrm{inv}} $ is the map $ (\langle n+1\rangle, \{0\}) \to (\langle n\rangle, \varnothing) $\Lucy{this might be off--revisit later!}.   
    Now let $ \mathcal{M}^\varoast $ denote the full simplicial subset of $ \overline{\mathcal{M}}^\varoast  $ spanned by those vertices for which $ \alpha $ is inert. 
\end{notation}
\begin{remark}
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ be a fibration of $ \infty $-operads, so $ q $ exhibits $ \mathcal{M}:= \mathcal{O}^\otimes_{\mathfrak{m}} $ as weakly enriched over $ \mathcal{O}^\otimes_{\mathfrak{a}} $. 
    By \cite[Example 4.3.1.4 \& Proposition 4.3.2.15]{HTT}, composition with the inclusion $ \{0\} \to \Delta^1 $ induces a trivial Kan fibration $ \mathcal{M}^\varoast \xrightarrow{\sim} \mathcal{O}^\otimes \times_{\mathcal{RM}^\otimes_{\mathrm{inv}}} \Delta^\op_\sigma $. \Lucy{Jacob explains this in a really terse way--just by citing Prop 4.3.2.15 of HTT. It does just follow from definitions/observations, but there are many (for instance, definition of inert edge).}
    In particular, the fiber of $ \mathcal{M}^\varoast $ over an object $ ([n], s) \in \Delta^\op_\sigma $ is canonically equivalent to $ \mathcal{M} \times \mathcal{C}^{\times n} $. 

    Finally, since $ q $ is a categorical fibration and categorical fibrations are closed under pullback and composition with trivial fibrations, $ q $ induces categorical fibrations $ \mathcal{M}^\varoast \to \mathcal{C}^\varoast \to \Delta^\op_\sigma $.     
\end{remark}
\begin{lemma} % Compare Lemma 4.2.2.20 of Higher algebra
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ be a cocartesian fibration of $ \infty $-operads, so $ q $ exhibits $ \mathcal{M}:= \mathcal{O}^\otimes_{\mathfrak{m}} $ as tensored over $ \mathcal{O}^\otimes_{\mathfrak{a}} $. 
    Then the associated functor $ \mathcal{M}^\varoast  \to \mathcal{C}^\varoast $ (Notation \ref{ntn:E_sigma_monoidal_cat_variant}) is a locally coCartesian fibration.     
\end{lemma}
\begin{proposition}
    Let $ q \colon \mathcal{O}^\otimes \to \mathcal{RM}^\otimes_{\mathrm{inv}} $ be a cocartesian fibration of $ \infty $-operads, so $ q $ exhibits $ \mathcal{M}:= \mathcal{O}^\otimes_{\mathfrak{m}} $ as tensored over $ \mathcal{O}^\otimes_{\mathfrak{a}} $. 
    Then precomposition with the functor $ \mathrm{MCut} $ of Construction \ref{cons:involutive_cut_module_operad} induces an equivalence of $ \infty $-categories
    \begin{equation*}
        R\Modh(\mathcal{M}) \simeq \Alg_{/\mathcal{RM}_{\mathrm{inv}}}(\mathcal{O}) \xrightarrow{\sim} R\Modh^{\AA_\infty^\sigma}\left(\mathcal{M}\right)\,.
    \end{equation*}
\end{proposition}
\begin{proof}
    Combine Lemma \ref{lemma:involutive_cut_is_approx_on_module_operad} with \cite[Theorem 2.3.3.23]{LurHA}. 
\end{proof} 
\begin{definition}
    \href{https://arxiv.org/abs/2504.02143}{Introduction to section 3.4 here} gives a recipe for defining $ \mathbb{E}_\sigma^\otimes $ as a genuine/parametrized $ \infty $-operad. 
    Relate the `underlying' $ \infty $-operad with $ C_2 $-action to $ \Associnv $? 
\end{definition} 
\Lucyil{Unravel what it means to be $ \mathbb{E}_\sigma $-monoidal in a genuine way!}
\begin{lemma}
    Let $ R $ be a Poincaré ring. 
    Then $ \mathrm{He}(\Mod_R^\omega,\Qoppa_R) \to \mathrm{He}\left(\mathrm{Hyp}(\Mod_R^\omega)\right) $ is canonically endowed with the structure of an $ \mathbb{E}_\sigma $-monoidal $ C_2 $-$ \infty $-category. 
    Recall that $ \mathrm{He}\left(\mathrm{Hyp}(\Mod_R^\omega)\right) \simeq \mathrm{TwAr}(\Mod_R^\omega) $ by \cite[\S2.2]{CDHHLMNNSI}. 
\end{lemma}
\Lucyil{What does it mean for a $ C_2 $-$ \infty $-category to be tensored over a $ \mathbb{E}_\sigma $-monoidal $ C_2 $-$ \infty $-category? Show that if $ (\mathcal{C},\Qoppa) $ is an $ R $-linear Poincaré $ \infty $-category, then $ \mathrm{He}(\mathcal{C},\Qoppa) \to \mathrm{He}(\mathcal{C}^e) $ is an $ \mathbb{E}_\sigma $-linear/-tensored over $ \underline{He}\left(\Mod_R^\omega\right) $?}

\subsection{Part (b)} 
\begin{proposition} \Lucy{This statement is \cite[Proposition 4.2.3.1]{LurHA} with some words changed; no claim of originality here.}
    Let $ \mathcal{C} $ be an involutive monoidal $ \infty $-category and let $ \mathcal{M} $ be an $ \infty $-category which is bitensored over $ \mathcal{C} $. 
    Let $ K $ be a simplicial set so that $ \mathcal{M} $ admits $ K $-indexed limits, and let $ \theta \colon R\Modh(\mathcal{M}) \to \Alg^\sigma(\mathcal{C}) $ be the forgetful functor. 
    Then
    \begin{enumerate}[label=(\arabic*)]
        \item For every commutative square 
        \begin{equation*}
        \begin{tikzcd}
            K \ar[r] \ar[d] & R\Modh(\mathcal{M})  \ar[d,"\theta"] \\
            K^{\triangleleft} \ar[r] \ar[ru,dashed] & \Alg^\sigma(\mathcal{C}) \,,
        \end{tikzcd}
        \end{equation*}
        there exists a dashed arrow which is a $ \theta $-limit diagram. 
        \item An arbitrary map $ \overline{g} \colon K^{\triangleleft} \to R\Modh(\mathcal{M}) $ is a $ \theta $-limit diagram if and only if the induced map $ K^{\triangleleft} \to \mathcal{M} $ is a limit diagram.   
    \end{enumerate}
\end{proposition}
\begin{proof}
    \Lucy{todo}
\end{proof}
\begin{corollary}
    $ \theta $ is a cartesian fibration, and a morphism $ f \colon \Delta^1 \to R\Modh(\mathcal{M}) $ is $ \theta $-cartesian if and only if the image of $ f $ in $ \mathcal{M} $ is an equivalence.     
\end{corollary}
\begin{corollary}
    Let $ \mathcal{C} $ be an involutive monoidal $ \infty $-category and let $ \mathcal{M} $ be an $ \infty $-category which is bitensored over $ \mathcal{C} $. 
    Let $ K $ be a simplicial set so that $ \mathcal{M} $ admits $ K $-indexed limits, and let $ \theta \colon R\Modh(\mathcal{M}) \to \Alg^\sigma(\mathcal{C}) $ be the forgetful functor. 
    Let $ A $ be an involutive algebra object of $ \mathcal{C} $. 
    Then
    \begin{enumerate}[label=(\arabic*)]
        \item $ R\Modh_A(\mathcal{M}) $ admits $ K $-indexed limits. 
        \item A diagram $ K^{\triangleleft} \to R\Modh_A(\mathcal{M}) $ is a limit diagram if and only if the induced diagram $ K^{\triangleleft} \to \mathcal{M} $ is a limit diagram. 
        \item Given a morphism $ A \to B $ of involutive algebra objects of $ \mathcal{C} $, the induced functor $ R\Modh_B(\mathcal{M}) \to R\Modh_A(\mathcal{M}) $ preserves $ K $-indexed limits. 
    \end{enumerate}
\end{corollary}
\subsection{Towards (e)}
\begin{construction}
    Define a functor $ \mathrm{Pr}\colon \mathbf{LM}_{\mathrm{inv}}^\otimes \times \mathbf{RM}_{\mathrm{inv}}^\otimes \to \mathbf{BM}_{\mathrm{inv}}^\otimes $. 
\begin{enumerate}[label=(\arabic*)]
    \item Let $ (\langle m\rangle, S) $ be an object of $ \mathbf{LM}_{\mathrm{inv}}^\otimes $ and let $ ( \langle n \rangle, T) $ be an object of $ \mathbf{RM}_{\mathrm{inv}}^\otimes $. 
    Let $ \mathrm{Pr}((\langle m\rangle, S), (\langle n\rangle, T)) = (X_*, c_{-}, c_{+}) $ where $ X_*, c_{-}, c_{+} $ are described in \cite[Construction 4.3.2.1(1)]{LurHA}. 
    \item Let $ (\alpha, \lambda) \colon (\langle m\rangle, S) \to (\langle m'\rangle, S') $ be a morphism in $ \mathbf{LM}_{\mathrm{inv}}^\otimes $ and let $ (\beta, \mu) \colon (\langle n\rangle, T) \to (\langle n'\rangle, T') $ be a morphism in $ \mathbf{RM}_{\mathrm{inv}}^\otimes $. 
    Write $ \mathrm{Pr}((\langle m'\rangle, S'), (\langle n'\rangle, T')) = (X_*', c_{-}', c_{+}') $. 
    Then $ \mathrm{Pr}\left((\alpha, \lambda),(\beta, \mu)\right) $ is the unique morphism in $ \mathbf{BM}_{\mathrm{inv}}^\otimes $ lying over the map $ \gamma \colon X_* \to X_*' $ described by 
    \begin{enumerate}[label=(\roman*)]
        \item $ \displaystyle \gamma(i,j) = \begin{cases}
            (\alpha(i), \beta(j)) & \text{ if } \alpha(i) \in \langle m' \rangle^\circ, \beta(j) \in \langle n' \rangle^\circ \\
            * & \text{ otherwise. }
        \end{cases} $
        \item Let $ i' \in \langle m' \rangle^\circ \setminus S' $ and $ j' \in T' $ so $ j' = \beta(j) $ for a unique $ j \in T $. 
        Then the linear ordering on $ \gamma^{-1}(i', j') = \alpha^{-1}(i') \times \{j\} $ is (a) determined by the map $ \alpha $ if $ \mu(j) = 1 $, and (b) it is the reverse of the linear ordering determined by $ \alpha $ if $ \mu(j) = -1 $. 
        The map $ \gamma^{-1}(i', j') = \alpha^{-1}(i') \times \{j\} \to \{\pm 1\} $ is determined by $ \lambda $ if $ \mu(j) = 1 $ and it is $ -\lambda $ if $ \mu(j ) = -1 $. 
        \item Likewise if $ i' \in S' $ and $ j' \in \langle n' \rangle^\circ \setminus T' $ 
        \item Let $ i' \in S' $ and $ j' \in T' $ so $ i' = \alpha(i) $ for a unique $ i \in S $ and $ j' = \beta(j) $ for a unique $ j \in T $. 
        Then $ \gamma^{-1} \{(i',j')\} = \{i\} \times \beta^{-1}\{(j')\} \sqcup_{\{(i,j)\}} \alpha^{-1}\{(i')\} \times \{j\} $. 
        Define $ \gamma^{-1} \{(i',j')\} \to \{\pm 1\} $ by $ \lambda \times \mu $. 
        Endow $ \gamma^{-1} \{(i',j')\} $ with the linear ordering from \cite[Construction 4.3.2.1(2)(iv)]{LurHA} if $ \lambda(i) = \mu(j) $ and endow $ \gamma^{-1} \{(i',j')\} $ with the opposite ordering if $ \lambda(i) \neq \mu(j) $ (or equivalently, if $\lambda(i) = -\mu(j) $). 
    \end{enumerate}
\end{enumerate}
    Write $ \mathrm{Pr} $ for the induced map $ \mathcal{LM}^\otimes_\sigma \times \mathcal{RM}^\otimes_\sigma \to \mathcal{BM}^\otimes_\sigma $ of $ \infty $-categories. 
\end{construction}
\begin{construction}
    Let $ q \colon \mathcal{C}^\otimes \to \mathcal{BM}^\otimes_\sigma $ be a fibration of $ \infty $-operads. 
    We define a map of simplicial sets $ \overline{L\Modh}(\mathcal{C}_{\mathfrak{m}})^\otimes \to \mathcal{RM}^\otimes_\sigma $ by the universal property: For any simplicial set $ K \to \mathcal{RM}^\otimes_\sigma $, there is a bijection
    \begin{equation*}
        \mathrm{Hom}_{\mathrm{sSet}_{/\mathcal{RM}^\otimes_\sigma}}\left(K,\overline{L\Modh}(\mathcal{C}_{\mathfrak{m}})^\otimes \right) \simeq  \mathrm{Hom}_{\mathrm{sSet}_{/\mathcal{BM}^\otimes_\sigma}}\left(\mathcal{LM}^\otimes_\sigma \times K, \mathcal{C}^\otimes \right)\,.
    \end{equation*}
    Let $ L\Modh(\mathcal{C}_{\mathfrak{m}})^\otimes $ denote the full simplicial subset of $ \overline{L\Modh}(\mathcal{C}_{\mathfrak{m}})^\otimes $ spanned by those vertices which correspond to a vertex $ X \in \mathcal{RM}^\otimes_\sigma $ and a functor $ F \colon \mathcal{LM}^\otimes_\sigma \{X\} \to \mathcal{BM}^\otimes_\sigma $ which takes inert morphisms in $ \mathcal{LM}^\otimes_\sigma $ to inert morphisms in $ \mathcal{BM}^\otimes_\sigma $. 
\end{construction}
\begin{remark}
   The composite $ \mathcal{LM}^\otimes_\sigma \times \{\mathfrak{m}\} \hookrightarrow \mathcal{LM}^\otimes_\sigma \times \mathcal{RM}^\otimes_\sigma \xrightarrow{\mathrm{Pr}} \mathcal{BM}^\otimes_\sigma $ agrees with the inclusion of Remark \ref{rmk:rmod_lmod_opd_to_inv_bimod_opd}. 
   Taking $ K \to \mathcal{RM}^\otimes_\sigma $ to be the inclusion $ \{\mathfrak{m}\} \hookrightarrow \mathcal{RM}^\otimes_\sigma $, we have an isomorphism of simplicial sets $ L\Modh(\mathcal{C}_{\mathfrak{m}})^\otimes \times_{\mathcal{RM}^\otimes_\sigma} \{\mathfrak{m}\} \simeq L\Modh(\mathcal{C}_{\mathfrak{m}}) $ where $ L\Modh(\mathcal{C}_{\mathfrak{m}}) $ is the $ \infty $-category of left modules associated to the fibration of $ \infty $-operads $ \mathcal{C}^\otimes \times_{\mathcal{BM}^\otimes_{\sigma}} \mathcal{LM}^\otimes_\sigma \to \mathcal{LM}^\otimes_\sigma $. 
\end{remark} 
\begin{proposition}
    Let $ q \colon \mathcal{C}^\otimes \to \mathcal{BM}^\otimes_\sigma $ be a fibration of $ \infty $-operads. Then
    \begin{enumerate}[label=(\arabic*)]
        \item the induced map $ p \colon L\Modh(\mathcal{C}_{\mathfrak{m}})^\otimes \to \mathcal{RM}^\otimes_\sigma $ is a fibration of $ \infty $-operads 
        \item a morphism $ \alpha $ in $ L\Modh(\mathcal{C}_{\mathfrak{m}})^\otimes $ is inert if and only if $ p (\alpha) $ is inert in $ \mathcal{RM}^\otimes_\sigma $ and for all $ X \in \mathcal{LM}_\sigma $, $ \alpha(X) $ is an inert morphism in $ \mathcal{C}^\otimes $. 
        \item if $ q $ is a cocartesian fibration of $ \infty $-operads, then so is $ p $
        \item if $ q $ is a cocartesian fibration of $ \infty $-operads, a morphism $ \alpha $ in $ L\Modh(\mathcal{C}_{\mathfrak{m}})^\otimes $ is $ p $-cocartesian if and only if, for all $ X \in \mathcal{LM}^\otimes_\sigma $, $ \alpha(X) $ is $ q $-cocartesian in $ \mathcal{C}^\otimes $. 
    \end{enumerate}
\end{proposition}
\begin{proof}
    Similar to \cite[Proposition 4.3.2.5]{LurHA}.    
\end{proof}
\begin{theorem}
    Let $ \mathcal{C} $ be an $ \EE_\sigma $-monoidal $ \infty $-category, and let $ A $ be an $ \EE_\sigma $-algebra in $ \mathcal{C} $. 
    Then $ L\Modh_A(\mathcal{C}) $ is right $ \EE_\sigma $-tensored over $ \mathcal{C} $. 
\end{theorem}

\subsection{Endomorphisms} 
Let $ \mathcal{C} $ be an $ \EE_\sigma $-monoidal $ \infty $-category, and write $ \sigma_{\mathcal{C}} \colon \mathcal{C} \xrightarrow{\sim} \mathcal{C} $ for its involution. 
Suppose $ M \in \mathcal{C} $ is an object equipped with an equivalence $ \sigma_M \colon M \simeq \sigma_{\mathcal{C}}(M) $. 
By \cite[\S4.7.1]{LurHA}, endomorphisms of $ M $ can be regarded as an $ \EE_1 $-algebra in $ u\left(\mathcal{C}\right)^{\otimes} $, where $ u $ is from Remark \ref{rmk:assoc_inv_mon_cat_as_mon_cat_with_autoequiv}. 
Now $ \sigma_{M} $ induces an equivalence $ \mathrm{End}_{\mathcal{C}}(M) \simeq \mathrm{End}_{\mathcal{C}}(\sigma_{\mathcal{C}} (M)) $
On the other hand, $ \sigma_{\mathcal{C}} $ induces an equivalence $ \mathrm{End}_{\mathcal{C}}(\sigma_{\mathcal{C}} (M)) \simeq \mathrm{End}_{\mathcal{C}}(M)^{\mathrm{rev}} $. 
In particular, for any $ \infty $-category $ \mathcal{M} $ left $ \EE_\sigma $-tensored over $ \mathcal{C} $ and any object $ M \in \mathcal{M} $ which is fixed by the involution on $ \mathcal{M} $, we expect the endomorphisms of $ M $ to admit the structure of an $ \EE_\sigma $-algebra in $ \mathcal{C} $. 

To this end, we will define an $ \infty $-category of objects acting on $ M $, show that it has an $ \EE_\sigma $-monoidal structure, and locate endomorphisms of $ M $ as the final object in this $ \infty $-category. 
Informally, we may define a category $ \mathcal{C}[M] $ whose objects consist of either
\begin{itemize}
    \item pairs $ (C, \eta) $ where $ C \in \mathcal{C} $ and $ \eta \colon C \otimes M \to M $ is a morphism in $ \mathcal{M} $; or
    \item pairs $ (C', \eta') $ where $ C'\in \mathcal{C} $ and $ \eta' \colon \sigma_{\mathcal{M}}(M) \otimes C' \to \sigma_{\mathcal{M}}(M) $. 
    \item pairs $ (D, \xi) $ where $ D \in \mathcal{C} $ and $ \xi \colon M \otimes D \to \sigma_{\mathcal{M}}(M) $ \Lucy{added July 26th}
    \item pairs $ (D, \xi') $ where $ D \in \mathcal{C} $ and $ \xi' \colon D \otimes \sigma_{\mathcal{M}}(M) \to M $ 
\end{itemize} 
The monoidal structure is as described in \cite[\S4.7.1]{LurHA}. 
Note that given an object $ (C, \eta) $, the involution $ \sigma_\mathcal{M} $ on $ \mathcal{M} $ sends $ \eta $ to the map $ \sigma_{\mathcal{M}}\left(C \otimes M\right)\simeq \sigma_{\mathcal{M}}(M) \otimes \sigma_{\mathcal{C}}(C) \to \sigma_{\mathcal{M}}(M) $. 
Given an object $ (D, \xi) $, the involution $ \sigma_\mathcal{M} $ on $ \mathcal{M} $ we may consider the map $ \xi' \colon \sigma_{\mathcal{C}}(D) \otimes M \xrightarrow{\mathrm{id} \otimes {\sigma_M}} \sigma_{\mathcal{C}}(D) \otimes \sigma_{\mathcal{M}}^2(M) \simeq \sigma_{\mathcal{M}}\left(M \otimes D\right)\xrightarrow{\sigma_{\mathcal{M}}(\xi)} \sigma_{\mathcal{M}}(M) $. 
The assignment $ (D,\xi) \mapsto (\sigma_{\mathcal{C}}(D), \xi') $... \Lucy{is an involution?} 
This is the involution on $ \mathcal{C}[M] $. 
\begin{definition}
    Let $ p \colon \mathcal{M}^\varoast  \to \Delta^1\times \Delta^\op_\sigma $ exhibit $ \mathcal{M}^\varoast $ as weakly enriched over $ \mathcal{C}^\varoast $. 
    An \emph{enriched morphism} of $ \mathcal{M} $ is a diagram 
    \begin{equation*}
        M \xleftarrow{\alpha} X \xrightarrow{\beta} N
    \end{equation*}
    satisfying either 
    \begin{itemize}
        \item $ p (\alpha) $ is the morphism $ (0, [1], c_{1}) \to (0,[0]) $ in $ \Delta^\op_\sigma $ determined by the embedding $ [0] \simeq \{0\} \hookrightarrow [1] $ and $ c_1 \colon \{1\} \to \{\pm 1\} $ is the constant function at $ +1 $, and
        \item the map $ \beta $ is inert, and $ p(\beta) $ is the morphism $ (0,[1], c_{1}) \to (0, [0]) $ in $ \Delta^1 \times \Delta^\op_\sigma $ determined by the embedding $ [0]\simeq \{1\} \hookrightarrow [1] $
    \end{itemize}
    or
    \begin{itemize}
        \item $ p (\alpha) $ is the morphism $ (0, [1], c_{-1}) \to (0,[0]) $ in $ \Delta^\op_\sigma $ determined by the embedding $ [0] \simeq \{0\} \hookrightarrow [1] $ and $ c_{-1} \colon \{1\} \to \{\pm 1\} $ is the constant function at $ -1 $. 
        \item the map $ \beta $ is inert, and $ p(\beta) $ is the morphism $ (0,[1], c_{-1}) \to (0, [0]) $ in $ \Delta^1 \times \Delta^\op_\sigma $ determined by the embedding $ [0]\simeq \{1\} \hookrightarrow [1] $
    \end{itemize}
    Let $ \mathrm{Str}\, \mathcal{M}^{\mathrm{en}}_{[1]} $ denote the full subcategory of $ \Fun_{\Delta^1 \times \Delta^\op_\sigma }\left(\Lambda^2_0, \mathcal{M}^{\varoast} \right) $ spanned by the enriched morphisms of $ \mathcal{M} $. 

    Note that there are two evaluation functors $ \mathrm{Str}\, \mathcal{M}^{\mathrm{en}}_{[1]} \to \mathcal{M} $. 
    Given $ M \in \mathcal{M} $, write $ \mathcal{C}[M] := \{M\} \times_{\mathcal{M}} \mathrm{Str}\, \mathcal{M}^{\mathrm{en}}_{[1]} \times_{\mathcal{M}} \{M\} $ and refer to it as the endomorphism $ \infty $-category of $ M $. 
\end{definition} 
\begin{definition}
    \emph{enriched $ n $-string} 
\end{definition}
\begin{proposition}
    [Segal condition] 
\end{proposition}
In the course of thinking about the `involutive' generalization of the statement that given an $ \EE_1 $-algebra, its category of modules is $ \EE_0 $ (and conversely, that given an object in a stable $\infty$-category, that its endomorphism spectrum is an $ \EE_1 $-algebra), I have run up against some questions. 
\begin{question}
\begin{itemize}
    \item Can we sidestep an involutive version of the construction of endomorphism categories of \cite[\S4.7.1]{LurHA}? 
    \item Suppose $ \mathcal{C} $ is a monoidal $ \infty $-category and $ \mathcal{M} $ is an $ \infty $-category which is enriched over $ \mathcal{C} $ in the sense of \cite[\S4.2.1]{LurHA}. 
    The opposite category $ \mathcal{M}^\op $ is enriched over $ \mathcal{C} $ by \cite[\S10]{Heine_2023}.   
\end{itemize}
\end{question}

\section{Poincaré structures on module categories} 
The assignment $ A \mapsto \Mod_A $ sending an associative algebra to its category of left modules is functorial in $ A $: Given a map of algebras $ A \to B $, $ B \otimes_A (-) $ defines a functor $ \Mod_A \to \Mod_B $. 
This observation/fact is simultaneously simple/basic and fundamental: It allows one to define quasi-coherent sheaves on a scheme $ X $ as a limit over affine open covers, and to formulate effective descent for modules. 
In this section, we consider what it means to extend this functoriality to module categories with Poincaré structure. 

Note that a lift of $ \Mod_A^\omega $ to $ \Catp $ or $ \Cath $ is additional data: by \cite[Theorem 3.3.1]{CDHHLMNNSI}, this equivalent to the data of a module with genuine involution over $ A $. 
We begin by defining an $ \infty $-category whose objects are associative algebras with the required additional structure; in order to handle the coherences involved, we use the language of ($ C_2 $-)$ \infty $-operads. 
Next, we construct a functor from said category to $ \Cath $ and show that it factors through $ \Catp $. 
Finally, in \S\ref{subsection:calgp_operadic} we show that the category $ \CAlgp $ admits a forgetful functor to these structured associative algebras by showing that $ \CAlgp $ is equivalent to algebras over a suitably defined $ C_2 $-$ \infty $-operad. 

We remark on the relationship between our construction and existing constructions in the literature. 
We note that \cite[\S3.3 \& \S3.4]{CHN2024} specifies the data needed to define a functor from schemes to Poincaré $ \infty $-categories. %; restricting to affine schemes, we consider this as a functor from commutative rings to $ \Catp $. 
In the language of this paper, the aforementioned functor endows a commutative ring $ R $ with trivial $ C_2 $-action/involution, then constructs Poincaré structures on $ \Mod^\omega_R $ whose duality functor is $ R $-linear. 
By considering rings with possibly nontrivial involution, we allow our duality functors to be conjugate linear. 
In the language of Poincaré objects, our construction allows us to speak of perfect complexes with nondegenerate \emph{hermitian} forms (or variants such as skew-hermitian) in addition to symmetric forms and their variants, while the former only gives rise to (anti)-symmetric forms.  
On the other hand, we do not consider forms valued in line bundles which are not trivial or explore how hermitian/Poincaré structures on $ \Mod_R^\omega $ might vary according to a given t-structure on $ \Mod_R $, so in these respects our construction is less general that that of Calmès--Harpaz--Nardin. 
Finally, the third author asserted (rather cavalierly) in \cite[\S5.2]{LYang_normedrings} that there is a functorial assignment from $ C_2 $-$ \EE_\infty $-algebras to Poincaré $ \infty $-categories; Theorem \ref{thm:calgp_to_poincare_cat} should be regarded as a more correct/precise demonstration of that assertion. 

\subsection{From Poincaré rings to Poincaré \texorpdfstring{$ \infty $}{∞}-categories}
\begin{notation}\label{ntn:t_order_equivariant_map}
    Let $ S, T $ be finite $ C_2 $-sets, and let $ f \colon S\to T $ be a $ C_2 $-equivariant map. 
    A \emph{t-ordering} on $ f $ is the data of, for all free orbits $ V \subset S $, $ V \simeq C_2 $ so that $ f(V) = \{*\} $, a choice of an ordering $ \le $ on $ V $. 
    A \emph{t-ordered map $ S \to T $} is the data of $ f $ and a t-ordering on $ f $.  

    Note that if $ f_i \colon S_i \to T_i $ are all t-ordered, there is a canonical t-ordering on $ \displaystyle \bigsqcup_i f_i $. 
    If $ f \colon S \to T $ is t-ordered and $ g \colon T \to U $ is t-ordered, there is a canonical t-ordering on $ g \circ f $. 
    Let us spell this out: Suppose given an orbit $ V \subset S $ on which $ C_2 $ acts freely so that $ g\circ f(V) $ is trivial. 
    There are two cases
    \begin{itemize}
        \item Suppose $ f $ restricts to an isomorphism $ f|_V \colon V \xrightarrow{\sim} f(V) $ and $ g $ sends $ f(V) $ to $ * $. 
        Then the t-ordering on $ g $ means we have an ordering on $ f(V) $, which we transport to an ordering on $ V $ via $ f|_V $. 
        \item Suppose $ f(V) = * $. 
        Then the t-ordering on $ f $ endows $ V $ with a canonical ordering.  
    \end{itemize} 
    Finally, we define a $ t $-ordering on pullbacks as follows: Suppose given a pullback square of $ C_2 $-sets. 
    \begin{equation*}
    \begin{tikzcd}
        Z \times_X W \ar[r,"{g^*f}"] \ar[d,"{\pi_1}"] &  W \ar[d,"{g}"] \\
        Z \ar[r,"f"] & X        
    \end{tikzcd}     
    \end{equation*} 
    and a t-ordering on $ f $. 
    Suppose given a free orbit $ C_2 \simeq U \subseteq Z \times_X W $ so that $ g^*(f)(U) $ is a singleton (with trivial $ C_2 $-action). 
    Because the square above is a pullback, $ \pi_1(U) \subset Z $ is acted on by $ C_2 $ freely, and $ \pi_1|_U $ defines an isomorphism $ U \simeq \pi_1(U) $. 
    By $ C_2 $-equivariance of $ g $, $ g(g^*(f)(U)) = f(\pi_1(U)) $ is a singleton. 
    The given t-ordering on $ f $ means $ \pi_1(U) $ has a given ordering, which we use to endow $ U $ with an ordering using the isomorphism $ \pi_1|_U $. 
\end{notation}
\begin{remark}\label{rmk:t_order_underlying}
    In the following pullback diagram in $ \Fin_{C_2} $, both t-orderings on $ f $ induce the same t-ordering on $ g^*(f) $ 
    \begin{equation*}
    \begin{tikzcd}
        C_2 \times C_2 \ar[r] \ar[d] & C_2 \ar[d,"{g}"] \\
        C_2 \ar[r,"{f}"] & C_2/C_2        
    \end{tikzcd}     
    \end{equation*}     
    (in fact the set of t-orderings on $ g^*(f) $ is a singleton.)
\end{remark}
In what follows, we will refer to the following diagram
\begin{equation}\label{diagram:C2_operad_generic_span}
\begin{tikzcd}
    U \ar[d] & \ar[l,"g"'] Z \ar[r,"f"]  \ar[d] & X \ar[d] \\
    V &  \ar[l] Y \ar[r,equals] & Y
\end{tikzcd}
\end{equation} 
in $ \underline{\Fin}_{C_2} $ or $ \underline{\Fin}_{C_2,*} $ repeatedly (see \cite[\S2.1]{NS22}). 
In particular, recall that in $ \underline{\Fin}_{C_2,*} $, the induced map $ Z \to U \times_V Y $ is always assumed to be a summand inclusion. 
\begin{definition}\label{defn:Poincare_ring_param_operad}
    Define a $ C_2 $-$ \infty $-operad $ \mathbb{E}_{\mathrm{p}}^\otimes \to \underline{\mathrm{Fin}}_{C_2, *} $ as having  
    \begin{itemize}
        \item objects consist of those arrows $ U \to V $ so that $ C_2 $ acts freely on $ U $ and transitively on $ V $ 
        \item morphisms consist of spans (\ref{diagram:C2_operad_generic_span}) in $ \underline{\mathrm{Fin}}_{C_2, *} $, plus the data of a t-ordering on $ f $ in the sense of Notation \ref{ntn:t_order_equivariant_map}.  
        \item composition is defined to agree with that in $ \underline{\mathrm{Fin}}_{C_2, *} $. 
    \end{itemize}
    There is a canonical map to $ \underline{\mathrm{Fin}}_{C_2, *} $ which is an inclusion on objects and on morphisms forgets the t-ordering. 
    \Lucyil{Say something about how (1) these are all $ C_2 $-$ \infty $-operads and (2) the underlying $ \infty $-categories are actually the nerve of $ (2,1) $-categories (see \cite[Remark 4.8]{LYang_normedrings}).}
\end{definition} 
\begin{definition}\label{defn:naive_assoc_param_operad}
    Define a $ C_2 $-$ \infty $-operad $ \underline{\mathrm{Assoc}}_{\mathrm{naive}}^\otimes \to \underline{\mathrm{Fin}}_{C_2, *} $ as having 
    \begin{itemize}
        \item objects consist of those arrows $ U \to V $ so that $ C_2 $ acts freely on $ U $ and transitively on $ V $ 
        \item morphisms consist of spans (\ref{diagram:C2_operad_generic_span}) in $ \underline{\mathrm{Fin}}_{C_2, *} $ plus the data of, for all orbits $ T \subset X $ an ordering on the orbits in the preimage $ f^{-1}(T) \subseteq Z $. 
        \item composition is defined to agree with that in $ \underline{\mathrm{Assoc}}^\otimes $. %\Lucy{Define a sub $ C_2 $-operad of $ \underline{\mathrm{Fin}}_{C_2, *} $ on free $ C_2 $-sets, then use Lemma 4.1.13 of Barkan--Haugseng--Steinebrunner to define via a fiber product?}
    \end{itemize}
    there is a canonical map to $ \underline{\mathrm{Fin}}_{C_2, *} $ which is an inclusion on objects and on morphisms forgets the ordering. 
\end{definition}
\begin{remark}\label{rmk:naive_assoc_alg_description}
    Let $ \underline{\mathrm{Free}}_{C_2, *} $ be the full subcategory of $ \underline{\mathrm{Fin}}_{C_2, *} $ on those arrows $ U \to V $ where $ U $ is a free $ C_2 $-set. 
    It is evident that $ \underline{\mathrm{Free}}_{C_2, *} $ is a sub $ C_2 $-$ \infty $-operad of $ \underline{\mathrm{Fin}}_{C_2, *} $ in the sense of \cite[Definition 2.2.7]{NS22}. 
    By \cite[Lemma 4.1.13]{BHS2022envelopes}, there is an equivalence of $ C_2 $-$ \infty $-operads $ \underline{\mathrm{Free}}_{C_2, *} \times_{\underline{\mathrm{Fin}}_{C_2, *}} \underline{\mathrm{Assoc}}^\otimes \simeq \underline{\mathrm{Assoc}}_{\mathrm{naive}}^\otimes $. 
    Now for any $ C_2 $-$ \infty $-operad $ \mathcal{C}^\otimes $, there is an equivalence 
    \begin{equation*}
        \hom_{\underline{\mathrm{Fin}}_{C_2, *}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}^\otimes, \mathcal{C}^\otimes\right) \simeq \hom_{\underline{\mathrm{Free}}_{C_2, *}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}^\otimes, \mathcal{C}^\otimes \times_{\underline{\mathrm{Fin}}_{C_2, *}} \underline{\mathrm{Free}}_{C_2, *}\right) \,. 
    \end{equation*}
    \Lucy{Now pass to spans of finite free $ C_2 $-sets (not spans of arrows!), and write $ \mathcal{C}^\otimes_{\mathrm{naive}} \to \mathrm{Free}_{C_2,*} $ and $ \mathrm{Assoc}_{\mathrm{naive}}^\otimes $. Use Higher algebra Remark 2.3.3.4 and (Thm 2.3.3.23 or Cor 2.3.2.13).} 
    The functor $ \mathrm{Free}_{C_2,*} \to \mathrm{Fin}_{*} $ which sends a (pointed, finite) free $ C_2 $-set to its set of orbits exhibits $ \mathrm{Free}_{C_2,*} $ as a generalized $ \infty $-operad in the sense of \cite[Definition 2.3.2.1]{LurHA}. \Lucy{(1) and (2) are clear, think about (3).} 
    Now choose a free $ C_2 $-set with transitive action; this determines a functor $ BC_2 \to \mathrm{Free}_{C_2,*} $. 
    This induces a functor $ p\colon BC_2 \times \mathrm{Fin}_{*} \to \mathrm{Free}_{C_2,*} $. 
    By \cite[Corollary 2.3.2.13]{LurHA}, there is an equivalence
    \begin{equation*}
        \hom_{\mathrm{Free}_{C_2, *}}\left(\mathrm{Assoc}_{\mathrm{naive}}^\otimes, \mathcal{C}^\otimes_{\mathrm{naive}} \right) \simeq \hom_{BC_2 \times \underline{\mathrm{Fin}}_{*}}\left(p^*(\mathrm{Assoc}_{\mathrm{naive}}^\otimes), p^*(\mathcal{C}^\otimes_{\mathrm{naive}} )\right)
    \end{equation*}
    where the left hand side denotes morphisms in generalized $ \infty $-operads over $ \mathrm{Free}_{C_2,*} $ and the right hand side denotes morphisms of $ BC_2 $-families of $ \infty $-operads in the sense of \cite[Definition 2.3.2.10]{LurHA}. 
    Now the latter is equivalent to $ \mathbb{E}_1 $-algebra objects in $ \left(\mathcal{C}^e\right)^{hC_2} $. 
\end{remark}
\begin{remark}
    Note that in the definition of $ \mathrm{Assoc}_{\mathrm{naive}} $ (\ref{diagram:C2_operad_generic_span}), $ f $ is equivalent to a fold map because $ X $ is acted upon freely by $ C_2 $. 
\end{remark}
\begin{definition}\label{defn:hermitian_mod_param_operad}
    Define a $ C_2 $-$ \infty $-operad $ \mathcal{HM}^\otimes \to \underline{\mathrm{Fin}}_{C_2, *} $ as having 
    \begin{itemize}
        \item objects consist of pairs $ (h : U \to V, \ell \colon U \to \{a, m\}) $ where $ h: U \to V $ is an object of $ \underline{\mathrm{Fin}}_{C_2, *} $ and $ \ell $ is a function which is constant on orbits (think `label') satisfying the condition that $ C_2 $ acts freely on $ \ell^{-1}(\{a\}) $. 
        \item a morphism from $ (h : U \to V, \ell_U \colon U \to \{a, m\}) $ to $ (h' : X \to Y, \ell_X \colon X \to \{a, m\}) $ consists of 
        \begin{itemize}
            \item a span (\ref{diagram:C2_operad_generic_span}) in $ \underline{\mathrm{Fin}}_{C_2, *} $
            \item $ Z $ is equipped with a labeling $ \ell_Z $ satisfying $ \ell_U = g \circ \ell_Z $ 
            \item a t-ordering on $ f $ in the sense of Notation \ref{ntn:t_order_equivariant_map}  
            \item for all orbits $ T \subset X $, an ordering $ \leq $ on the orbits in the preimage $ f^{-1}(T) \subseteq Z $. 
        \end{itemize} 
        These are required to satisfy the conditions 
        \begin{itemize}
            \item if $ x \in X $ is so that $ \ell_X(x) = m $, there exists at exactly one orbit, call it $ Z_x $ in $ f^{-1}(x) $ which $ \ell_Z $ sends to $ m $, which is maximal with respect to the ordering.  
            \item let $ x \in X $ be so that $ \ell_X(x) = m $, and write $ Z_x $ for the orbit in $ f^{-1}(x) $ which $ \ell_Z $ sends to $ m $ of the previous bullet point. Then $ f $ restricts to an isomorphism $ f|_{Z_x} $. % if $ z \in Z $ is so that $ \ell_Z(z) = m $ and $ C_2 $ acts freely on the orbit containing $ z $, then $ C_2 $ acts freely on the orbit containing $ f(z) $
        \end{itemize}
    \end{itemize}
    there is a canonical map to $ \underline{\mathrm{Fin}}_{C_2, *} $ which is an inclusion on objects and on morphisms forgets the ordering. 
\end{definition}
\begin{remark}\label{rmk:param_operad_maps}
    There is a map of $ C_2 $-$ \infty $-operads $ s \colon \mathcal{HM}^\otimes \to \mathbb{E}_p^\otimes $ which forgets the data of the labelings and the orderings on the preimages of the orbits (but remembers the t-orderings!).  
    Furthermore, there is a map of $ C_2 $-$ \infty $-operads $ \iota_a \colon \mathrm{Assoc}_{\mathrm{naive}}^\otimes \to \mathcal{HM}^\otimes $ which sends $ U \to V $ to the pair $ (U \to V, U \to\{a\} \hookrightarrow \{a,m\}) $. 
\end{remark}
\begin{definition}\label{defn:genuine_hermitian_modules}
    Let $ \mathcal{C}^\otimes $ be a $ C_2 $-symmetric monoidal $ C_2 $-$ \infty $-category. 
    Write $ \Mod^h(\mathcal{C}) $ denote the $ C_2 $-$ \infty $-category $ \underline{\Alg}_{\mathcal{HM}}(\mathcal{C}) $. 
    Note that precomposition with the map $ \iota_a $ of Remark \ref{rmk:param_operad_maps} defines a map of $ C_2 $-$ \infty $-categories $ \theta \colon \Mod^h(\mathcal{C}) \to \underline{\mathrm{Assoc}_{\mathrm{naive}}}(\mathcal{C}) $. 
\end{definition}
\begin{remark}\label{rmk:from_param_operad_maps_to_alg_mod_maps}
    Let $ \mathcal{C}^\otimes $ be the $ C_2 $-symmetric monoidal $ C_2 $-$ \infty $-category of $ C_2 $-spectra equipped with the Hill--Hopkins--Ravenel norm.  
    In view of Remark \ref{rmk:naive_assoc_alg_description}, we may regard an $ \mathcal{O}^\op_{C_2} $-object of $ \Mod^h\left(\underline{\Spectra}^{C_2}\right) $ as consisting of a pair $ (A,M) $ where $ A $ is an $ \EE_1 $-algebra in $ \Spectra^{BC_2} $ and $ M $ is an $ N^{C_2}A $-module in $ \Spectra^{BC_2} $. 
    Precomposition with the maps of Remark \ref{rmk:param_operad_maps} induces a commutative diagram
    \begin{equation*}
    \begin{tikzcd}
        & \Mod^h \ar[d] \\
        \underline{\Alg}_{\EE_p}\left(\underline{\Spectra}^{C_2}\right) \ar[r] \ar[ru] & \underline{\Alg}_{\underline{\mathrm{Assoc}}_{\mathrm{naive}}}\left(\Spectra^{C_2}\right)          
    \end{tikzcd}     
    \end{equation*} 
\end{remark}
\begin{construction}\label{cons:norm_in_families}
    Recall that by \cite[Proposition 2.8.7(1)]{NS22}, there is an equivalence $ \underline{\Alg}_{\underline{\mathrm{Assoc}}_{\mathrm{naive}}}\left(\underline{\Spectra}^{C_2}\right) \simeq \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) $. 
    % In the following, we will be interested in objects of $ Ar^{\mathrm{act}}(\underline{\Fin}_{C_2,*}) $ in the fiber over $ C_2/C_2 $, so we omit it from notation. 
    % Define objects
    % \begin{equation*}
    % \begin{split}
    %     X = \left(C_2 \to C_2/C_2, C_2 \to C_2/C_2, C_2 = C_2\right) \\
    %     Y = \left(C_2 \to C_2/C_2, C_2 \to C_2/C_2, C_2 \to C_2/C_2 \right)    
    % \end{split}
    % \end{equation*}
    % in $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) $. 
    % The collapse map gives a canonical morphism $ c \colon X \to Y $; observe that $ c $ is cocartesian over $ \underline{\Fin}_{C_2,*} $. 
    % Using semiaddivity/universal properties\Lucy{todo; see e.g. \cite[Notation 4.1]{LYang_normedrings}}, define a functor which is uniquely characterized by 
    % \begin{equation*}
    % \begin{split}
    %     \Delta^1 \times \Assoc &\to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) \\
    %     (0,\langle 1 \rangle) &\mapsto X \\
    %     (0, \langle 1 \rangle) &\mapsto Y \\
    %     (0 <1, \mathrm{id}_{\langle 1 \rangle}) &\mapsto (c \colon X \to Y)\,.
    % \end{split}
    % \end{equation*}
    % Precomposition with $ \Assoc \to \Fin_* $ defines a functor\footnote{with values in the fiber over $ C_2/C_2 $ of the target} 
    The assignment $ S_+ \mapsto [S \times C_2 \sqcup \{*\} \to C_2/C_2] $ sends a finite pointed set to a finite pointed set with free $ C_2 $-action (away from the basepoint), and for any tuple $ \left(f \colon S_+ \to T_+, \left(\leq_t \text{ ordering on }f^{-1}(\{t\})\right)_{t \in T}\right) $ (which defines a morphism in $ \Assoc^\otimes $, see \cite[Remark 4.1.1.4]{LurHA}), we have a span
    \begin{equation*}
    \begin{tikzcd}[column sep=large]
        S \times C_2 \sqcup \{*\} \ar[d] & f^{-1}(T) \times C_2 \sqcup \{*\} \ar[l] \ar[d] \ar[r,"{f|_{f^{-1}(T)} \times \id_{C_2}}"] & T \times C_2 \sqcup \{*\} \ar[d] \\
        C_2/C_2 & C_2/C_2 \ar[l,equals] \ar[r,equals] & C_2/C_2
    \end{tikzcd}
    \end{equation*}
    and for each $ C_2 $-orbit $ Z \simeq \{t\} \times C_2 \subset T \times C_2 $, an ordering on the orbits in $ \left(f|_{f^{-1}(T)} \times \id_{C_2}\right)^{-1}(Z) $. 
    In other words, we have a functor 
    \begin{equation}\label{eq:assoc_opd_to_param_assoc}
        q_{-1} \colon \Assoc^\otimes \to \left(\underline{\Assoc}_{\mathrm{naive}}\right)_{C_2/C_2}
    \end{equation}
    where $ (-)_{C_2/C_2} $ denotes the non-parametrized fiber. 
    Now recall that $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) \simeq \underline{\mathrm{Assoc}}_{\mathrm{naive}} \times_{\underline{\Fin}_{C_2,*}} Ar^{\mathrm{act}}(\underline{\Fin}_{C_2,*}) $ \cite[Definition 2.8.4]{NS22}. 
    Since the identity map on any object in $ \underline{\Fin}_{C_2,*} $ is an active arrow, (\ref{eq:assoc_opd_to_param_assoc}) induces a map
    \begin{equation}\label{eq:assoc_opd_to_envelope_param_assoc}
        q_{0} \colon \Assoc^\otimes \to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}\right) 
    \end{equation}
    Observe that $ \Assoc^\otimes \times \{0\} \to \Assoc^\otimes \times \Delta^1 $ is left anodyne by (the dual to) \cite[Corollary 2.1.2.7]{HTT}. 
    It follows from (the dual to) \cites[Corollary 2.4.2.5]{HTT}[\href{https://kerodon.net/tag/01VF}{Tag 01VF} Theorem 5.2.1.1(1')]{kerodon} that there exists an essentially unique extension 
    \begin{equation}\label{eq:assoc_opd_interval_to_envelope_param_assoc}
        q\colon \Delta^1 \times \Assoc^\otimes \to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}\right) 
    \end{equation}
    of (\ref{eq:assoc_opd_to_envelope_param_assoc}) which sends $ (0<1, \id_A) $ to a morphism which is cocartesian with respect to the structure map $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) \to \underline{\Fin}_{C_2,*} $. 
    Write $ p $ for the composite $ \Delta^1 \times \Assoc^\otimes \to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) \to \underline{\Fin}_{C_2,*} $. 
    Restriction along the functor of (\ref{eq:assoc_opd_interval_to_envelope_param_assoc}) defines 
    \begin{equation}\label{eq:assoc_alg_norm_in_families}
        \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}\right), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) \to \Fun_{\Delta^1 \times \Assoc^\otimes}\left(\Delta^1 \times \Assoc^\otimes, p^*\left(\underline{\Spectra}^{C_2}\right)\right) \,.
    \end{equation}
    Observe that $ p^*\left(\underline{\Spectra}^{C_2}\right) \to \Delta^1 \times \Assoc^\otimes $ is a $ \Delta^1 $-cocartesian family of monoidal $ \infty $-categories in the sense of \cite[Definition 4.8.3.1]{LurHA}, and the image of the aforementioned restriction functor consists of $ \Delta^1 $-cocartesian families of associative algebra objects in $ p^*\left(\underline{\Spectra}^{C_2}\right) $. 
    In particular, by \cite[Remark 4.8.3.8]{LurHA}, the aforementioned restriction functor refines to 
    \begin{equation}\label{eq:assoc_alg_norm_in_families_straightened}
        G \colon \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}\right), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) \to \Fun\left(\Delta^1, \CAT^{\Alg} \right) \,, 
     \end{equation} 
     where $ \CAT^{\Alg} $ is \cite[Definition 4.8.3.7]{LurHA}. 
     By construction, its image in $ \Fun\left(\Delta^1,\Alg\left(\CAT\right) \right) $ consists of the single arrow $ N^{C_2} \colon \Spectra \to \Spectra^{C_2} $. 
\end{construction}
\begin{remark}
    In fact, we can take $ \CAT^{\Alg}\left(\mathcal{K}^{\mathrm{sift}}\right) $ where $ \mathcal{K}^{\mathrm{sift}} $ denotes the collection of sifted simplicial sets. 
    However, we cannot take $ \mathcal{K} $ to be a collection containing not necessarily sifted diagrams, since the norm $ N^{C_2} $ does not take coproducts in $ \Spectra $ to coproducts in $ \Spectra^{C_2} $.  
\end{remark}
% \begin{definition}
%     \Lucy{compare Higher Algebra Definition 4.8.3.7} 
%     Let $ \Cat^{\Alg\Mod}_\infty $ denote the full subcategory of the fiber product 
%     \begin{equation*}
%         \Mon_{\Assoc}\left(\Cat_\infty\right) \times_{\Fun_{\Assoc}\left(\Assoc, \Assoc \times \Mon_{\Assoc}\left(\Cat_\infty\right) \right)} \Fun_{\Assoc}\left(\mathcal{LM}^\otimes, \widetilde{\Mon}_{\Assoc}\left(\Cat_\infty\right) \right)
%     \end{equation*}
%     on those triples $ (\mathcal{C}^\otimes, A, M) $ where $ \mathcal{C}^\otimes $ is a monoidal $ \infty $-category, $ A $ is an algebra object of $ \{\mathcal{C}^\otimes\} \times_{\Mon_{\Assoc}\left(\Cat_\infty\right) } \widetilde{\Mon}_{\Assoc}\left(\Cat_\infty\right) \simeq \mathcal{C}^\otimes $, and $ M $ is a left $ A $-module in $ \mathcal{C} $. 
% \end{definition}
% \begin{remark}
%     \Lucyil{The \textbf{KEY} is getting an analogue of Remark 4.8.3.8 of Higher Algebra for $ \Cat^{\Alg\Mod}_\infty $ instead of $ \Cat^{\Alg} $. Here is an attempt.}
%     For any simplicial set $ S $, there is a bijection between equivalence classes of maps $ S \to \Cat^{\Alg\Mod}_\infty $ and equivalence classes of diagrams
%     \begin{equation*}
%     \begin{tikzcd}
%         \mathcal{LM}^\otimes \times S  \ar[r,"{M_A}"]& \mathcal{C}^\otimes \ar[d,"q"] \\
%         \Assoc^\otimes \times S \ar[u] \ar[r,"{\mathrm{id}}"] \ar[r] & \Assoc^\otimes \times S
%         % && \mathcal{C}^\otimes \ar[d,"q"] \\
%         % \Assoc^\otimes \times S \ar[r] \ar[rr, bend right=30,"{\mathrm{id}}"] &\mathcal{LM} \times S \ar[r] \ar[ru,"{M_A}"] & \Assoc^\otimes \times S
%     \end{tikzcd}
%     \end{equation*}
%     where $ q $ exhibits $ \mathcal{C}^\otimes $ as an $ S $-cocartesian family of monoidal $ \infty $-categories and $ M_A $ is an $ S $-family of $ \mathcal{LM} $-algebra objects (i.e. associative algebra objects and modules over them).\Lucy{to-do: cardinalities}
% \end{remark}

\begin{construction}\label{cons:module_with_gen_involution_in_families}    
    Recall that by \cite[Proposition 2.8.7(1)]{NS22}, there is an equivalence $ \Modh\left(\underline{\Spectra}^{C_2}\right) \simeq \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\mathcal{HM}^\otimes), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) $. 

    Choose a $ C_2 $-set $ U $ on which $ C_2 $ acts freely and transitively, and fix an ordering $ \leq $ on $ U $. 
    Define a functor 
    \begin{equation*}
    \begin{split}
        \iota_m \colon \mathcal{LM}^\otimes & \to \left(\mathcal{HM}^\otimes\right)_{C_2/C_2} \\
         \left(\langle n \rangle, S \right) & \mapsto \left((\langle n \rangle^\circ \setminus S) \times U \sqcup S_+ \to C_2/C_2, \ell(i) = \begin{cases}
             a & i \in (\langle n \rangle^\circ \setminus S) \times U \\
             m & i \in S 
         \end{cases} \right) \\
         \left(\alpha \colon \left(\langle n \rangle, S\right) \to \left(\langle m \rangle, T\right) \right) & \mapsto \left(\left.\alpha\right|_{(\langle n \rangle^\circ \setminus S)} \times \id_U\right) \sqcup \alpha_{S} 
    \end{split}
    \end{equation*} 
    where $ \left(\mathcal{HM}^\otimes\right)_{C_2/C_2} $ denotes the fiber of $ \mathcal{HM}^\otimes $ over $ C_2/C_2 $. 
    To define $ \iota_m $, we must give a t-ordering on $ \iota_m(\alpha) $ and, for all orbits $ Z \subseteq (\langle m \rangle^\circ \setminus T) \times U \sqcup T $, an ordering on the orbits in the preimage $ \iota_m(\alpha)^{-1}(Z) $. 
    If $ Z \simeq \{j\} \times U \subseteq (\langle m \rangle^\circ \setminus T) \times U $ or $ Z = \{j\} \subseteq T $, then there is a canonical bijection from the orbits in $ \iota_m(\alpha)^{-1}(Z) $ and $ \alpha^{-1}(j) $; the given ordering on $ \alpha^{-1}(j) $ induces an ordering on the orbits of $ \iota_m(\alpha)^{-1}(Z) $. 
    If $ Z = \{t\} \subseteq T $, then we use the given ordering on $ U $ to endow $ \iota_m(\alpha) $ with a t-ordering. 
    % \Lucy{explain how the ordering on $ U $ is used to define the map!}

    Now recall that $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\mathcal{HM}^\otimes) \simeq \mathcal{HM}^\otimes \times_{\underline{\Fin}_{C_2,*}} Ar^{\mathrm{act}}(\underline{\Fin}_{C_2,*}) $ \cite[Definition 2.8.4]{NS22}. 
    Notice that the fiber of $ \underline{\Fin}_{C_2,*} $ over $ C_2/C_2 $ has a final object given by the identity arrow at $ [C_2/C_2 = C_2/C_2] $ and for every object $ [U \to C_2/C_2] $ in $ \underline{\Fin}_{C_2,*} $, the unique arrow from $ [U \to C_2/C_2] $ to $ [C_2/C_2 \to C_2/C_2] $, hence the composite $ \mathcal{LM}^\otimes \to \mathcal{HM}^\otimes_{C_2/C_2} \to \left(\underline{\Fin}_{C_2,*}\right)_{C_2/C_2} $ lifts to $ \mathcal{LM}^\otimes \to \mathcal{HM}^\otimes_{C_2/C_2} \to \left(\underline{\Fin}_{C_2,*}\right)_{C_2/C_2/[\mathrm{id}_{C_2/C_2}]} \to Ar^{\mathrm{act}}(\underline{\Fin}_{C_2,*}) $. 
    This defines a functor \Lucy{observe that $ r $ sends inert maps to inert maps? What does it mean for a morphism to be inert in $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(-) $?}
    \begin{equation}\label{lm_operad_to_genuine_fiber_hm_param_operad}
        r \colon \mathcal{LM}^\otimes \to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\mathcal{HM}^\otimes) \simeq \mathcal{HM}^\otimes \times_{\underline{\Fin}_{C_2,*}} Ar^{\mathrm{act}}(\underline{\Fin}_{C_2,*}) \,.
    \end{equation}
    Writing $ \iota_a $ for the canonical inclusion $ \mathrm{Assoc}^\otimes \to \mathcal{LM}^\otimes $, there is an equivalence\footnote{Actually, need to postcompose right hand side with the canonical map $ \mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\underline{\mathrm{Assoc}}_{\mathrm{naive}}) \to \mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\mathcal{HM}^\otimes\right) $ induced by Remark \ref{rmk:param_operad_maps}.} 
    \begin{equation}
        r \circ \iota_a = p \circ \left(\iota_{1} \times \mathrm{id}_{\mathrm{Assoc}^\otimes}\right) =:p_1 \,.
    \end{equation}
    Restriction along the functor (\ref{lm_operad_to_genuine_fiber_hm_param_operad}) sends maps of $ C_2 $-$ \infty $-operads to maps of ordinary $ \infty $-operads, hence it defines 
    \begin{equation}
        \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\mathcal{HM}^\otimes), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) \to \Alg_{\mathcal{LM}/\mathrm{Assoc}}\left(p_1^*\left(\underline{\Spectra}^{C_2,\otimes}\right)\right) \to \Alg_{/\mathrm{Assoc}}\left(p_1^*\left(\underline{\Spectra}^{C_2,\otimes}\right)\right)
    \end{equation}
    in the notation of \cite[Definition 2.1.3.1]{LurHA}. 
    Now observe that $ p_1^*\left(\underline{\Spectra}^{C_2,\otimes}\right) $ is the ordinary $ \infty $-category of $ C_2 $-spectra, regarded as a monoidal $ \infty $-category via smash product, and there is a commutative diagram
    \begin{equation}
    \begin{tikzcd}
         \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}(\mathcal{HM}^\otimes), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) \ar[r] \ar[d] & \LMod\left(\Spectra^{C_2,\otimes}\right) \ar[r] \ar[d] & \widetilde{\CAT^{\mathrm{ex}}} \ar[d] \\
         \Fun^\otimes_{C_2}\left(\mathrm{Env}_{\underline{\Fin}_{C_2,*}}\left(\underline{\mathrm{Assoc}}_{\mathrm{naive}}\right), \left(\underline{\Spectra}^{C_2}\right)^\otimes\right) \ar[r] &  \Alg_{\mathbb{E}_1}\left(\Spectra^{C_2}\right) \ar[r] & \CAT^{\mathrm{ex}} 
    \end{tikzcd}
    \end{equation}
    where $ \widetilde{\CAT^{\mathrm{ex}}} \to \CAT^{\mathrm{ex}} $ is the restriction of the universal cocartesian fibration to $ \CAT^{\mathrm{ex}} \subseteq \CAT $, the left vertical arrow is restriction along the map $ \underline{\mathrm{Assoc}}_{\mathrm{naive}}^\otimes \to \mathcal{HM}^\otimes $ of Remark \ref{rmk:param_operad_maps}, and the left horizontal arrow is (\ref{eq:assoc_alg_norm_in_families}) composed with restriction along $ \Assoc^\otimes \times \{1\} \hookrightarrow \Assoc^\otimes \times \Delta^1 $. 
    The right hand square is a pullback by \cite[Corollary 4.2.3.7(3)]{LurHA} and the straightening-unstraightening equivalence.  
\end{construction}

\begin{observation}   
    There is a canonical forgetful functor $ U \colon \CAT^{\Mod} \to \CAT $, where $ \CAT^{\Mod} = \mathrm{Mon}_{\mathcal{LM}}\left(\CAT\right) $ is defined in \cite[immediately preceding Remark 4.8.3.20]{LurHA}. % $ \Fun\left(\Delta^1, \Cat^{\Mod}_\infty \right) \times_{\Cat^{\Mod}_\infty} \Cat^{\Alg\Mod}_\infty \to \Fun\left(\Delta^1, \Cat_\infty \right) \times_{\Cat_\infty} \Cat_{\infty,*} $. 
    Combining Constructions \ref{cons:norm_in_families} and \ref{cons:module_with_gen_involution_in_families} and composing with the forgetful functor $ U $, we obtain a commutative diagram
    % Define a functor $ \Modh \to \Fun\left(\Delta^1, \Cat^{\Mod}_\infty \right) \times_{\Cat^{\Mod}_\infty} \Cat^{\Alg\Mod}_\infty $ living in a commutative square
    \begin{equation}\label{diagram:calgp_to_functor_cat_with_pointed_target}
    \begin{tikzcd}[cramped]
        \Modh \ar[rrr] \ar[d] & & & \widetilde{\CAT^{\mathrm{ex}}} \ar[d] \\ 
        % \Fun\left(\Delta^1, \Cat^{\Mod}_\infty \right) \times_{\Cat^{\Mod}_\infty} \Cat^{\Alg\Mod}_\infty \ar[d] \\
        \underline{\Alg}_{\underline{\mathrm{Assoc}}_{\mathrm{naive}}}\left(\underline{\Spectra}^{C_2}\right) \ar[r,"{U \circ \Theta \circ G}"] & \Fun\left(\Delta^1, \CAT \right) \ar[r,"{\ev_1}"] & \CAT & \CAT^{\mathrm{ex}} \ar[l] 
        % \underline{\Alg}_{\underline{\mathrm{Assoc}}_{\mathrm{naive}}}\left(\underline{\Spectra}^{C_2}\right) \ar[r] & \Fun\left(\Delta^1, \Cat^{\Alg}_\infty \right) \ar[r,"{\Theta}"] & \Fun\left(\Delta^1, \Cat^{\Mod}_\infty \right) \ar[r,"{\ev_1}"] & \Cat_\infty & \Catex \ar[l]
    \end{tikzcd}
    \end{equation}
    where $ G $ is (\ref{eq:assoc_alg_norm_in_families_straightened}) from Construction \ref{cons:norm_in_families} and $ \Theta $ is from \cite[Construction 4.8.3.24]{LurHA}. \Lucy{left or right modules? see \cite[Variant 4.8.3.19]{LurHA}.}

    Define $ \CAT^\epoly $ to be a large $ \infty $-category of not necessarily small stable $ \infty $-categories and reduced excisively polynomial functors between them; it defines a full subcategory of $ \CAT $ which moreover contains $ \CAT^{\mathrm{ex}} $ as a non-full subcategory. 
    Now let us observe that for any $ \EE_1 $-algebra $ A $ in $ \Spectra $, $ N^{C_2} \colon \Mod_A(\Spectra) \to \Mod_{N^{C_2}A}\left(\Spectra^{C_2}\right) $ is reduced and quadratic. 
    Therefore, $ U \circ \Theta \circ G $ takes values in stable $ \infty $-categories and reduced excisively polynomial functors between them. 
    Thus there is an essentially unique refinement of (\ref{diagram:calgp_to_functor_cat_with_pointed_target}) to a commutative diagram
    \begin{equation}\label{diagram:calgp_to_epoly_functor_cat_with_pointed_target}
    \begin{tikzcd}[cramped]
        \Modh \ar[rrr] \ar[d] & & & \widetilde{\CAT^{\mathrm{ex}}} \ar[d] \\ 
        \underline{\Alg}_{\underline{\mathrm{Assoc}}_{\mathrm{naive}}}\left(\underline{\Spectra}^{C_2}\right) \ar[r,"{U \circ \Theta \circ G}"] & \Fun\left(\Delta^1, \CAT^\epoly \right) \ar[r,"{\ev_1}"] & \CAT^\epoly & \CAT^{\mathrm{ex}} \ar[l] 
    \end{tikzcd}
    \end{equation} 
\end{observation}

% Define a functor $ \Catex_{,*} \to \Catex_{,(-)^\op/\Spectra} $. 
\begin{lemma}\label{lemma:stable_cat_functorial_Yoneda}
    Write $ \widetilde{\CAT^{\mathrm{ex}}} \to \CAT^{\mathrm{ex}} $ for the restriction of the universal cocartesian fibration to $ \CAT^{\mathrm{ex}} \subseteq \CAT $, where $ \CAT^{\mathrm{ex}} $ denotes stable $ \infty $-categories and exact functors between them. 
    Consider the cocartesian fibration $ \CAT^{\mathrm{ex}}_{,(-)^\op/\Spectra} \to \CAT $ classified by the functor $ \Fun^{\mathrm{ex}}\left((-)^\op, \Spectra\right) $, with cocartesian transport given by left Kan extension. 
    Then there is a functor $ \widetilde{\CAT^{\mathrm{ex}}} \to \CAT^{\mathrm{ex}}_{,(-)^\op/\Spectra} $ over $ \CAT^{\mathrm{ex}} $ which preserves cocartesian edges. 
    %\Lucy{replace $ \Catex $ by `large' stable $ \infty $-categories}
\end{lemma}
\begin{proof}
    \Lucyil{inspired by Yonatan's answer \href{https://mathoverflow.net/questions/385382/what-is-the-functoriality-of-the-infty-categorical-slice-construction}{here}; further useful discussion \href{https://mathoverflow.net/questions/383275/a-construction-of-the-universal-cocartesian-fibration}{here}. }
    Write $ \mathrm{RFib} \subset \mathrm{Ar}\left(\CAT\right) \times_{\CAT} \CAT^{\mathrm{ex}} $ be the full subcategory of the arrow category spanned by the right fibrations with target a stable $ \infty $-category. 
    Write $ \mathrm{RFib}_* \subseteq \mathrm{RFib} $, resp. $ \mathrm{RFib}^{\omega\text{-fil}} $ for the full subcategory on those arrows $ \mathcal{C} \to \mathcal{D} $ so that $ \mathcal{C} $ has a final object, resp. is $ \omega $-filtered (i.e., for every diagram $ K \to \mathcal{C} $ where $ K $ is finite, there exists an extension $ K^{\vartriangleright} \to \mathcal{C} $). 
    Observe that there is a commutative diagram 
    \begin{equation}\label{diagram:stable_functorial_Yoneda_unstraightened}
    \begin{tikzcd}[column sep=small]
        \mathrm{RFib}_* \ar[rr,"i"] \ar[rd,"{t_0}"'] & & \mathrm{RFib}^{\omega\text{-fil}} \ar[ld,"{t_1}"] \\
        & \CAT^{\mathrm{ex}} & 
    \end{tikzcd} 
    \end{equation} 
    of inner fibrations.  
    % where the diagonal arrows are cocartesian fibrations and $ i $ sends $ t_0 $-cocartesian arrows to $ t_1 $-cocartesian arrows.  
    % The maps $ \mathrm{RFib}_* \to \CAT^{\mathrm{ex}} $, $ \mathrm{RFib}^{\omega\text{-fil}} \to \CAT^{\mathrm{ex}} $ which send an arrow to its target are cocartesian fibrations. 
    By \cite[Corollary 6.5]{MR4545922} (cf. Corollary A.32 of \cite{MR3690268}), the left hand arrow in (\ref{diagram:stable_functorial_Yoneda_unstraightened}) is equivalent to the \emph{universal} cocartesian fibration $ \mathrm{RFib}_* \simeq \widetilde{\CAT^{\mathrm{ex}}} $.  
    By \cite[Corollary 5.3.5.4]{HTT}, the fiber of $ \mathrm{RFib}^{\omega\text{-fil}} \to \CAT^{\mathrm{ex}} $ over $ \mathcal{D} $ may be identified with the $ \infty $-category $ \Fun^{\mathrm{lex}}\left(\mathcal{D}^\op,\Spaces\right) $ of functors which preserve finite limits. \Lucy{Assume that there exists a strongly inaccessible regular cardinal $ \delta $, so that $ \mathcal{D} $ is $ \delta $-\emph{small} as required in \cite[Corollary 5.3.5.4]{HTT}. Then replace $ \Spectra $ by $ \delta $-small spectra, etc.} 
    By \cite[Corollary 1.4.2.23]{LurHA}, the functor $ \Omega^\infty $ induces an equivalence $ \Fun^{\mathrm{lex}}\left(\mathcal{D}^\op,\Spaces\right) \simeq \Fun^{\mathrm{lex}}\left(\mathcal{D}^\op,\Spectra\right) $.  
    It follows from \cite[Lemma 1.4.1(i)]{CDHHLMNNSI} that $ \mathrm{RFib}^{\omega\text{-fil}} \to \CAT^{\mathrm{ex}} $ is a cocartesian fibration classified by the functor $ \Fun^{\mathrm{lex}}\left((-)^\op,\Spectra\right) $, and $ i $ takes $ t_0 $-cocartesian morphisms to $ t_1 $-cocartesian morphisms.     
    Thus, we have identified $ i $ of (\ref{diagram:stable_functorial_Yoneda_unstraightened}) with the desired functor.  
    % For $ \mathcal{C} \in \CAT^{\mathrm{ex}} $, write $ \mathrm{RFib}_*(\mathcal{C}) $ for the $ \infty $-category of right fibrations over $ \mathcal{C} $ with a terminal object. 
    % Corollary A.32 of \cite{MR3690268} implies that there is a functor $ \CAT \to \Fun\left(\Delta^1, \widehat{\CAT}\right) $ which sends an $ \infty $-category $ \mathcal{C} $ to the equivalence $ \Fun'\left(\mathcal{C}^\op,\mathrm{Gpd}_\infty\right) \simeq \mathrm{RFib}_*(\mathcal{C}) $, where $ \Fun' $ denotes functors which preserve all limits. 
    % Use Corollary A.32 \href{https://arxiv.org/pdf/1501.02161}{here}.
    % IN PROGRESS AUGUST 5, 2025 PLEASE DO NOT DELETE THANKS--LUCY
    % -----------------------------------------------------------------------
    % Given a right fibration $ c \colon \widetilde{\mathcal{C}} \to \mathcal{C} $, consider\Lucy{Technically I should consider the space of all diagrams and consider the projection which forgets $ t^*(c) $. This is a trivial Kan fibration, so we can choose an inverse.}
    % \begin{equation*}
    % \begin{tikzcd}
    %     &  t^*(c) \ar[d] \ar[r]\ar[rd,phantom,"\lrcorner", very near start] & \widetilde{\mathcal{C}} \ar[d,"c"] \\
    %     \mathcal{C}^\op & \mathrm{TwAr}(\mathcal{C}) \ar[r,"t"] \ar[l] & \mathcal{C} \,. 
    % \end{tikzcd}
    % \end{equation*}
    % If $ \widetilde{\mathcal{C}} $ has a final object $ * $ and we write $ c = c(*) $, then the composite $ t^{-1}(c) \to \mathcal{C}^\op $ is a right fibration \cite[Proposition 1.1]{BG_16}. 
    % Furthermore, the right fibration $ t^{-1}(c) \to \mathcal{C}^\op $ straightens to the functor $ \hom_{\mathcal{C}}(-, c) \in \Fun'(\mathcal{C}^\op,\Spaces) \subseteq \Fun(\mathcal{C}^\op,\Spaces) $ where $ \Fun' $ denotes the full sub $ \infty $-groupoid on those functors which preserve finite limits. 
    % Since $ \mathcal{C} $ is stable, $ \Omega^\infty $ induces an equivalence $ \Fun'(\mathcal{C}^\op,\Spectra) \simeq \Fun'(\mathcal{C}^\op,\Spaces) $ by \cite[Corollary 1.4.2.23]{LurHA}. 
\end{proof}
% Then define a functor $ \Fun\left(\Delta^1, \Cat_\infty \right) \times_{\Cat_\infty} \Catex_{,*} \to \Fun\left(\Delta^1, \Cat_\infty \right) \times_{\Cat_\infty}\Catex_{,(-)^\op/\Spectra} \xrightarrow{\mathrm{compose}} \Cat_{(-)^\op/\Spectra} $. 
% \Lucyil{use a model for the former in terms of bifibrations and representable left fibrations! Finally use naturality of unstraightening in the base \href{https://arxiv.org/abs/1501.02161}{Proposition A.31 here}, esp. see how it is used in Paper I p.149}
\begin{construction}
    Combining (\ref{diagram:calgp_to_epoly_functor_cat_with_pointed_target}) with Lemma \ref{lemma:stable_cat_functorial_Yoneda} and Remark \ref{rmk:from_param_operad_maps_to_alg_mod_maps}, we obtain a commutative diagram\Lucy{Replace $ \CAlgp $ by something more general like $ \EE_\sigma\Alg $?}
    \begin{equation}\label{diagram:calgp_to_functor_cat_with_presheaf_on_target}
    \begin{tikzcd}
        & & \int \Fun^{\mathrm{ex}}( (-)^\op, \Spectra) \ar[d] \\
        \CAlgp \ar[r] \ar[rru,dashed,bend left=15] & \left(\CAT^\epoly\right)^{\Delta^1} \times_{\CAT^\epoly} \CAT^{\mathrm{ex}} \ar[r] & \CAT^{\mathrm{ex}} \,.
    \end{tikzcd}
    \end{equation}
    There is a functor $ \Fun^\epoly((-)^\op, \Spectra ) \colon \CAT^\epoly \to \CAT $. 
    Under the non-full subcategory inclusion $ \CAT^\mathrm{ex} \to \CAT^\epoly $, for any $ \mathcal{C} \in \CAT^\mathrm{ex} $, there is an inclusion $ \Fun^{\mathrm{ex}}(\mathcal{C}^\op,\Spectra) \subseteq \Fun^\epoly(\mathcal{C}^\op, \Spectra) $, where $ \Fun^{\mathrm{ex}}(\mathcal{C}^\op,\Spectra) $ denotes the full subcategory on exact functors. % the full subcategory on reduced quadratic functors $ \mathcal{C}^\op \to \Spectra $ as in \cite[\S1]{CDHHLMNNSI}. 
    In particular, there is a map of cartesian fibrations 
    \begin{equation}\label{diagram:extended_fibration_Cat_epoly}
    \begin{tikzcd}
        \int \Fun^{\mathrm{ex}}( (-)^\op, \Spectra) \ar[r] \ar[d] & \int \Fun^{\epoly}( (-)^\op, \Spectra) \ar[d] \\
        \CAT^\mathrm{ex} \ar[r] & \CAT^\epoly\,.
    \end{tikzcd}
    \end{equation}
    Composing (\ref{diagram:calgp_to_functor_cat_with_presheaf_on_target}) with (\ref{diagram:extended_fibration_Cat_epoly}) and noting that the map $ \left(\CAT^\epoly\right)^{\Delta^1} \to \CAT^\epoly $ defining the middle term in (\ref{diagram:calgp_to_functor_cat_with_presheaf_on_target}) is given by evaluation at the target, we obtain a diagram\Lucy{delete the middle of this diagram?} 
    \begin{equation}\label{diagram:calgp_to_functor_cat_with_presheaf_on_target_extended}
    \begin{tikzcd}[row sep=small]
        & & \int \Fun^{\epoly}( (-)^\op, \Spectra) \ar[dd] \\
        \CAlgp \times \{1\} \ar[r,"M"] \ar[rru,bend left=15,"{M_*}"] \ar[d] & \left(\CAT^\epoly\right)^{\Delta^1} \times \{1\} \ar[d] &  \\
        \CAlgp \times \Delta^1 \ar[r,"{M \times \mathrm{id}_{\Delta^1}}"] & \left(\CAT^\epoly\right)^{\Delta^1} \times \Delta^1 \ar[r,"{\mathrm{ev}}"] & \CAT^\epoly  \,.
    \end{tikzcd}
    \end{equation}
    Observe that in the bottom row of (\ref{diagram:calgp_to_functor_cat_with_presheaf_on_target_extended}), given a Poincaré ring $ A $, the morphism $ (\mathrm{id}_A, 0\to 1) $ from $ (A,0) $ to $ (A, 1) $ on the lower left is sent to the morphism $ N^{C_2} \colon \Mod_{A^e}(\Spectra) \to \Mod_{N^{C_2}A}\left(\Spectra^{C_2} \right) $ in the lower right. 
    Now observe that $ \{1\} \to \Delta^1 $ and $ \CAlgp \times \{1\} \to \CAlgp \times \Delta^1 $ are right anodyne by \cite[Corollary 2.1.2.7]{HTT}. 
    It follows from \cites[Corollary 2.4.2.5]{HTT}[\href{https://kerodon.net/tag/01VF}{Tag 01VF} Theorem 5.2.1.1(1)]{kerodon} that there exists a functor $ \overline{M}_* \colon \CAlgp \times \Delta^1 \to \int \Fun^\epoly\left((-)^\op,\Spectra\right) $ in (\ref{diagram:calgp_to_functor_cat_with_presheaf_on_target_extended}) extending $ M_* $. 
    Moreover, by \cite[\href{https://kerodon.net/tag/01VF}{Tag 01VF} Theorem 5.2.1.1(2)]{kerodon}, we see that $ \overline{M}(A,0) $ is the cartesian transport of $ M (A, 1) = \hom_{N^{C_2}A}(-,A) $ along the functor $$ \Fun^\epoly\left(\Mod_{N^{C_2} A}\left(\Spectra^{C_2}\right) ^\op, \Spectra\right) \to \Fun^\epoly\left(\Mod_{A^e}\left(\Spectra\right),\Spectra\right) $$ classified by $ \mathrm{ev} \circ \left(M \times \mathrm{id}_{\Delta^1}\right) $. 
    Consider the restriction of $ \overline{M}_* $ to $ \CAlgp \times \{0\} $. 
    Since the restriction of $ M \times \mathrm{id}_{\Delta^1} $ to $ \CAlgp \times \{0\} $ agrees with $ \Mod_{(-)^e} $ by Construction \ref{cons:norm_in_families}, we have that the image of $ \left.\left( M \times \mathrm{id}_{\Delta^1} \right)\right|_{\CAlgp \times \{0\}} $ factors through the inclusion $ \CAT^{\mathrm{ex}} \subseteq \CAT^\epoly $.  
    It follows that we may regard $ \overline{M}_*|_{\CAlgp \times \{0\}} $ as having codomain the total space of the cartesian fibration $ \int \Fun^\epoly\left((-)^\op,\Spectra\right) \to \CAT^{\mathrm{ex}} $. 

    We claim that $ \overline{M}_*|_{\CAlgp \times \{0\}} $ admits an essentially unique factorization through the cartesian fibration $ \int \Fun^q(-) \to \Catex $. 
    Since the natural transformation $ \Fun^q(-) \subseteq \Fun^\epoly\left((-)^\op,\Spectra\right) $ of functors $ \CAT^{\mathrm{ex}} \subseteq \CAT $ is given pointwise by full inclusions, the induced map $ \int \Fun^q(-) \to \int \Fun^\epoly\left((-)^\op,\Spectra\right) $ of cartesian fibrations over $ \CAT^{\mathrm{ex}} $ is a full inclusion by \cite[Proposition 2.4.4.2]{HTT}. 
    Therefore, to show that $ \overline{M}_*|_{\CAlgp \times \{0\}} $ factors through $ \int \Fun^q(-) $, it suffices to check that $ \overline{M}_*|_{\CAlgp \times \{0\}} $ sends objects of $ \CAlgp $ to objects of $ \int \Fun^q(-) $. 
    This is true because $ \overline{M}_*|_{\CAlgp \times \{0\}}(A,0) = \left(\Mod_{A^e}, \hom_{N^{C_2}A}\left(N^{C_2}(-), A\right)\right) $, $ N^{C_2} \colon \Mod_{A^e} \to \Mod_{N^{C_2}A} $ is quadratic, and a composite of a reduced quadratic functor and an exact functor is reduced and quadratic. \Lucy{reference for last fact?} 

    In sum, we have produced a commutative diagram like so: 
    \begin{equation}
    \begin{tikzcd}[row sep=small]
        & & \int \Fun^{q}(-) \ar[d] \ar[rd] & \\
        \CAlgp \times \{0\} \ar[rr,"{\mathrm{ev}_0 \circ M \simeq \Mod_{(-)^e}}"] \ar[rru,bend left=15,"{\left.\overline{M}_*\right|_{\CAlgp \times \{0\}}}"] \ar[d] & & \CAT^{\mathrm{ex}} \ar[rd] & \int \Fun^\epoly\left((-)^\op,\Spectra\right) \ar[d] \\
        \CAlgp \times \Delta^1 \ar[r,"{M \times \mathrm{id}_{\Delta^1}}"] & \left(\CAT^\epoly\right)^{\Delta^1} \times \Delta^1 \ar[rr,"{\mathrm{ev}}"] & &\CAT^\epoly  \,.
    \end{tikzcd}
    \end{equation}
    Let us write $ \mathrm{ev}_0 \circ M =: M_0 $ and $ \left.\overline{M}_*\right|_{\CAlgp \times \{0\}} =: \overline{M}_{*,0} $. 
    Now let us observe that there is an equivalence of functors $ M_0 \simeq \Mod_{(-)^e} \simeq \ev_1 \circ \iota^\omega $, where $ \iota^\omega $ is defined in Observation \ref{obs:cpct_modules_to_all_modules}. \Lucy{technically, need to precompose $ \iota^\omega $ forgetful functor from $ \EE_p $-algebras to $ \EE_1 $ algebras.}
    Now there is a commutative diagram
    \begin{equation*}
    \begin{tikzcd}
        \CAlgp \times \{1\} \simeq \CAlgp \ar[rr,"{\overline{M}_{*,0}}"] \ar[d] & & \int \Fun^{q}(-) \ar[d,"c"] \\
        \CAlgp \times \Delta^1 \ar[r] & \EE_1\Alg(\Spectra) \times \Delta^1 \ar[r,"{\iota^\omega}"] & \CAT^{\mathrm{ex}} \,.
    \end{tikzcd}
    \end{equation*}
    By the same argument as before, there is a canonical diagonal map $ \widetilde{M}_{*} $ extending $ \overline{M}_{*,0} $ so that $ \widetilde{M}_* $ sends $ (\id_A, 0<1) $ to a $ c $-cartesian arrow. 
    Observe that the restriction $ \widetilde{M}_*^\omega $ of $ \widetilde{M}_* $ to $ \CAlgp \times \{0\} $ sits in a commutative diagram
    \begin{equation}\label{diagram:calgp_to_hermitian_cat}
    \begin{tikzcd}
        \CAlgp \simeq \CAlgp \times \{0\} \ar[d] \ar[r,"{\widetilde{M}^\omega_*}"] & \int \Fun^{q}(-) \simeq \Cath \ar[d] \\
        \EE_1\Alg(\Spectra) \ar[r,"{\ev_0 \circ \iota^\omega}"] & \Catex \,.         
    \end{tikzcd}     
    \end{equation} 
    By definition of $ \widetilde{M}_* $ and $ \iota^\omega $, the functor $ \widetilde{M}_{*}^\omega $ sends a Poincaré ring $ A $ to the composite $ \Mod_{A^e}^\omega \subseteq \Mod_{A^e} \xrightarrow{N^{C_2}} \Mod_{N^{C_2}A} \xrightarrow{\hom_{N^{C_2}A}(-,A)} \Spectra $. 
\end{construction}
\begin{observation}\label{obs:cpct_modules_to_all_modules}
    Consider the cocartesian fibration $ p \colon \LMod\left(\Spectra\right) \to \EE_1\Alg\left(\Spectra\right) $ \cite[Corollary 4.2.3.7(3)]{LurHA}. 

    Write $ \LMod^\omega\left(\Spectra\right) $ for the full subcategory of $ \LMod\left(\Spectra\right) $ on those pairs $ (A, M) $ so that $ M $ is $ \omega $-compact as an $ A $-module. 
    Observe that given any $ (A, M) \in \LMod^\omega $ and any map $ f \colon A \to B $ in $ \EE_1 \Alg\left(\Spectra\right) $, then $ p $-cocartesian pushforward of $ (A,M) $ along $ f $ is equivalent to $ (B,B \otimes_A M) \in \LMod^\omega $. 
    In other words, $ p $-cocartesian pushforward preserves the subcategory $ \LMod^\omega\left(\Spectra\right) $ because the functor $ B \otimes_A (-) $ admits a right adjoint which preserves $ \omega $-filtered colimits. 
    It follows that the restriction $ \overline{p} $ of $ p $ to $ \LMod^\omega\left(\Spectra\right) $ exhibits $ \LMod^\omega\left(\Spectra\right) \to \EE_1\Alg\left(\Spectra\right) $ as a cocartesian fibration, and the inclusion $ \LMod^\omega\left(\Spectra\right) \to \LMod\left(\Spectra\right) $ takes $ \overline{p} $-cocartesian edges to $ p $-cocartesian edges. 
    Unstraightening the inclusion $ \LMod^\omega\left(\Spectra\right) \to \LMod\left(\Spectra\right) $, we obtain a functor 
    \begin{equation*}
        \iota^\omega \colon \EE_1\Alg\left(\Spectra\right) \to \Fun\left(\Delta^1,\CAT^{\mathrm{ex}}\right) \qquad \text{ or equivalently } \qquad \EE_1\Alg\left(\Spectra\right) \times \Delta^1 \to \CAT^{\mathrm{ex}}
    \end{equation*}
    so that the composite $ \ev_0 \circ \iota^\omega $ factors through $ \Catex \subseteq \CAT^{\mathrm{ex}} $. 
    Informally, $ \iota^\omega $ sends an $ \EE_1 $-algebra $ A $ to the inclusion $ \LMod^\omega_A \to \LMod_A $. 
    Here $ \CAT^{\mathrm{ex}} $ is the large $ \infty $-category of stable $ \infty $-categories and exact functors between them. 
\end{observation}
\begin{definition}\label{defn:calgp_to_hermitian_cat}
    Let us write $ \Mod^p $ for the functor of (\ref{diagram:calgp_to_hermitian_cat}). 
\end{definition}
\begin{theorem}\label{thm:calgp_to_poincare_cat}
\begin{enumerate}[label=(\arabic*)]
    \item \label{thmitem:calgp_to_hermitian_factors} The functor of Definition \ref{defn:calgp_to_hermitian_cat} factors through the subcategory $ \Catp \subseteq \Cath $. 
    \item \label{thmitem:unit_to_unit} Recall that $ \CAlgp $ has an initial object given by the sphere spectrum (Remark \ref{rmk:E_sigma_operad_unital}). 
    Then there is an equivalence $ \Mod^p_{\sphere} \simeq \left(\Spectra^\omega,\Qoppa^u\right) $ where the latter is the universal Poincaré $ \infty $-category of \cite[\S4.1]{CDHHLMNNSI}. 
    \item Recall that $ \Catpidem $ has a symmetric monoidal structure. 
    Then the functor $ \Mod^p $ is symmetric monoidal. \Lucy{to-do! Use \cite[Example 5.1.6]{CDHHLMNNSI}?}
\end{enumerate}
\end{theorem}
\begin{proof}
    Part \ref{thmitem:calgp_to_hermitian_factors} follows from observing that given a map $ A \to B $ in $ \CAlgp $, the induced functor $ \Mod^p_A \to \Mod^p_B $ satisfies the assumptions of \cite[Lemma 3.4.3]{CDHHLMNNSI}. 
    Part \ref{thmitem:unit_to_unit} follows from unraveling definitions. 
\end{proof}
\begin{corollary}
    Suppose $ A \in \CAlgp $. 
    Then $ A^e $ canonically promotes to a Poincaré object $ (A^e, q_A) $ of $ \Mod^p_A $. 
\end{corollary}
\begin{proof}
    By Remark \ref{rmk:E_sigma_operad_unital}, there is an equivalence $ \CAlgp \simeq \CAlgp_{\sphere/-} $. 
    By Theorem \ref{thm:calgp_to_poincare_cat}, we have a canonical map $ \Mod^p_{\sphere} \simeq \left(\Spectra^\omega,\Qoppa^u\right) \to \Mod^p_A $. 
    The result follows from noting that $ \left(\Spectra^\omega,\Qoppa^u\right) $ corepresents $ \mathrm{Pn} $ by \cite[Proposition 4.1.3]{CDHHLMNNSI}. 
\end{proof}

\subsection{An operadic description of Poincaré rings}\label{subsection:calgp_operadic}
In this subsection, we show that algebras over $ \mathbb{E}_p $ are equivalent to Poincaré rings defined diagrammatically. 
The constructions and proofs are very similar to those of \cite{LYang_normedrings}, with the $ C_2 $-$ \infty $-operad $ \EE_p^\otimes $ in place of the commutative/terminal $ C_2 $-$ \infty $-operad. 
We give a terse outline of the argument, including proofs of modified versions of key auxiliary results of \emph{loc. cit.}, but otherwise refer to \emph{loc. cit.} for details.   

Let $ K $ denote the $ \infty $-categorical nerve of the $ 1 $-category
\begin{equation*}%\label{diagram:indexing_normedrings}
\begin{tikzcd}[cramped, row sep=tiny]
    & 3 \ar[dd] & \\
    & & 2 \ar[dd] \ar[lu] \\
    & 5 & \\
    1  \ar[rr] \ar[ru] \ar[ruuu, bend left=15] & & 4 \ar[lu]
\end{tikzcd}
\end{equation*}
in which all triangles and squares commute. 

\begin{definition}\label{defn:calgp_alt_diagram}
    Consider the diagram $ \mathcal{P} \colon K \to \Cat_\infty $ 
    \begin{equation}%\label{diagram:normedrings}
    \begin{tikzcd}[column sep=small]
        & \Fun\left(\Delta^1,\EE_\infty\Alg\left(\Spectra\right)^{BC_2}\right) \ar[dd,"{\mathrm{ev}_{0},\mathrm{ev}_{1}}"]  & \\
        & & \Fun\left(\Delta^1,\EE_\infty\Alg\left(\Spectra^{C_2}\right)\right) \ar[dd,"{\mathrm{ev}_{0}, \mathrm{ev}_{1}}"] \ar[lu,"{(-)^e}"'] \\
        &\EE_\infty\Alg(\Spectra)^{BC_2} \times \EE_\infty\Alg(\Spectra)^{BC_2} & \\
        \EE_\infty\Alg\left(\Spectra^{C_2}\right)  \ar[rr,"{N^{C_2}(-^e) \times \id}"'] \ar[ru] \ar[ruuu,"{m \circ (-^e)}", bend left=30] & &\EE_\infty\Alg\left(\Spectra^{C_2}\right) \times \EE_\infty\Alg\left(\Spectra^{C_2}\right) \ar[lu,"{(-)^e \times (-)^e}"]
    \end{tikzcd}
    \end{equation}
    where $ m $ is the functor of \cite[Construction 3.1]{LYang_normedrings} precomposed with the canonical map $ \Delta^1 \to \mathcal{O}_{C_2} $. 
    Observe that the right-hand trapezoid commutes essentially by definition, and the leftmost triangle commutes because $ \left(N^{C_2} A \right)^e \simeq (A^e)^{\otimes 2} $. 
    Consider the limit of the diagram 
    \begin{equation}
        \CAlgp'\left(\Spectra^{C_2}\right) := \lim_K \mathcal{P} .
    \end{equation} 

    There is a canonical forgetful functor $ G' \colon \CAlgp\left(\Spectra^{C_2}\right) \to \EE_\infty\Alg\left(\Spectra^{C_2}\right)  $ given by the canonical projection to the lower left corner of the diagram. 
\end{definition}
\begin{observation}\label{obs:limits_of_limits}
    Let $ F \colon K \to \mathcal{C} $ be any diagram and let $ \mathcal{C} $ be any $ \infty $-category with finite limits. 
    Then there is a canonical equivalence $ \displaystyle \lim_K F \simeq F(1) \times_{\left(F(3) \times_{F(5)} F(4)\right)} F(2) $. 
\end{observation}
\begin{observation}
    By the recollement decomposition of $ \Spectra^{C_2} $, $ \lim_K \mathcal{P} $ is equivalent to the limit of the diagram\footnote{`res' means restriction.} 
    \begin{equation}%\label{diagram:normedrings}
    \begin{tikzcd}[column sep=small]
        & \Fun\left(\Delta^1,\EE_\infty\Alg\left(\Spectra\right)\right) \ar[dd,"{\mathrm{ev}_{0},\mathrm{ev}_{1}}"]  & \\
        & & \Fun\left(\Delta^1 \times \Delta^1,\EE_\infty\Alg\left(\Spectra\right)\right) \ar[dd,"{(\mathrm{res}_{\Delta^1 \times \{0\}},\mathrm{res}_{\Delta^1 \times \{1\}})}"] \ar[lu,"{\mathrm{res}_{\{1\} \times \Delta^1}}"'] \\
        &\EE_\infty\Alg(\Spectra) \times \EE_\infty\Alg(\Spectra) & \\
        \EE_\infty\Alg\left(\Spectra^{C_2}\right)  \ar[rr,"{N^{C_2}(-^e) \times \id}"'] \ar[ru] \ar[ruuu,"{m^{tC_2} \circ (-^e)}", bend left=30] & &\EE_\infty\Alg\left(\Spectra^{C_2}\right)^{\Delta^1} \times \EE_\infty\Alg\left(\Spectra^{C_2}\right)^{\Delta^1} \ar[lu,"{\ev_1 \times \ev_1}"]
    \end{tikzcd}
    \end{equation} 
    By Observation \ref{obs:limits_of_limits} and the fact that all commutative trapezoids below \emph{except} the upper left are pullbacks: 
    \begin{equation}
    \begin{tikzcd}[column sep=small]
        \EE\Alg(\Spectra)^{\Delta^1 \times \Delta^1} \ar[rr,"{\ev_{00\to10\to11}}"] \ar[d,"{(\mathrm{res}_{\Delta^1 \times \{0\}},\mathrm{res}_{\Delta^1 \times \{1\}})}"'] & & \EE\Alg(\Spectra)^{\Delta^2} \ar[d,"{(d_2,\ev_2)}"] \ar[rr,"{d_0}"] & & \EE\Alg(\Spectra)^{\Delta^1} \ar[d,"{(\ev_0,\ev_1)}"] & \\
        \left(\EE\Alg(\Spectra)^{\Delta^1}\right)^{\times 2} \ar[rr,"{(\id,\ev_1)}"] \ar[d,"{\pi_2}"] & &\EE\Alg(\Spectra)^{\Delta^1} \times \EE\Alg(\Spectra) \ar[rd,"{\pi_1}"] \ar[d,"{\pi_2}"] \ar[rr,"{(\ev_1, \id)}"] & & \EE\Alg(\Spectra)^{\times 2} \ar[rd,"{\pi_1}"] & \\
        \EE\Alg(\Spectra)^{\Delta^1} \ar[rr,"{\ev_1}"] & & \EE\Alg(\Spectra) & \EE\Alg(\Spectra)^{\Delta^1} \ar[rr,"{\ev_1}"] & & \EE\Alg(\Spectra)\,,
    \end{tikzcd}
    \end{equation} 
    (Here $ \pi_1, \pi_2 $ denote projections onto the first and second factors, resp.) 
    it follows that 
    \begin{equation*}
        \lim_K \mathcal{P} \simeq \left(\EE_\infty \Alg\left(\Spectra^{C_2}\right)\right) \times_{\left(\EE_\infty\Alg(\Spectra)^{\Delta^2} \times_{\EE_\infty \Alg(\Spectra)} \EE_\infty\Alg(\Spectra)^{\Delta^1}\right)} \EE_\infty\Alg(\Spectra)^{\Delta^1 \times \Delta^1} \,.
    \end{equation*}
    Thus $ \lim_K \mathcal{P} $ is equivalent to $ \CAlgp $ as defined in main.tex (see the limit of diagram \texttt{diagram:Poincare\_ring\_alternate\_diagram} in Remark 3.4). 
\end{observation}
\begin{remark}\label{rmk:operadic_Poincare_rings_to_E_infty_alg_in_genuine_spectra}
    There is a map of $ C_2 $-$ \infty $-operads $ \mathrm{Com}_{\mathcal{O}_{C_2}^\simeq} \to \EE_p $. 
    By \cite[Lemma 4.24]{LYang_normedrings}, this induces a functor $ G'\colon \EE_p\Alg\left(\Spectra^{C_2}\right) \to \EE_\infty\Alg\left(\Spectra^{C_2}\right) $, which by an argument similar to Proposition 4.23 \emph{loc.cit.} is monadic. 
\end{remark}
\begin{construction}\label{cons:calgp_operadic_to_diagrammatic}
    Define a functor $ \gamma \colon \EE_p \Alg(\Spectra^{C_2}) \to \CAlgp $ (similar to \cite[\S4.1]{LYang_normedrings}). 
\end{construction}
\begin{theorem}\label{thm:operadic_diagrammatic_calgp_agree}
    The functor of Construction \ref{cons:calgp_operadic_to_diagrammatic} is an equivalence. 
\end{theorem}
\begin{proof}
    The proof is nearly identical to that of \cite[Theorem 4.21]{LYang_normedrings}, but we include it here for the reader's convenience. 
    Consider the commutative diagram of forgetful functors 
    \begin{equation}\label{diagram:forgetforget_is_forget}
    \begin{tikzcd}[column sep=tiny]
        \EE_p\Alg\left(\Spectra^{C_2}\right) \ar[rr,"\gamma"] \ar[rd,"G"'] & & \CAlgp\left(\Spectra^{C_2}\right) \ar[ld,"G'"] \\
        & \EE_\infty\Alg\left(\Spectra^{C_2}\right) & 
    \end{tikzcd}
    \end{equation} 
    where $ G $ is from Remark \ref{rmk:operadic_Poincare_rings_to_E_infty_alg_in_genuine_spectra} and $ G' $ is from Definition \ref{defn:calgp_alt_diagram}. 

    The functor $ G $ is monadic by Remark \ref{rmk:operadic_Poincare_rings_to_E_infty_alg_in_genuine_spectra}. 
    The functor $ G' $ is monadic by Proposition \ref{prop:calgp_monadic}.
    Now for any $ A \in \EE_\infty\Alg\left(\Spectra^{C_2}\right) $, the unit $ A \to \gamma F(A) $ of Theorem \ref{thm:free_operadic_calgp_formula} induces an equivalence $ F'(A) \simeq \gamma F(A) $ by Corollary \ref{cor:free_algebras_agree}.  
    The result follows from \cite[Proposition 4.7.3.16]{LurHA}. 
    % \Lucyil{Similar to proof of \cite[Theorem 4.21]{LYang_normedrings}, using Proposition \ref{prop:calgp_monadic}, Theorem \ref{thm:free_operadic_calgp_formula}, Proposition \ref{prop:unit_in_diagrammatic_calgp}. Include discussion that $ \EE_p\Alg $ is monadic over $ \EE_\infty\Alg $.}
\end{proof}
\begin{proposition}\label{prop:calgp_monadic}
    The forgetful functor $ G' \colon \CAlgp\left(\Spectra^{C_2}\right) \to \EE_\infty\Alg\left(\Spectra^{C_2}\right) $ of Definition \ref{defn:calgp_alt_diagram} is monadic. 
\end{proposition}
\begin{proof}
    \Lucyil{Similar to \cite[Proposition 3.23]{LYang_normedrings}, except there I forgot to show that $ G' $ \emph{has} a left adjoint (oops!). That's ok; it does, and we showed that the relevant functor for $ \CAlgp $ does in \texttt{main.tex}.}
\end{proof}
\begin{theorem}\label{thm:free_operadic_calgp_formula}
    Let $ A \in \EE_\infty\Alg\left(\Spectra^{C_2}\right) $ and consider the adjunction $ F \dashv G $ between $ \EE_p $ and $ \EE_\infty $-algebras in $ \Spectra^{C_2} $. % of Recollection \ref{recollection:freealg_colimit}. 
    \begin{enumerate}[label=(\arabic*)]
    \item The underlying $ C_2 $-spectrum of the free $ \EE_p $ algebra $ F(A) $ on $ A $ is given by 
    \begin{equation}\label{eq:free_operadic_calgp_formula}
    F(A) \simeq
    \begin{tikzcd}
        &  A^{\varphi C_2} \otimes A^e \ar[d,"{s_A \otimes \nu_A}"] \\
        A^e \ar[r,mapsto] & A^{tC_2}
    \end{tikzcd}
    \end{equation}
    where $ u $ is the unit, $ s_A : A^{\varphi C_2} \to A^{tC_2} $ is the structure map, and $ \nu_A $ is the twisted Tate-valued Frobenius. 
    \item There is a canonical $ \EE_\infty $ ring map $ \eta_A \colon A \to GF(A) $ given by $ \id_{A^{\varphi C_2}} \otimes (\eta_{A^e}:\mathbb{S}^0 \to A^e) $ on geometric fixed points and the identity on underlying.
    \end{enumerate}
\end{theorem}
\begin{proof}
    Similar to proof of \cite[Theorem 4.15]{LYang_normedrings}, substituting $ \mathrm{Env}_{\EE_p, \underline{\Fin}_{C_2,*}}\left(\mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}}\right) $ for $ \mathrm{Com}_{\mathcal{T}^\simeq,act}^\otimes = \mathrm{Env}_{\underline{\Fin}_{C_2,*}, \underline{\Fin}_{C_2,*}}\left(\mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}}\right) $. 
    Since the indexing diagram is different, one uses Lemma \ref{lemma:freeoperadic_calgp_colimdiagram} instead of Lemma 4.19 \emph{loc. cit}. 
\end{proof}

\begin{lemma}\label{lemma:freeoperadic_calgp_colimdiagram}
    Consider the (non-parametrized) fiber $ I $ of $ \mathrm{Env}_{\EE_p, \underline{\Fin}_{C_2,*}}\left(\mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}}\right) $ over $ \mathrm{id}_{C_2/C_2} $. 
    An object of $ I $ can be thought of as a pair $ \left([U \to V], \alpha \colon i([U \to V]) \to [\mathrm{id}_{C_2/C_2}]\right)$ where $ [U \to V ] $ is an object in the fiber of $ \mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}} $ over $ C_2/C_2 $, $ i $ denotes the inclusion $ \mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}} \to \EE_p $, and $ \alpha $ is an active arrow in $ \EE_p $. 

    Choose a $ C_2 $-set $ U $ with free and transitive $ C_2 $-action, and fix an ordering $ \leq $ on $ U $. 
    This determines a t-ordering on the collapse map $ C_2/C_2 \sqcup U \to C_2/C_2 $, hence an active arrow $ \beta $ in $ \EE_p^\otimes $. 
    The inclusion
    \begin{equation*}
        \{*\} \xrightarrow{* \mapsto \beta} I
    \end{equation*}
    is cofinal. 
\end{lemma}
\begin{proof}
    By \cite[Theorem 4.1.3.1]{HTT}, it suffices to show that for all $ X \in I $, the category $ \{*\} \times_{I} I_{X/} $ has an initial object. 
    Informally, an object $ X $ of $ I $ is given by a tuple $ (S, \alpha \colon S \to C_2/C_2) $ where $ S $ is a finite $ C_2 $-set and $ \alpha $ is an active arrow in $ \left(\EE_p^\otimes\right)_{C_2/C_2} $. 
    We observe that $ \alpha $ is given by a $ C_2 $-equivariant map $ f $ (in fact, $ f $ is unique) and a t-ordering on $ f $ in the sense of Notation \ref{ntn:t_order_equivariant_map}. 
    Morphisms are given by tuples; note that a morphism $ \psi \colon (S,\alpha) \to (T,\gamma) $ determines a map $ S \to T $ in $ \left(\mathrm{Com}_{\mathcal{O}_{C_2}^\simeq}\right)_{C_2/C_2} $; in particular, the map $ S \to T $ must be equivalent to a disjoint union of fold maps. 
    Now the t-ordering on $ f $ is equivalent to giving, for each free orbit $ Z \subseteq S $, $ Z \simeq C_2 $, an ordering $ \leq_Z $ on $ Z $. 
    For each such $ Z $, there is a unique order-preserving, $ C_2 $-equivariant isomorphism $ j_Z \colon Z \simeq U $. 
    Write $ S \simeq S^f \sqcup S^t $ for the canonical decomposition where $ C_2 $ acts freely on $ S^f $ and trivially on $ S^t $. 
    Then $ \displaystyle S \simeq S^t \sqcup \left(\bigsqcup_{Z \in \mathrm{Orbit}(S^f)} Z\right) \xrightarrow{\nabla \sqcup \left(\bigsqcup j_Z\right)} C_2/C_2 \sqcup U $ defines a morphism in $ \left(\mathrm{Com}_{\mathcal{O}_{C_2}^{\simeq,\op}}\right)_{C_2/C_2} $ so that the diagram
    \begin{equation*}
    \begin{tikzcd}
        S \ar[rr,"{\nabla \sqcup \left(\bigsqcup j_Z\right)}"] \ar[rd,"\alpha"] & & C_2/C_2 \sqcup U\ar[ld,"{\beta}"] \\
        & C_2/C_2 &         
    \end{tikzcd}     
    \end{equation*} 
    commutes in $ \EE_p $; this is the desired initial object of $ \{*\} \times_{I} I_{X/} $.  
\end{proof}
\begin{proposition}\label{prop:unit_in_diagrammatic_calgp}
    Let $ A $ be an $ \EE_\infty $-ring in $ \Spectra^{C_2} $ and let $ (B, n_B \colon N^{C_2}B \to B) $ be a Poincaré ring in $ \Spectra^{C_2} $. 
    Then precomposition with the $ \EE_\infty $-map $ \eta_A : A \to GF(A) $ of Theorem \ref{thm:free_operadic_calgp_formula} induces an equivalence of morphism spaces
    \begin{equation}\label{eq:unit_in_normedalg}
    \begin{tikzcd}
        {\hom_{\CAlgp}\left(\left(\gamma F(A), n_{F(A)} \colon N^{C_2}\gamma F(A) \to \gamma F(A)\right),\left(B, n_B \colon N^{C_2} B \to B \right)\right)} \ar[d,"{G'}"] \ar[dd, bend left=75,looseness=2,"{\rotatebox{90}{$\sim$}}"] \\
        \hom_{\EE_\infty}(G'\gamma F(A), G'(B)) \ar[d,"{\eta^*}"] \\
         \hom_{\EE_\infty}(A, G'(B)).
    \end{tikzcd}
    \end{equation}
    where $ G' $ is the forgetful functor and $ \gamma $ is the functor of Construction \ref{cons:calgp_operadic_to_diagrammatic}. 
    That is, $ \eta_{(-)} $ is a unit for the functors $ (\gamma \circ F, G') $ in the sense of \cite[Definition 5.2.2.7]{HTT}. 
\end{proposition}
\begin{corollary}\label{cor:free_algebras_agree}
    The natural transformation $ \eta_{(-)} $ exhibits $ \gamma \circ F $ as a left adjoint to $ G' $. 
\end{corollary}
\begin{proof}[Proof of Proposition \ref{prop:unit_in_diagrammatic_calgp}]
    Notice that 
    \begin{equation*}
        \hom_{\EE_\infty\Alg\left(\Spectra^{C_2}\right)}(F(A),B) \simeq \hom_{\EE_\infty\Alg\left(\Spectra^{C_2}\right)}(A,B) \fiberproduct_{\hom\left(A^{tC_2},B^{tC_2}\right) } \hom \left( \morphism{A}{\nu_A}{A^{tC_2}}, \morphism{B^{\varphi C_2}}{\Delta}{B^{tC_2}} \right)
    \end{equation*}
    and moreover the composite
    \begin{equation*}
        \hom_{\CAlgp}(F(A), B) \xrightarrow{G'} \hom_{\EE_\infty\Alg\left(\Spectra^{C_2}\right)}(F(A),B) \xrightarrow{\pi_1} \hom_{\EE_\infty\Alg\left(\Spectra^{C_2}\right)}(A,B)
    \end{equation*}
     is equivalent to $ \eta^* \circ G' $. 
    Unravelling definitions, we see that given a point $ f \in \hom_{\EE_\infty\Alg\left(\Spectra^{C_2}\right)}(A,B) $, the fiber of $ \eta^* \circ G' $ over $ f $ is given by the space of fillings of the below diagram to a commutative diagram $ (\Delta^1)^{\times 3} \to \EE_\infty\Alg(\Spectra) $:  
    \begin{equation*}
    \begin{tikzcd}[row sep=small] %column sep=small, 
        A^e \ar[rr,"{f^e}"] \ar[dd] \ar[rd,equals] & & B^e \ar[dd] \ar[rd,"{n_B}"] & \\
            & A^e  \ar[rr, dotted,crossing over] & & B^{\varphi C_2} \ar[dd] \\
        {(A^{\otimes 2})^{tC_2}} \ar[rr,"{(f^{\otimes 2})^{tC_2}}",very near end] \ar[rd] & & {( B^{\otimes 2})^{tC_2}} \ar[rd] & \\
        & A^{tC_2} \ar[rr,"{f^{tC_2}}"] & & B^{tC_2} \ar[from=2-2,to=4-2,crossing over,"{\nu_{A^e}}", near end]
    \end{tikzcd}
    \end{equation*} 
    wherein all but the top and front face are given. 
    This space is contractible. 
\end{proof}
\section{Categorification and structure--new leaf}
Let $ \Ar^{\mathrm{cart}}\left(\Fin_{C_2}\right) $ denote the wide subcategory of the arrow category whose morphisms are cartesian squares. 
\begin{definition}%\label{defn:gen_alg_inv_param_operad}
    Define a colored $ \mathcal{O}_{C_2} $-operad $ \mathbf{\Assoc}_{\sigma} \to \underline{\mathrm{Fin}}_{C_2, *} $ as having 
    \begin{enumerate}[label=(\arabic*)]
        \item $ \mathrm{ob}\mathbf{\Assoc}_{\sigma} \to \mathrm{Fin}_{C_2} $ is classified by a functor $ \mathrm{Fin}_{C_2}^\op \to \mathrm{Set} $ which sends $ C_2 $ and $ C_2/C_2 $ to a singleton  
        \item Multimorphisms are given by 
        \begin{equation}
        \begin{split}
            \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} \colon \Ar^{\mathrm{cart}}\left(\Fin_{C_2}\right) & \to \mathrm{Set} \\
            (f : U \to V) & \mapsto \left\{ \left( \leq_v \text{ ordering on }f^{-1}(\{v\})\right)_{v \in V}\right\}^{C_2}
        \end{split}
        \end{equation}
        where $ C_2 $ acts on $ \left\{ \left( \leq_v \text{ ordering on }f^{-1}(\{v\})\right)_{v \in V}\right\} $ by $ \left(\leq_v\right)_{v \in V} \mapsto \left(\geq_{\sigma(v)} \right) $ (here $ \geq_v $ is meant to denote the reverse of the ordering $ \leq_v $), and $ (-)^{C_2} $ denotes fixed points.  
        \item The identity $ \ast\to \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} $ is determined by observing that $ \left\{ \left( \leq_v \text{ ordering on }\id^{-1}(\{v\})\right)_{v \in V}\right\}^{C_2} \simeq * $ 
        \item The composition law $ \circ : \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} \times \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} \to \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} $ is defined by composing maps in $ \Fin_{C_2} $ and taking the lexicographic order on compositions (see \cite[Remark 4.1.1.4]{LurHA}).
    \end{enumerate}
    Postcomposing $ \mathrm{Mul}_{\mathbf{\Assoc}_{\sigma}} $ with the constant simplicial set functor gives a fibrant simplicial $ C_2 $-operad in the sense of \cite[Definition 2.5.4]{NS22}, which we also denote by $ \mathbf{\Assoc}_{\sigma} $. 
    % constant simplicial sets are Kan complexes! 
\end{definition}
\begin{definition}\label{defn:gen_alg_inv_param_operad}
    Define $ \underline{\Assoc}_{\sigma}^\otimes \to \underline{\mathrm{Fin}}_{C_2, *} $ to be the $ C_2 $-$ \infty $-operad associated to $ \mathbf{\Assoc}_{\sigma} $ under \cite[Construction 2.5.5 \& Proposition 2.5.6]{NS22}. 
    In particular, it has 
    \begin{itemize}
        \item objects consist of pairs $ (h : U \to V) $ where $ h: U \to V $ is an object of $ \underline{\mathrm{Fin}}_{C_2, *} $.  
        \item a morphism from $ (h : U \to V) $ to $ (h' : X \to Y) $ consists of 
        \begin{itemize}
            \item a span (\ref{diagram:C2_operad_generic_span}) in $ \underline{\mathrm{Fin}}_{C_2, *} $
            \item for each $ x \in X $, an ordering $ \leq_x $ on $ f^{-1}(\{x\}) $ satisfying the condition (write $ \sigma \in C_2 $ for the generator): under the isomorphism $ f^{-1}(\{x\}) \simeq f^{-1}(\{\sigma(x)\}) $ induced by the $ C_2 $-action, the ordering $ \leq_x $ is sent to the reverse of the ordering $ \leq_{\sigma(x)} $.  
        \end{itemize} 
    \end{itemize}
    there is a canonical map to $ \underline{\mathrm{Fin}}_{C_2, *} $ which is an inclusion on objects and on morphisms forgets the data of the orderings. 
\end{definition}
% Fix a free orbit $ \{x\} \subseteq X $. The ordering $ \leq_x $ is equivalent to the data of (a) an ordering $ \leq_{O(x)}$ on the orbits in $ f^{-1}(\{x\}) $ so that at most one orbit is trivial, and any such trivial orbit in $ f^{-1}(\{x\}) $ is maximal with respect to the ordering and (b) a t-ordering on $ f|_{f^{-1}(\{x\})} $. Suppose given $ \leq_x $. The subset $ \bigsqcup_{W \in \mathrm{Orbit}(f^{-1}(\{x\}))} \{\min(W)\} \subseteq f^{-1}(\{x\}) $ (where we take the minimum with respect to $ \leq_x $) inherits an ordering from $ \leq_x $. Then the canonical isomorphism $ \bigsqcup_{W \in \mathrm{Orbit}(f^{-1}(\{x\}))} \{\min(W)\} \simeq \mathrm{Orbit}(f^{-1}(\{x\})) $ endows the latter with an ordering, and each free orbit $ W $ inherits an ordering from $ \leq_x $. On the other hand, given (a) and (b), we may define an ordering on $ f^{-1}(\{x\}) $ which satisfies: if $ W \leq Z $, then $ \min(W) \leq \min(Z) \leq \max(Z) \leq \max(W) $.
\begin{remark}
    By \cite[Construction 2.5.5 \& Proposition 2.5.6]{NS22}, $ \underline{\Assoc}_{\sigma}^\otimes $ is equivalent to the nerve of a 1-category.     
\end{remark}
\begin{recollection} [Little disks operad]
    Let $ V=\RR^\sigma $ denote the sign $ C_2 $-representation on $ \RR $. 
    Let $ D_V^\otimes $ denote the simplicial $ C_2 $-operad obtained by taking $ \mathrm{Sing}_\bullet $ of the little disks operad associated to $ V $ \cite[Definition 1.1]{GuillouMay}. 
    Write $ \EE_\sigma^\otimes := N\left(D_V^\otimes\right) $ where $ N $ is the genuine operadic nerve \cites[\S4.1]{MR4011810}[Example 3.9.4]{Horev19}; $ \EE_\sigma^\otimes $ is a $ C_2 $-$ \infty $-operad. 
\end{recollection}
The following lemma shows that Definition \ref{defn:gen_alg_inv_param_operad} is a combinatorial model for the little disks operad associated to the sign representation of $ C_2 $. 
\begin{lemma}
    There is an equivalence $ \EE_\sigma^\otimes \simeq \underline{\Assoc}_\sigma^\otimes $ of $ C_2 $-$ \infty $-operads. 
\end{lemma}
\begin{proof} 
    % The following is a special case, which may be included for instructive purposes. 
    % --------------------------------------------------------------
    % If $ U $ is a finite $ C_2 $-set, then a $ C_2 $-equivariant affine embedding $ U \times D(\RR^\sigma) \to D(\RR^\sigma) $ determines an ordering on $ U $ which is sent under the $ C_2 $-action on $ U $ to its reverse; in fact $ \mathrm{Emb}^{\mathrm{Aff},C_2}(U \times D(\RR^\sigma), D(\RR^\sigma)) \to \pi_0 \mathrm{Emb}^{\mathrm{Aff},C_2}(U \times D(\RR^\sigma), D(\RR^\sigma)) $ is a homotopy equivalence. 
    Fix a $ C_2 $-equivariant map $ f \colon U \to V $ and consider $ \varphi_f \in \mathrm{Emb}^{C_2,\mathscr{S}}_f(U \times D(\RR^\sigma), V \times D(\RR^\sigma)) $ in the notation of \href{https://nataliesstewart.github.io/files/dunn.pdf}{here} where $ \mathscr{S} $ denotes the `equidiameter' embeddings of Remark 2.3 \emph{loc. cit.} 
    For any $ v \in V $, such $ \varphi_f $ determines a linear ordering $ \leq_v $ on $ \pi_0 \varphi_f^{-1}( \{v\} \times D(\RR^\sigma)) \simeq f^{-1}(v) $. 
    Moreover, since $ \varphi_f $ is $ C_2 $-equivariant, under the isomorphism $ \pi_0 \varphi_f^{-1}( \{v\} \times D(\RR^\sigma)) \simeq \pi_0 \varphi_f^{-1}( \{\sigma(v)\} \times D(\RR^\sigma)) $, the linear ordering $ \leq_v $ is sent to the linear ordering $ \geq_{\sigma(v)} $. 
    It follows that each connected component of $ \mathrm{Emb}^{C_2,\mathscr{S}}_f(U \times D(\RR^\sigma), V \times D(\RR^\sigma)) $ is homeomorphic to a nonempty convex subset of Euclidean space and is therefore contractible. 
    It follows that taking connected components on multimorphism spaces induces a weak equivalence $ D_V^\otimes \to \mathbf{Assoc}^\otimes_\sigma $ of simplicial $ C_2 $-operads. 
    It follows that there is an equivalence $ \EE_\sigma^\otimes \simeq \underline{\Assoc}_\sigma^\otimes $ of $ C_2 $-$ \infty $-operads. 
    % Definition \ref{defn:gen_alg_inv_param_operad} is equivalent to the $ C_2 $-genuine nerve of the little disks operad $ \EE_\sigma $. 
\end{proof}
\begin{remark}\label{rmk:E_sigma_operad_unital}
    The $ C_2 $-$ \infty $-operads $ \underline{\Assoc}_\sigma^\otimes $ and $ \EE_p^\otimes $ are unital in the sense of \cite[Definition 5.2.1]{NS22}. 
    Let $ \mathcal{C}^\otimes $ be a $ C_2 $-symmetric monoidal $ C_2 $-$ \infty $-category. %, and write $ \mathbbm{1} $ for the unit. 
    It follows from Proposition 5.2.8 and Theorem 5.2.11 \emph{ibid.} that the unit object $ \mathbbm{1} $ of $ \mathcal{C} $ has a canonical structure of an $ \EE_\sigma $ (resp. $ \EE_p $-)algebra, and moreover with this structure $ \mathbbm{1} $ is the initial object in $ \EE_\sigma\Alg\left(\mathcal{C}\right) $, (resp. $ \EE_p\Alg\left(\mathcal{C}\right) $). 
\end{remark}
\begin{observation}
    Suppose given a finite $ C_2 $-set $ Z $ and an ordering $ \leq_Z $ so that the $ C_2 $-action on $ Z $ sends $ \leq_Z $ to its reverse. 
    We may associate to this a canonical t-ordering on the map $ f \colon Z \to C_2/C_2 $: For each free orbit $ U \subseteq Z $, take the restriction of $ \leq_Z $ to $ U $. 
    This assignment induces a canonical forgetful map of $ C_2 $-$ \infty $-operads $ \underline{\Assoc}_\sigma^\otimes \to \EE_p^\otimes $.  
\end{observation}
The following observation will allow us to write down functors between the $ \infty $-operads we care about without worrying about higher coherences. 
\begin{observation}\label{obs:operad_maps_to_infty_operad_maps}
    Let $ \mathcal{T} $ be an atomic orbital category with a final object, and let $ T $ be a 1-categorical model for $ \mathcal{T} $ (\cite[Proposition 2.5.1]{NS22}). 
    Fix an object $ U \in \mathcal{T} $, and suppose given a simplicial colored $ T $-operad $ O $ in the sense of Definition 2.5.4 \emph{loc. cit.} 
    Consider
    \begin{enumerate}[label=(\arabic*)]
        \item set of colors is the value of $ \mathbf{F}^\op_T \to \mathrm{Set} $ on $ U $
        \item for each finite set $ I $ and $ I $-indexed collection of objects $ \{X_i\} $ and $ Y \in \mathrm{ob}O $, $ \mathrm{Mul}_O $ evaluated on $ (\nabla \colon U^I \to U, (X_i)_{i \in I}, Y) $ is the collection of multimorphisms, where $ \nabla $ denotes a fold map.  
        \item composition and unit...
    \end{enumerate}
    Observe that this defines a simplicial colored operad; call it $ O_U $. 
    Now suppose given a simplicial colored operad $ P $ and a map of simplicial colored operads $ P \to O_U $. 
    Then there are maps of $ \infty $-categories 
    \begin{equation*}
        N^\otimes(P) \to N^\otimes\left(O_U\right) \to N^\otimes (O) 
    \end{equation*} 
    where the left two instances of $ N^\otimes $ denote the operadic nerve of \cite[Definition 2.1.1.23]{LurHA} and the latter denotes the genuine operadic nerve \cites[\S4.1]{MR4011810}. 
    Moreover, the composite $ N^\otimes(P) \to N^\otimes(O) $ sends inert maps in the $ \infty $-operad $ N^\otimes(P) $ to inert maps in the $ \mathcal{T} $-$ \infty $-operad $ N^\otimes(O) $ (cf. proof of Theorem I \emph{ibid.}). 
\end{observation}
\begin{construction}
    We will construct a map $ \Assoc^\otimes \to \underline{\Assoc}^\otimes_{\sigma, C_2/e} $. 
    Here the subscript $ C_2/e $ means we consider the (non-parametrized) fiber over $ C_2/e $. 

    Observe that if $ \nabla \colon (C_2/e)^{\sqcup n} \simeq C_2/e \times \langle n \rangle \to C_2/e $ is the fold map, then a lift of $ \nabla $ to a morphism in $ \underline{\Assoc}^\otimes_{\sigma, C_2/e} $ is equivalent to the choice of an ordering on $ \{1,2, \ldots, n\} \simeq \nabla^{-1}(\{e\}) $; the ordering on $ \nabla^{-1}(\{\sigma\}) $ is uniquely determined by the ordering on $ \nabla^{-1}(\{e\}) $. 
    There are functors
    \begin{equation*}
    \begin{split}
        \iota_e, \iota_\sigma \colon \Assoc^\otimes &\to \underline{\Assoc}^\otimes_{\sigma, C_2/e} \\
        \langle n \rangle &\mapsto C_2/e \times \langle n \rangle \\
        \iota_e \colon \left(f \colon \langle n \rangle \to \langle m \rangle, (\leq_i)_{i \in \langle m \rangle^\circ}\right) & \mapsto \left(\id_{C_2} \times f \colon \langle n \rangle \to \langle m \rangle, (\leq_i \text{ ordering on }f^{-1}(i) \times \{e\})_{i \in \langle m \rangle^\circ}\right) \\
        \iota_\sigma \colon \left(f \colon \langle n \rangle \to \langle m \rangle, (\leq_i)_{i \in \langle m \rangle^\circ}\right) & \mapsto \left(\id_{C_2} \times f \colon \langle n \rangle \to \langle m \rangle, (\leq_i \text{ ordering on }f^{-1}(i) \times \{\sigma\})_{i \in \langle m \rangle^\circ}\right) \,.
    \end{split}
    \end{equation*} 
    Furthermore, there is a commutative diagram
    \begin{equation}
    \begin{tikzcd}
        \Assoc^\otimes \ar[d,"{\mathrm{rev}}"] \ar[r,"{\iota_e}"] & \underline{\Assoc}^\otimes_{\sigma, C_2/e} \ar[d,"{\sigma^*}"] \\
        \Assoc^\otimes \ar[r,"{\iota_e}"] \ar[ru,"{\iota_\sigma}"] & \underline{\Assoc}^\otimes_{\sigma, C_2/e}
    \end{tikzcd}
    \end{equation} 
    where $ \mathrm{rev} $ is the automorphism considered in \cite[Remark 4.1.1.7]{LurHA} and $ \sigma^* $ is the cocartesian pushforward along the nontrivial automorphism of $ C_2/e $ in $ \mathcal{O}_{C_2}^\op $. 
    Now if $ \mathcal{C}^\otimes $ is any $ C_2 $-symmetric monoidal $ C_2 $-$ \infty $-category, let us write $ \mathcal{C}^{e, \otimes} $ for its underlying symmetric monoidal $ \infty $-category with naive $ C_2 $-action. 
    Then the aforementioned diagram induces a commutative diagram
    \begin{equation*}
    \begin{tikzcd}[row sep=tiny]
        & \EE_1 \Alg\left(\mathcal{C}^{e,\otimes}\right) \ar[dd,"{\mathrm{rev}}","\sim"'] \\
        \Alg_{\underline{\Assoc}^\otimes_{\sigma}}\left(\mathcal{C}^\otimes\right) \ar[ru] \ar[rd] & \\
        & \EE_1 \Alg\left(\mathcal{C}^{e,\otimes}\right) \,. 
    \end{tikzcd}
    \end{equation*}
\end{construction}
\Lucyil{Define Azumaya algebras with involution in terms of algebras over $ \underline{\Assoc}_\sigma^\otimes $ instead? I think it is `better' to use $ \underline{\Assoc}_\sigma^\otimes $ instead of $ \mathcal{HM}^\otimes $. To define a functor from algebras over $ \underline{\Assoc}_\sigma^\otimes $ to Hermitian $ \infty $-categories, we can define a functor from $ \mathcal{LM}^\otimes $ to $ \underline{\Assoc}^\otimes_{\sigma,C_2/C_2} $, then use the same argument as in Construction \ref{cons:module_with_gen_involution_in_families}.} 
\begin{construction}
    \Lucyil{add argument from Construction \ref{cons:module_with_gen_involution_in_families} when moving to \texttt{main.tex}.}
    Choose a $ C_2 $-set $ U = \{u, v \} $ on which $ C_2 $ acts freely and transitively, and fix an ordering $ u \leq v $ on $ U $; we will write $ p \colon U \to C_2/C_2 $. 
    Define a functor 
    \begin{equation*}
    \begin{split}
        \iota_m \colon \Delta^1 \times \mathcal{LM}^\otimes & \to \left(\underline{\Assoc}_\sigma^\otimes\right)_{C_2/C_2} \\
         \left(0, \left(\langle n \rangle, S\right) \right) & \mapsto \left(\langle n \rangle^\circ \times U \to C_2/C_2\right) \\
         \left(1, \left(\langle n \rangle, S\right) \right) & \mapsto \left((\langle n \rangle^\circ \setminus S) \times U \sqcup S \to C_2/C_2\right) \\
         \left(\id_0,\alpha \colon \left(\langle n \rangle, S\right) \to \left(\langle m \rangle, T\right) \right) & \mapsto \left(\left.\alpha\right|_{\langle n \rangle} \times \id_U\right)  \\
         \left(\id_1,\alpha \colon \left(\langle n \rangle, S\right) \to \left(\langle m \rangle, T\right) \right) & \mapsto \left(\left.\alpha\right|_{(\langle n \rangle^\circ \setminus S)} \times \id_U\right) \sqcup \alpha_{S} \\
         \left(0<1,\id_{\left(\langle n \rangle, S\right)}\right) & \mapsto \left(\left.\id\right|_{(\langle n \rangle^\circ \setminus S)} \right) \sqcup \id_S \times p \,.
    \end{split}
    \end{equation*} 
    To define $ \iota_m $, we must give, for each $ t \in (\langle m \rangle^\circ \setminus T) \times U \sqcup T $, an ordering $ \leq_t $ on $ \iota_m(\alpha)^{-1}(t) $ so that the $ C_2 $-action sends $ \leq_t $ to the reverse of $ \leq_{\sigma(t)} $.  
    There are three cases
    \begin{itemize}
        \item If $ t = (j, u) $, endow $ \iota_m(\alpha)^{-1}(t) $ with the ordering induced by the canonical isomorphism $ \iota_m(\alpha)^{-1}(t) \simeq \alpha^{-1}(t) $ 
        \item If $ t = (j,v) $, endow $ \iota_m(\alpha)^{-1}(t) $ with the reverse of the ordering induced by the canonical isomorphism $ \iota_m(\alpha)^{-1}(t) \simeq \alpha^{-1}(t) $. 
        \item If $ t \in T $, endow $ \iota_m(\alpha)^{-1}(t) $ with the ordering so that if $ i, i' \notin S, s \in S $ and $ \alpha(i)=\alpha(i') = \alpha(s) = t $ and $ i \leq i' $, then
        \begin{equation*}
            (i,u) \leq s \leq (i, v) \qquad (i,u) \leq (i',u) \qquad (i',v) \leq (i,v) \,.
        \end{equation*}
    \end{itemize}
    Informally, restriction along $ \iota_m $ induces a functor $ \EE_\sigma\Alg\left(\Spectra^{C_2}\right) \to \Fun\left(\Delta^1, \LMod\left(\Spectra^{C_2}\right)\right) $ which sends an $ \EE_\sigma $-algebra $ A $ to a map $ N^{C_2} A \to A $ of left $ N^{C_2} A $-modules. 
\end{construction}
\begin{construction}
    Define a functor
    \begin{equation*}
    \begin{split}
        f \colon \mathcal{LM}^\otimes & \to \left(\underline{\Assoc}_\sigma^\otimes\right)_{C_2/e} \\
         \left(\langle n \rangle, S \right) & \mapsto \left(\langle n + k \rangle \times C_2 \to C_2/e \right) \quad \text{ where } n-|S|=k \\
         \left(\alpha \colon \left(\langle n \rangle, S\right) \to \left(\langle m \rangle, T\right) \right) & \mapsto \begin{pmatrix} f(\alpha) \colon \langle n+k \rangle \times C_2 \to \langle m + \ell \rangle \times C_2 \\
         (p,\gamma) \mapsto \begin{cases}
             (\alpha(p),\gamma) & \text{ if } p \leq n \\
             (\alpha (i),\gamma) & \text{ if } p = n+i, \alpha(i) \in T \\
             (m+i',\sigma\gamma) & \text{ if } p = n+i, \alpha(i) = i'_{j'}
         \end{cases}\end{pmatrix} 
    \end{split}
    \end{equation*} 
    where we write $ \gamma $ for a generic element of $ C_2 $ and $ \sigma \in C_2 $ for the generator. 
    To define $ f(\alpha) $, we must give, for each $ (j,e) \in \langle m + \ell \rangle \times C_2 $, an ordering $ \leq_{j,e} $ on $ f(\alpha)^{-1}(j,e) $ so that the $ C_2 $-action sends $ \leq_{j,e} $ to the reverse of $ \leq_{j,\sigma} $. 
    We endow $ f(\alpha)^{-1}(j,e) $ with an ordering via the equivalence $ f(\alpha)^{-1}(j,e) \subseteq \alpha^{-1}(j) \times C_2 \xrightarrow{\pi_1} \alpha^{-1}(j) $. 

    Restriction along $ f $ defines a functor $ \EE_\sigma\Alg\left(\Spectra^{C_2}\right) \to \LMod\left(\Spectra\right) $; informally, this sends an $ \EE_\sigma $-algebra $ A $ to its underlying spectrum $ A^e $, regarded as an $ A^e \otimes A^{e,\op} $-bimodule (compare \cite[Construction 4.6.3.7]{LurHA}). 
\end{construction}

\section{Comparing involutive classical Brauer and involutive higher Brauer}
\begin{question}
\begin{itemize}
    \item If, for a Poincaré $ \infty $-category $ (\mathcal{C},\Qoppa) $, there exists a Poincaré object $(E,q) $ so that $ E $ is a compact generator, can we rewrite both the category and its Poincaré structure in terms of $ \mathrm{End}_{\mathcal{C}}(E) $? 
    \item Can the \emph{property} of an existence of a Poincaré object $ (E,q) $ in $ \left(\mathrm{Perf}_X, \Qoppa_L \right) $ so that $ E $ is a compact generator be checked Zariski-locally? 
    See Toën's paper \S3.  
\end{itemize}
\end{question}

\section{Other} 

\begin{proposition}
    Assume that $ X $ has a \emph{good quotient} $ Y $ in the sense of \cite[Remark 4.20]{azumaya_involution}, and write $ p \colon X \to Y $ for the quotient map. 
    Let $ i \colon U \subseteq Y $ be the largest open subscheme on which $ \pi|_{X_U} $ is étale \cite[Proposition 4.45]{azumaya_involution}. 
    Write $ Z(\pi) $ for the closed complement of $ U $ regarded as a topological space, and let $ j \colon Z(\pi) \to Y $ denote the inclusion\footnote{$ Z(\pi) $ is referred to as the \emph{branch locus} in \cite{azumaya_involution}}. 
    Then $ \underline{\mathcal{O}}^{\varphi C_2} $ is in the essential image of $ j_* \colon \mathrm{Shv}_{\mathrm{Zar}}(Z(\pi)) \to \mathrm{Shv}_{\mathrm{Zar}}(Y) $. 
    In other words, there exists a sheaf $ \mathcal{Q} $ of $ \EE_\infty $-rings on $ Z(\pi) $ so that $ j_* \mathcal{Q} \simeq \underline{\mathcal{O}}^{\varphi C_2} $. \Lucy{hypothesis? move to main text?}
\end{proposition}
\Lucyil{How does $ \mathcal{Q} $ relate to the structure sheaf on the branch locus (as reduced subscheme of $ Y $) used in First--Williams?}
\begin{proof}
    Recall that the open-closed decomposition of $ Y $ induces a symmetric monoidal récollement
    \begin{equation*}
        \mathrm{Shv}_{\mathrm{Zar}}(U) \xleftarrow{i^*} \mathrm{Shv}_{\mathrm{Zar}}(Y) \xrightarrow{j^*} \mathrm{Shv}_{\mathrm{Zar}}(Z(\pi)) \,.
    \end{equation*}
    Therefore, to show that $ \underline{\mathcal{O}}^{\varphi C_2} $ is in the essential image of $ j_* $, it suffices to show that $ i^*\left( \underline{\mathcal{O}}^{\varphi C_2}\right) \simeq 0 $ as a sheaf on $ U $. 

    By \cite[Proposition 4.45]{azumaya_involution}, it suffices to show that if $ y $ is a point in $ U $, then $ \underline{\mathcal{O}}^{\varphi C_2}_{y} = 0 $. \Lucy{Need hypercompleteness to reduce to checking on points? Appeal to Clausen--Mathew and add finite Krull dim hypothesis?}  
    Since $ \underline{\mathcal{O}}^{\varphi C_2}_{y} = \tau_{\geq 0} \left(\Gamma\mathcal{O}_{X \times_Y \{y\}}^{tC_2}\right) $ where $ A = \Gamma\mathcal{O}_{Y,y} \to B = \Gamma\mathcal{O}_{X \times_Y \{y\}} $ is a quadratic étale map so that $ B $ has an involution $ \lambda $ and $ A = B^{\lambda} $ is a local ring with maximal ideal $ \mathfrak{m}_A $ (therefore $ B $ is semilocal by \cite[Proposition 3.15]{azumaya_involution}), it suffices to show that $ \pi_0 B^{tC_2} = 0 $. 
    By \cite[Lemma I.2.9]{NS}, we may without loss of generality replace $ A $ and $ B $ by their $ 2 $-completions. \Lucyil{this is unnecessary to the proof--but shows that the support of $ \mathcal{Q} $ intersects trivially with the open subscheme $ Y \left[\frac{1}{2}\right] $.}
    % Since $ B^{tC_2} $ is $ 2 $-complete, it suffices to show that $ B^{tC_2} \otimes \FF_2 $ vanishes. 
    By the recollement of $ A $-modules in terms of $ \mathfrak{m}_A $-complete and $ A[\mathfrak{m}_A^{-1}] $-modules, it suffices to show that $ \left(B_{\mathfrak{m}_A}^{\wedge}\right)^{tC_2} = 0 $ and $ \left(B[\mathfrak{m}_A^{-1}]\right)^{tC_2} = 0 $. 

    By \cite[Propositions 3.4 \& 3.15]{azumaya_involution}, $ B \mathfrak{m}_A = J \subseteq B $, where $ J $ denotes the Jacobson radical of $ B $. 
    We claim that $ B \simeq \lim_i B/J^i $ induces an equivalence $ B^{tC_2} \to \lim_i \left(B/J^i\right)^{tC_2} $. 
    Granting the claim, it suffices to show that $ \left(B[\mathfrak{m}_A^{-1}]\right)^{tC_2} = 0 $ and $ \left(B/J^i\right)^{tC_2} $ is zero for each $ i $. 
    Since $ (-)^{tC_2} $ is exact and lax symmetric monoidal and each $ B/J^i $ can be written as an extension of finitely many $ B/J $-modules, it suffices to show that $ \left(B[\mathfrak{m}_A^{-1}]\right)^{tC_2} $ and $ \left(B/J\right)^{tC_2} $ are zero. 
    % Now we have an exact sequence $ B/\mathfrak{m}_B \xrightarrow{\mathrm{Tr}} A/\mathfrak{m}_A = (B/\mathfrak{m}_B)^{C_2} \to \pi_0 (B/\mathfrak{m}_B)^{tC_2} \to 0 $. 

    Now observe that $ A/\mathfrak{m}_A $ (resp. $ A[\mathfrak{m}_A^{-1}] $-algebra) is a field and $ B/J $ (resp. $ B[\mathfrak{m}_A^{-1}] $) is a quadratic étale $ A/\mathfrak{m}_A $-algebra (resp. $ A[\mathfrak{m}_A^{-1}] $-algebra). 
    By \cite[Proposition 3.4(ii)]{azumaya_involution}, $ B/J $ (resp. $ B[\mathfrak{m}_A^{-1}] $) is either a separable quadratic field extension of $ A/\mathfrak{m}_A $-algebra (resp. $ A[\mathfrak{m}_A^{-1}] $-algebra), or it is isomorphic to $ \prod_{C_2} A/\mathfrak{m}_A $ (resp. $ \prod_{C_2} A[\mathfrak{m}_A^{-1}] $). 
    In the latter case, the action of $ C_2 $ on $ B/J $ (resp. $ B[\mathfrak{m}_A^{-1}] $) is manifestly free, hence $ (B/J)^{tC_2} = 0 $ (resp. $ B[\mathfrak{m}_A^{-1}]^{tC_2} = 0 $). 
    Suppose instead that $ B/J $ (resp. $ B[\mathfrak{m}_A^{-1}] $) is a separable quadratic field extension of $ A/\mathfrak{m}_A $-algebra (resp. $ A[\mathfrak{m}_A^{-1}] $-algebra). 
    By \cite[Proposition 3.4(ii)]{azumaya_involution}, $ \lambda \otimes_{B} B/J $ (resp. $ \lambda \otimes_B B[\mathfrak{m}_A^{-1}] $) is nontrivial, hence by \cite[Lemma 9.21.2, Tag 09DU]{stacks} the extension $ A/\mathfrak{m}_A \to B/J $ (resp. $ A[\mathfrak{m}_A^{-1}] \to B[\mathfrak{m}_A^{-1}] $) is Galois. 
    Since $ C_2 $ acts freely on $ B/J $ as an $ A/\mathfrak{m}_A $-module by the normal basis theorem, $ (B/J)^{tC_2} = 0 $ (resp. $ B[\mathfrak{m}_A^{-1}]^{tC_2} $).

    We conclude the proof by proving the claim. 
    Since homotopy fixed points commute with arbitrary limits, it suffices to show that $ B \simeq \lim_i B/\mathfrak{m}_B^i $ induces an equivalence $ B_{hC_2} \to \lim_i \left(B/\mathfrak{m}_B^i\right)_{hC_2} $. 
    This is true because the $ B/\mathfrak{m}_B^i $ are uniformly bounded below. \Lucy{compare \cite[Remark 2.8]{MR4280864}.}      
\end{proof}  
\begin{example}
    If $ \lambda = \mathrm{id}_X $ and $ Y = X $, then $ \pi_0 \underline{\mathcal{O}}^{\varphi C_2} = \mathcal{O}_Y /2 $. 
    On $ \pi_0 $, the norm map $ \underline{\mathcal{O}}^e \simeq \mathcal{O}_X \to \underline{\mathcal{O}}^{\varphi C_2} $ takes $ f \mapsto f^2 $. 
\end{example}

\paragraph{pushforwards along quotient maps} 
Two attempts to show the pushforward preserves filtered colimits. 
\Lucyil{ DEPRECATED JUNE 3RD: 
Here are some thoughts towards showing that the canonical map $ \colim_{[a,b]} \pi_* \mathbf{M}_{A^e}^{[a,b]} \to \pi_* \mathbf{M}_{A^e} $ is an equivalence. Later: see if \href{https://arxiv.org/pdf/2311.08051}{Example 3.1.2 here} could be useful?} 
\begin{enumerate}
    \item Each $ \mathbf{M}_{A^e}^{[a,b]} $ and $ \mathbf{M}_{A^e} $ is a hypersheaf. 
    For $ \mathbf{M}_{A^e} $ this follows from \cite[Lemma 5.4]{MR3190610}; need to prove for $ \mathbf{M}_{A^e}^{[a,b]} $. 
    \item $ \pi_* $ sends hypersheaves on the small \'etale site of $ X $ to hypersheaves on the small \'etale site of $ Y $; this follows from the proof of \cite[Proposition 6.5.2.13]{HTT}. \Lucy{which I learned from Recollection 1.14 of \href{https://math.berkeley.edu/~phaine/files/Homotopy_invariance_constructible_sheaves_published.pdf}{this paper}.} 
    \item Is $ \colim_{[a,b]} \pi_* \mathbf{M}_{A^e}^{[a,b]} $ still a hypersheaf? Hypersheaves are not in general closed under colimits, but maybe we can argue using an explicit model for this sheaf? 
    \item The hypercompletion of the \'etale $ \infty $-topos of $ Y $ has enough points; this follows from \cite[Theorem A.4.0.5]{Lurie_SAG} and Proposition 3.7.3 of Exodromy. 
    \item It suffices to show that the canonical map $ \colim_{[a,b]} \pi_* \mathbf{M}_{A^e}^{[a,b]} \to \pi_* \mathbf{M}_{A^e} $ is an equivalence on points; use the explicit model from \cite[Theorem 3.16]{azumaya_involution}?
\end{enumerate}

\Lucyil{As of June 3, I am suspicious of the next argument/think something has gone wrong--(\ref{eq:basechange}) is not supposed to hold in this level of generality. I'm not sure what the problem is yet--maybe that $ \pi_* $ does not in fact define a morphism of recollements? Will revisit later.}
\begin{lemma}
    Let $ (X,\sigma, Y,\pi) $ be a scheme with involution and good quotient. 
    Let $ \widetilde{U} \subseteq X $ be the largest open subscheme of $ X $ on which $ \pi $ is quadratic \'etale and let $ W \subseteq Y $ and $ Z = \pi^{-1}(W) \subseteq X $ be the branch and ramification loci of $ \pi $ in the sense of \cite[Proposition 4.45-4.47]{azumaya_involution} (in particular, $ W $ and $ Z $ are endowed with the reduced subscheme structure). 
    Assume that $ 2 \in \mathcal{O}_Y^\times $. 
    Then the pushforward $ \pi_* \colon \mathrm{Shv}_{\mathrm{\acute{e}t}}(X; \Spaces) \to \mathrm{Shv}_{\mathrm{\acute{e}t}}(Y; \Spaces) $ preserves filtered colimits. 
\end{lemma} 
\begin{proof}
    Since $ W \subseteq Y $, $ Z \subseteq X $ are closed immersions,\Lucy{this is automatic, but \cite[Lemma 5.36]{azumaya_involution} asserts that $ W \to Y $ is a closed embedding without proof} there exist r\'ecollements 
    \begin{equation*}
    \begin{tikzcd}[row sep=small,column sep=large]
        \mathrm{Shv}_{\mathrm{\acute{e}t}}(\widetilde{U}; \Spaces) \ar[r, bend right=10,"{j_{\widetilde{U}*}}"'] & \mathrm{Shv}_{\mathrm{\acute{e}t}}(X; \Spaces) \ar[l, bend right=10,"{j_{\widetilde{U}}^*}"'] \ar[r,bend right=10,"{i_{Z}^*}"']& \mathrm{Shv}_{\mathrm{\acute{e}t}}(Z; \Spaces)   \ar[l, bend right=10,"{i_{Z*}}"']  \\
        \mathrm{Shv}_{\mathrm{\acute{e}t}}(U; \Spaces) \ar[r, bend right=10,"{j_{U*}}"'] & \mathrm{Shv}_{\mathrm{\acute{e}t}}(Y; \Spaces) \ar[l, bend right=10,"{j_{U}^*}"'] \ar[r,bend right=10,"{i_{W}^*}"']& \mathrm{Shv}_{\mathrm{\acute{e}t}}(W; \Spaces)   \ar[l, bend right=10,"{i_{W*}}"']  
    \end{tikzcd}    \,.
    \end{equation*}
    Moreover, the pushforward functor $ \pi_* $ is a morphism of r\'ecollements in the sense of \cite[Definition 2.3]{ShahRS}. 
    In particular, the `components' of $ \pi_* $ (see Observation 2.4 of \emph{loc. cit.}) are 
    \begin{equation*}
    \begin{split}
        \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(\widetilde{U}; \Spaces)} = j_U^* \circ \pi_* \circ j_{\widetilde{U}*} = j_{U}^* \circ (\pi \circ j_{\widetilde{U}})_* = j_U^* \circ (j_U \circ \pi|_{\widetilde{U}})_* = j_U^* \circ j_{U*} \circ (\pi|_{\widetilde{U}})_* \\
        \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(Z; \Spaces)} = i_W^* \circ \pi_* \circ i_{Z*} = i_{W}^* \circ (\pi \circ i_{Z})_* = i_W^* \circ (i_W \circ \pi|_{Z})_* = i_W^* \circ i_{W*} \circ (\pi|_{Z})_* \,.
    \end{split}
    \end{equation*}
    Now $ j_U^* \circ j_{U*} \circ (\pi|_{\widetilde{U}})_* \simeq (\pi|_{\widetilde{U}})_* $ (resp. $ i_W^* \circ i_{W*} \circ (\pi|_{Z})_* \to (\pi|_{Z})_* $) induced by the counit of the adjunction $ (j_U^*, j_{U*}) $ (resp. $ (i_W^*, i_{W*}) $) is an equivalence because $ j_{U*} $ (resp. $ i_{W*}$) is fully faithful, thus
    \begin{equation}
         \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(\widetilde{U}; \Spaces)} \simeq (\pi|_{\widetilde{U}})_* \qquad \qquad  \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(Z; \Spaces)} \simeq (\pi|_{Z})_* \,. 
    \end{equation}
    We note for further reference the equivalences\Lucy{diagram instead?}
    \begin{equation}\label{eq:basechange}
         \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(\widetilde{U}; \Spaces)} \circ j_{\widetilde{U}}^* \simeq j_U^* \circ \pi_* \qquad \qquad \left. \pi_* \right|_{\mathrm{Shv}_{\mathrm{\acute{e}t}}(Z; \Spaces)}  \circ i_W^* \simeq i_Z^* \circ \pi_* \,.
    \end{equation}
    Suppose given a filtered diagram $ \mathcal{F}_\bullet $ in $ \mathrm{Shv}_{\mathrm{\acute{e}t}}(X; \Spaces) $ and write $ \mathcal{F} $ for its colimit. 
    We would like to show that the canonical map $ \colim_\bullet \pi_*(\mathcal{F}_\bullet) \to \pi_*(\mathcal{F}) $ is an equivalence.  
    Since $ j_U^*, i_W^* $ are jointly conservative (by definition of a r\'ecollement, see \cite[Definition A.8.1(e)]{LurHA}), it suffices to show that the canonical maps
    \begin{equation}\label{eq:colim_diagram_restricted}
    \begin{split}
        j^*_U \left(\colim_\bullet \pi_*(\mathcal{F}_\bullet) \right) & \to j^*_U \pi_*(\mathcal{F}) \\
        i^*_W \left(\colim_\bullet \pi_*(\mathcal{F}_\bullet) \right) & \to i_W^* \pi_*(\mathcal{F})      
    \end{split}
    \end{equation}
    are equivalences. 
    Since $ j^*_U $ and $ i^*_W $ preserve all colimits, the morphisms of (\ref{eq:colim_diagram_restricted}) can be identified with the canonical maps
    \begin{equation*}
    \begin{split}
        \colim_\bullet j^*_U \pi_*(\mathcal{F}_\bullet) \simeq \colim_\bullet (\pi|_{\widetilde{U}})_*(j^*_{\widetilde{U}}\mathcal{F}_\bullet) \to (\pi|_{\widetilde{U}})_*(j^*_{\widetilde{U}}\mathcal{F}_\bullet) \\
        \colim_\bullet i^*_W \pi_*(\mathcal{F}_\bullet) \simeq \colim_\bullet (\pi|_{W})_*(i^*_{W}\mathcal{F}_\bullet) \to (\pi|_{Z})_* i_Z^*(\mathcal{F})     \,,    
    \end{split}
    \end{equation*}
    respectively, where we have used (\ref{eq:basechange}). 
    Now $ \pi|_W $ is an equivalence and $ \pi|_{\widetilde{U}} $ is finite \'etale by \cite[Proposition 4.47]{azumaya_involution}, hence $ (\pi|_{\widetilde{U}})_* $ and $ (\pi|_{W})_* $ preserve filtered colimits. 
\end{proof}

\subsection{Algebras with genuine involution}
\begin{construction}\label{cons:pointed_left_module_cats}  
   Assume $ \mathcal{C} $ is a presentable monoidal $ \infty $-category such that the monoidal product $ - \otimes - \colon \mathcal{C} \times \mathcal{C} \to \mathcal{C} $ preserves small colimits separately in each variable. 
   Then there is an $ \infty $-category $ \LMod(\mathcal{C}) $ \cite[Example 4.2.1.18]{LurHA} whose objects are pairs $ (A, M) $ where $ A $ is an associative algebra object of $ \mathcal{C} $ and $ M $ is a left $ A $-module. 
   Write $ a, m $ respectively for the canonical forgetful functors $ \LMod(\mathcal{C})\to \mathrm{Alg}(\mathcal{C}) $, $ \LMod(\mathcal{C}) \to \mathcal{C} $ which send $ (A, M) $ to $ A $ and $ M $, resp. 
   Then $ a $ is a cocartesian fibration \cite[Corollary 4.2.3.7]{LurHA}, hence it is classified by a functor $ \mathrm{mod} \colon \mathrm{Alg}(\mathcal{C}) \to \Cat_\infty $. 

   The functor $ s $ of \cite[Example 4.2.1.17]{LurHA} determines a commutative diagram 
   %a natural transformation $ \eta \colon * \to \mathrm{mod} $, where $ * \colon \mathrm{Alg}(\mathcal{C}) \to \{*\} \hookrightarrow \Cat_\infty $ is the constant functor at the trivial category, or equivalently
   \begin{equation}
   \begin{tikzcd}
       & \mathcal{U} \ar[d] \\
        \mathrm{Alg}(\mathcal{C}) \ar[r,"\mathrm{mod}"] \ar[ru,"\eta"] & \Cat_\infty   
   \end{tikzcd}    
   \end{equation}
   where $ \mathcal{U} $ is the universal cocartesian fibration. 
   Now consider the functor $ o \colon \mathcal{U} \to \Cat_\infty $ which sends $ (\mathcal{D}, d \in \mathcal{D}) $ to the undercategory $ \mathcal{D}_{d/-} $. 
   Define $ \LMod(\mathcal{C})_{*/-} $ to be the cocartesian fibration over $ \mathrm{Alg}(\mathcal{C}) $ classified by $ o \circ \eta $. 
   Informally, an object of $ \LMod(\mathcal{C})_{*/-} $ lying over $ A \in \mathrm{Alg}(\mathcal{C}) $ is the data of a left $ A $-module $ M $ and a map of left $ A $-modules $ A \to M $. 
\end{construction}
\begin{variant}
    % Let $ \mathcal{C} $ be as in Recollection \ref{rec:left_module_cats}. 
    % There is a similar construction where left modules is replaced by \emph{bimodules} \cite[Definition 4.3.1.12]{LurHA}. 
    Let $ \mathcal{C} $ be an involutive monoidal $ \infty $-category in the sense of Definition \ref{defn:naive_involutive_algebras}. 
    There is a variation on Construction \ref{cons:pointed_left_module_cats} where left modules is replaced by \emph{bimodules} \cite[Definition 4.3.1.12]{LurHA}. \Lucy{involutive bimodules?}
\end{variant}
\begin{construction}\label{cons:alg_inv_is_bimod_canonically}
   Regard $ \mathbb{E}_1\mathrm{Alg}(\Spectra) $ as a category with $ C_2 $-action given by taking the opposite/reverse algebra.  
   There are functors $ b \colon \mathbb{E}_1\mathrm{Alg}\left(\Spectra\right)^{hC_2} \to \LMod(\Spectra) $ and $ b \colon \mathbb{E}_1\mathrm{Alg}\left(\Spectra\right)^{hC_2} \to \BiMod(\Spectra)_{*/-} $ so that $ (a, m) \circ b $ and $ (a, m)\circ b_* $ are (canonically) equivalent to $ (-^e) \otimes(-^ e)^\mathrm{op}, (-)^e $. 
   Informally, an $ \mathbb{E}_1 $-algebra with involution $ B $ can be regarded as a $ B \otimes B^\op $-module in a canonical way, and there is a canonical $ B \otimes B^\op $-module map $ B \otimes B^\op \to B $. 
\end{construction}
\begin{definition}
   The category of \emph{$\mathbb{E}_1$-algebras with genuine involution} is defined to be the limit of the $\Cat_\infty$-valued diagram 
   \begin{equation}\label{diagram:E1_alg_gen_involution}
   \begin{tikzcd}[column sep=small]
       & \LMod(\Spectra) \ar[dd,"{a,m}"]  & \\
       & & \LMod\left(\Spectra^{C_2}\right) \ar[dd,"{a, m}"] \ar[lu,"{(-)^e}"'] \\
       &\mathbb{E}_1\mathrm{Alg}(\Spectra) \times \Spectra & \\
       \mathbb{E}_1\mathrm{Alg}\left(\Spectra\right)^{hC_2} \times_{\Spectra} \Spectra^{\Delta^1}  \ar[rr,"{N^{C_2}(-^e) \times U}"'] \ar[ru,"{(-^e) \otimes(-^ e)^\mathrm{op}, (-)^e}"] \ar[ruuu,"{b \circ (-^e)}", bend left=30] & &\mathbb{E}_1\mathrm{Alg}\left(\Spectra^{C_2}\right) \times \Spectra^{C_2} \ar[lu,"{(-)^e \times (-)^e}"]
   \end{tikzcd}
   \end{equation}
   where
   \begin{itemize}
       \item $ b $ is the functor/section of Construction \ref{cons:alg_inv_is_bimod_canonically} 
       \item $ U $ is the `underlying' $C_2$-spectrum functor $ \mathbb{E}_1\mathrm{Alg}\left(\Spectra\right)^{BC_2} \times_{\Spectra} \Spectra^{\Delta^1} \to \Spectra^{BC_2} \times_{\Spectra} \Spectra^{\Delta^1} \simeq \Spectra^{C_2} $ 
       \item The upper right trapezoid commutes canonically by definition of $ \LMod $ (and the fact that the functors $ a, m $ are given by restriction to subcategories of $ LM^\otimes $). 
   \end{itemize}
   Write $ \mathbb{E}_1\mathrm{Alg}^{\mathrm{gi}}\left(\Spectra^{C_2}\right) $ for the $\infty $-category of $\mathbb{E}_1$-algebras with genuine involution. 
\end{definition}
% \begin{definition}
%    The category of \emph{$\mathbb{E}_\sigma$-algebras} is defined to be the limit of the $\Cat_\infty$-valued diagram 
%    \begin{equation}\label{diagram:E_sigma_alg}
%    \begin{tikzcd}[column sep=small]
%        & \BiMod(\Spectra)_{*/-} \ar[dd,"{a,m}"]  & \\
%        & & \BiMod\left(\Spectra^{C_2}\right)_{*/-} \ar[dd,"{a, m}"] \ar[lu,"{(-)^e}"'] \\
%        &\mathbb{E}_1\mathrm{Alg}(\Spectra) \times \Spectra & \\
%        \mathbb{E}_1\mathrm{Alg}\left(\Spectra\right)^{hC_2} \times_{\Spectra} \Spectra^{\Delta^1}  \ar[rr,"{N^{C_2}(-^e) \times U}"'] \ar[ru,"{(-^e) \otimes(-^ e)^\mathrm{op}, (-)^e}"] \ar[ruuu,"{b_* \circ (-^e)}", bend left=30] & &\mathbb{E}_1\mathrm{Alg}\left(\Spectra^{C_2}\right) \times \Spectra^{C_2} \ar[lu,"{(-)^e \times (-)^e}"]
%    \end{tikzcd}\,.
%    \end{equation}   
%    Write $ \mathbb{E}_\sigma\mathrm{Alg}\left(\Spectra^{C_2}\right) $ for the $\infty $-category of $\mathbb{E}_\sigma$-algebras. 
% \end{definition}
\begin{variant}
   Let the base be $ R $ an $ \mathbb{E}_\infty $-algebra or Poincaré ring instead of $ \mathbb{S}^0 $. 
\end{variant}
\begin{remarks}
\begin{enumerate}
   \item Compare \cite[Corollary 3.10]{AKGH_real_THH}. 
   \item There are canonical forgetful functors $  \mathbb{E}_\sigma\mathrm{Alg} \to \mathbb{E}_1\mathrm{Alg}^{\mathrm{gi}} \to \mathbb{E}_1\mathrm{Alg}^{hC_2} \to \mathbb{E}_1\mathrm{Alg}(\Spectra) $. 
\end{enumerate}
\end{remarks}
\begin{construction}\label{cons:Esigma_alg_to_R_lin_hermitian_cat}
   Let $ R, R^{\varphi C_2} \to R^{tC_2} $ be a Poincaré ring. 
   There is a functor $ \left(\Mod_{(-)}^\omega, \Qoppa_{(-)}\right) \colon \mathbb{E}_\sigma\mathrm{Alg}_R \to \left(\Cat^h_R\right)_{\left(\Mod_R^\omega,\Qoppa_R\right)/-} $. 
\end{construction}
\begin{lemma}\label{lemma:Esigma_alg_to_R_lin_hermitian_cat}
   Let $ R, R^{\varphi C_2} \to R^{tC_2} $ be a Poincaré ring. 
   \begin{enumerate}
       \item \label{lemma_item:Esigma_alg_to_R_lin_Poincare_cat} The functor of Construction \ref{cons:Esigma_alg_to_R_lin_hermitian_cat} factors through the subcategory $ \left(\Cat^p_R\right)_{\left(\Mod_R^\omega,\Qoppa_R\right)/-} $. 
       In other words, a map of $ \mathbb{E}_\sigma $-$ R $-algebras $ A \to B $ induces a duality-preserving map of $ R $-linear Poincaré $ \infty $-categories. 
       \item Write $ \Mod^p \colon \EE_1^{\mathrm{gi}} \Alg_R \to \left(\Cat^p_R\right)_{\left(\Mod_R^\omega,\Qoppa_R\right)/-} $ for the canonical factorization from part \ref{lemma_item:Esigma_alg_to_R_lin_Poincare_cat}. 
       Then $ \Mod^p $ is fully faithful. 
   \end{enumerate}
\end{lemma} 
\begin{proof}
    \Lucyil{Proof of the first point should be quite similar to/a relative variant on Corollary 3.4.2, Lemma 3.4.3 of \cite{CDHHLMNNSI}. }
    Let $ A, B $ be $ \EE_1 $-$ R $-algebras with genuine involution. 
    Then there is a fiber sequence
    \begin{equation*}
    \begin{tikzcd}[row sep=small]
        \hom_{\Mod^p_R /-}\left(\Mod^p_A, \Mod^p_B\right) \ar[r] & {\hom_{\Mod^p_R\text{-linear}}\left(\Mod^p_A, \Mod^p_B\right)} \ar[r] \ar[d,"\sim"] & {\hom_{\Mod^p_R\text{-linear}}\left(\Mod^p_R, \Mod^p_B\right)} \ar[d,"\sim"] \\
       &  \mathrm{Pn} \left(\Mod_{A^\op \otimes_R B}, \Qoppa_{A^\op \boxtimes B} \right) \ar[r] & \mathrm{Pn} \left(\Mod_{B}, \Qoppa_{B} \right) 
    \end{tikzcd}    
    \end{equation*}
    where we have used Corollary \ref{cor:poincare_fourier_mukai}. \Lucy{this refers to main text; will be fixed when we move it.} 
    The fiber of the horizontal map over the point $ (B, q_B) \in \mathrm{Pn} \left(\Mod_{B}, \Qoppa_{B} \right) $ ($q_B$ is the canonical nondegenerate form on $ B $) is %the space of $ A \otimes_R B $-module structures on $ B $ so that the induced $ N^{C_2}_R(A^\op) \otimes_{R^L}  N^{C_2}_R(B) $-module structures on $ N^{C_2}_R (B) $ is compatible with the canonical $ N^{C_2}_R(B) $-module structure on $ B $
    \Lucyil{IN PROGRESS: should be some sort of $ \EE_\sigma $ version of \cite[Proposition 3.1]{MR3190610}.}
\end{proof}

Now we observe that given a Poincaré object $ (x,q) $ of $ \left(\mathcal{C}, \Qoppa_\mathcal{C}\right) $, its endomorphism algebra admits a canonical lift to a $ \mathbb{E}_\sigma $-algebra. 
\begin{construction}\label{cons:endomorphism_of_hermitian_obj}
   There is a functor $ \mathrm{End}(-)\colon \left(\Cat^h_R\right)_{\left(\Mod_R^\omega,\Qoppa_R\right)} \to \mathbb{E}_\sigma\mathrm{Alg} $ lifting the functor $ \left(\Cat^h_R\right)_{\left(\Mod_R^\omega,\Qoppa_R\right)} \to \mathbb{E}_1\mathrm{Alg}^{hC_2} $ of \cite[Proposition 3.1.16]{CDHHLMNNSI}. 
\end{construction}
\begin{theorem}
   The functors of Construction \ref{cons:Esigma_alg_to_R_lin_hermitian_cat} and \ref{cons:endomorphism_of_hermitian_obj} form an adjoint pair. \Lucy{make everything Poincaré}
\end{theorem}
\begin{lemma}\label{lemma:poincare_endomorphisms_continuous}
    The right adjoint of Construction \ref{cons:endomorphism_of_hermitian_obj} preserves filtered colimits. 
    \Lucyil{similar to \cite[Lemma 3.4]{MR3190610}.}
\end{lemma}
\begin{proof}
    
\end{proof}
\begin{proposition}
    Let $ A $ be an $\mathbb{E}_1$-$ R $-algebra with genuine involution. 
    Then $ A $ is compact in $ \EE_1^{\mathrm{gi}} \Alg_R $ if and only if $ \Mod^p_A $ is compact in $ \Catp_R $. 
    \Lucyil{similar to \cite[Proposition 3.5]{MR3190610}.}
\end{proposition}
\begin{proof}
    The only if part of the statement follows from observing that $ \Mod^p $ admits a right adjoint which preserves filtered colimits (Lemma \ref{lemma:poincare_endomorphisms_continuous}) and \cite[Lemma 5.5.1.4]{HTT}. \Lucy{other half of the statement} 
\end{proof}
\begin{proposition}
    Let $ A $ be an $\mathbb{E}_1$-$ R $-algebra with genuine involution. 
    If $ \Mod^p_A $ is dualizable in $ \Catp_R $, then $ A $ is compact in $ \EE_1^{\mathrm{gi}} \Alg_R $.  
    \Lucyil{similar to \cite[Proposition 3.11]{MR3190610}.}
\end{proposition}
\begin{proof}
    
\end{proof}

\section{Speculative norm for Brauer group at the level of infinity categories}

	We would want a functor from $A^e$-linear stable idempotent complete infinity categories to $A^L$-linear stable idempotent complete infinity categories in order to get an extension of our exact sequence to the right. Here is what I think might do it:
	
	\begin{construction}
		Let $\lambda: A^e\to A^e$ denote the involution. Consider the functor \[\mathrm{Mod}_{\mathrm{Mod}_{A^{e}}^\omega}(\mathrm{Cat}_{\infty, \textrm{idem}}^{st})\xrightarrow{\left(-\otimes_{\mathrm{Mod}_{A^e}^\omega} \lambda^*-\right)^{hC_2}}\mathrm{Mod}_{(\mathrm{Mod}_{A^e}^\omega)^{hC_2}}(\mathrm{Cat}_{\infty, \textrm{idem}}^{st})\] which we will denote by $N_{A^{hC_2}/A}$. This functor is symmetric monoidal and we have that the composite with the base change functor gives \[\left(\mathcal{C}\otimes_{(\mathrm{Mod}_{A^e}^\omega)^{hC_2}}\mathrm{Mod}_{A^e}^\omega \otimes_{\mathrm{Mod}_{A^e}^\omega}\lambda^*(\mathcal{C}\otimes_{(\mathrm{Mod}_{A^e}^\omega)^{hC_2}}\mathrm{Mod}_{A^e}^\omega)\right)^{hC_2}\simeq \mathcal{C}^{\otimes_{(\mathrm{Mod}_{A^e}^\omega)^{hC_2}}2}\]\Noah{Maybe... We would want this to be true but I don't see a proof immediately... }
		For $\mathcal{C}\in \mathrm{Mod}_{A^e}$, we have that 
		\[(\mathcal{C}\otimes_{\mathrm{Mod}_{A^e}}\lambda^*\mathcal{C})^{hC_2}\otimes_{\mathrm{Mod}_{A^e}^{hC_2}}\mathrm{Mod}_{A^e}\simeq \mathcal{C}^{\otimes_{\mathrm{Mod}_{A^e}}2}\] via the functor which forgets the $C_2$-action. 
	\end{construction}
	
	\begin{lemma}
		The composite $\pnbr(A)\to \mathrm{br}(A^e)\to \mathrm{Pic}(\mathrm{Mod}_{\mathrm{Mod}_{A^e}^{hC_2}})$ is nullhomotopic. 
	\end{lemma}
	\begin{proof}
		The underlying category of a Poincar{\'e} invertible category is self-dual, and so its square will vanish. Since the functor is naturally nullhomotopic so too is the composite after applying the functor $\Pic(-)$.
	\end{proof}
	
	There is thus a map $\pnbr(-)\to \mathcal{F}(-)$, where $\mathcal{F}(-)$ is the fiber. Delooping both fiber sequences we see that we get a map of fiber sequences \[
	\begin{tikzcd}
		\Pic(\mathrm{Mod}_{A^L}(\mathrm{Sp}^{C_2})) \ar[r] \ar[d] & \pnbr(A) \ar[r] \ar[d] & \mathrm{br}(A^e)\ar[d,"="]\\
		\Pic(\mathrm{Mod}_{A^e}^{hC_2}) \ar[r] & \mathcal{F}(A) \ar[r] & \mathrm{br}(A^e)
	\end{tikzcd}
	\]
	from which we see that the middle horizontal map must be an equivalence whenever $\frac{1}{2}\in A^e$ and $A^{\varphi C_2}=0$.
\printbibliography

\end{document}
